
# Secondary Outcomes: Reply Speed

```{r load-packages, include = FALSE}
library(here)
source(here("R", "_library.r"))
source(here("R", "_outcome_labels.r"))
```

```{r load-data, include = FALSE}
root <- "D:/JMDPフィールド実験"

rawdt <- read_csv(
  here(root, "shaped.csv"),
  locale = locale(encoding = "cp932")
)

use <- rawdt %>%
  mutate(treat = factor(treat, levels = LETTERS[1:4]))

testdt <- use %>%
  dplyr::filter(exg_stop_reply == 0  & prefecture != "海外") %>%
  select(
    id,
    reply,
    days_reply,
    treat,
    RCTweek,
    month,
    week,
    prefecture,
    male,
    age,
    coordinate
  ) %>%
  mutate(
    prefecture = factor(prefecture, c("東京都", unique(rawdt$prefecture)[-11])),
    age_less30 = if_else(age <= 30, 1, 0),
    age_demean = age - mean(rawdt$age),
    coordinate1 = if_else(coordinate == 1, 1, 0),
    days_reply = if_else(
      is.na(days_reply),
      max(use$days_reply, na.rm = TRUE),
      days_reply
    )
  )
```

## Heterogenous Effect on Secondary Outcomes

性別×年齢（30歳以下かどうか）でサブサンプルを構築し、以下の分析を実施

1. 返信までの日数の生存分析
1. $X$日以内返信のLinear probability model

```{r heterogeneity-survival}
log_rank_test <- testdt %>%
  dplyr::filter(outcome == "Reply") %>%
  group_by(male, age30) %>%
  do(log.rank = {
    test <- survdiff(Surv(days_reply, value) ~ treat, data = .)
    tibble(chisq = test$chisq, p = 1 - pchisq(test$chisq, 3))
  }) %>%
  rowwise(male, age30) %>%
  summarize(chisq = log.rank$chisq, p = log.rank$p) %>%
  ungroup()

surv_data <- testdt %>%
  dplyr::filter(outcome == "Reply") %>%
  group_by(male, age30) %>%
  do(surv = {
    survfit(Surv(days_reply, value) ~ treat, data = .) %>%
      tidy() %>%
      mutate(treat = str_extract(strata, "[A-D]")) %>%
      select(-strata)
  })
```

## Survival Analysis (Females aged more than 30)

```{r plot-reply-days-female-over30}
with(subset(surv_data, male == 0 & age30 == 0), surv[[1]]) %>%
  ggplot(aes(x = time, y = 1 - estimate, group = treat)) +
    geom_line(aes(color = treat)) +
    annotate(
      geom = "text",
      x = 50, y = 0.6,
      label = sprintf(
        "Log-rank test\nchi-square = %1.3f; p-value = %1.3f",
        with(subset(log_rank_test, male == 0 & age30 == 0), chisq),
        with(subset(log_rank_test, male == 0 & age30 == 0), p)
      ),
      size = 5
    ) +
    scale_y_continuous(breaks = seq(0, 1, 0.1)) +
    scale_x_continuous(breaks = seq(0, 90, 5)) +
    scale_color_hue() +
    labs(x = "Days", y = "Reply rates", color = "Experimental Arms") +
    simplegg()
```

## Survival Analysis (Females aged 30 and younger)

```{r plot-reply-days-female-under30}
with(subset(surv_data, male == 0 & age30 == 1), surv[[1]]) %>%
  ggplot(aes(x = time, y = 1 - estimate, group = treat)) +
  geom_line(aes(color = treat)) +
  annotate(
    geom = "text",
    x = 50, y = 0.6,
    label = sprintf(
      "Log-rank test\nchi-square = %1.3f; p-value = %1.3f",
      with(subset(log_rank_test, male == 0 & age30 == 1), chisq),
      with(subset(log_rank_test, male == 0 & age30 == 1), p)
    ),
    size = 5
  ) +
  scale_y_continuous(breaks = seq(0, 1, 0.1)) +
  scale_x_continuous(breaks = seq(0, 90, 5)) +
  scale_color_hue() +
  labs(x = "Days", y = "Reply rates", color = "Experimental Arms") +
  simplegg()
```

## Survival Analysis (Males aged more than 30)

```{r plot-reply-days-male-over30}
with(subset(surv_data, male == 1 & age30 == 0), surv[[1]]) %>%
  ggplot(aes(x = time, y = 1 - estimate, group = treat)) +
  geom_line(aes(color = treat)) +
  annotate(
    geom = "text",
    x = 50, y = 0.6,
    label = sprintf(
      "Log-rank test\nchi-square = %1.3f; p-value = %1.3f",
      with(subset(log_rank_test, male == 1 & age30 == 0), chisq),
      with(subset(log_rank_test, male == 1 & age30 == 0), p)
    ),
    size = 5
  ) +
  scale_y_continuous(breaks = seq(0, 1, 0.1)) +
  scale_x_continuous(breaks = seq(0, 90, 5)) +
  scale_color_hue() +
  labs(x = "Days", y = "Reply rates", color = "Experimental Arms") +
  simplegg()
```

## Survival Analysis (Males aged 30 and younger)

```{r plot-reply-days-male-under30}
with(subset(surv_data, male == 1 & age30 == 1), surv[[1]]) %>%
  ggplot(aes(x = time, y = 1 - estimate, group = treat)) +
  geom_line(aes(color = treat)) +
  annotate(
    geom = "text",
    x = 50, y = 0.6,
    label = sprintf(
      "Log-rank test\nchi-square = %1.3f; p-value = %1.3f",
      with(subset(log_rank_test, male == 1 & age30 == 1), chisq),
      with(subset(log_rank_test, male == 1 & age30 == 1), p)
    ),
    size = 5
  ) +
  scale_y_continuous(breaks = seq(0, 1, 0.1)) +
  scale_x_continuous(breaks = seq(0, 90, 5)) +
  scale_color_hue() +
  labs(x = "Days", y = "Reply rates", color = "Experimental Arms") +
  simplegg()
```

## Reply within $X$ days (Females aged more than 30)

```{r heterogeneity-reply-within-days}
model <- value ~ treat + coordinate + prefecture + factor(month) + factor(week)

days_collapse <- testdt %>%
  dplyr::filter(outcome == "Reply") %>%
  mutate(
    value10 = if_else(days_reply <= 10, 1, 0),
    value20 = if_else(days_reply <= 20, 1, 0),
    value30 = if_else(days_reply <= 30, 1, 0),
    value40 = if_else(days_reply <= 40, 1, 0),
    value85 = value
  ) %>%
  select(-value) %>%
  pivot_longer(
    value10:value85,
    names_to = "until",
    names_prefix = "value"
  ) %>%
  mutate(until = factor(
    until,
    levels = c("10", "20", "30", "40", "85")
  )) %>%
  group_by(until, male, age30)

est_days_collapse <- days_collapse %>%
  do(est = lm_robust(
    model,
    cluster = RCTweek,
    se_type = "stata",
    data = .
  ))

bc_ftest <- days_collapse %>%
  do(
    lh_robust(
      model,
      cluster = RCTweek,
      se_type = "stata",
      linear_hypothesis = "treatB - treatC = 0",
      data = .
    ) %>%
      with(lh) %>%
      tibble()
  )

bd_ftest <- days_collapse %>%
  do(
    lh_robust(
      model,
      cluster = RCTweek,
      se_type = "stata",
      linear_hypothesis = "treatB - treatD = 0",
      data = .
    ) %>%
      with(lh) %>%
      tibble()
  )

cd_ftest <- days_collapse %>%
  do(
    lh_robust(
      model,
      cluster = RCTweek,
      se_type = "stata",
      linear_hypothesis = "treatC - treatD = 0",
      data = .
    ) %>%
      with(lh) %>%
      tibble()
  )
```

```{r tab-reply-until-days-female-over30}
est_days_collapse %>%
  dplyr::filter(male == 0 & age30 == 0) %>%
  pull(est) %>%
  setNames(paste0("(", seq(length(.)), ")")) %>%
  modelsummary(
    stars = c("*" = 0.1, "**" = 0.05, "***" = 0.01),
    coef_map = c(
      "treatB" = "B",
      "treatC" = "C",
      "treatD" = "D"
    ),
    gof_omit = "R2|AIC|BIC|Log|Std|FE|se_type",
    add_rows = subset(bc_ftest, male == 0 & age30 == 0)$p.value %>%
      rbind(subset(bd_ftest, male == 0 & age30 == 0)$p.value) %>%
      rbind(subset(cd_ftest, male == 0 & age30 == 0)$p.value) %>%
      data.frame(term = c("B = C", "B = D", "C = D"), .)
  ) %>%
  kableExtra::kable_styling(font_size = 9) %>%
  kableExtra::add_header_above(c(
    " " = 1, "\u2266 10days" = 1,
    "\u2266 20days" = 1, "\u2266 30days" = 1,
    "\u2266 40days" = 1, "\u2266 85days" = 1
  )) %>%
  kableExtra::column_spec(2:6, width = "5em") %>%
  kableExtra::group_rows(
    "F-tests, p-value", 8, 10,
    bold = FALSE, italic = TRUE
  )
```

## Reply within $X$ days (Females aged 30 and younger)

```{r tab-reply-until-days-female-under30}
est_days_collapse %>%
  dplyr::filter(male == 0 & age30 == 1) %>%
  pull(est) %>%
  setNames(paste0("(", seq(length(.)), ")")) %>%
  modelsummary(
    stars = c("*" = 0.1, "**" = 0.05, "***" = 0.01),
    coef_map = c(
      "treatB" = "B",
      "treatC" = "C",
      "treatD" = "D"
    ),
    gof_omit = "R2|AIC|BIC|Log|Std|FE|se_type",
    add_rows = subset(bc_ftest, male == 0 & age30 == 1)$p.value %>%
      rbind(subset(bd_ftest, male == 0 & age30 == 1)$p.value) %>%
      rbind(subset(cd_ftest, male == 0 & age30 == 1)$p.value) %>%
      data.frame(term = c("B = C", "B = D", "C = D"), .)
  ) %>%
  kableExtra::kable_styling(font_size = 9) %>%
  kableExtra::add_header_above(c(
    " " = 1, "\u2266 10days" = 1,
    "\u2266 20days" = 1, "\u2266 30days" = 1,
    "\u2266 40days" = 1, "\u2266 85days" = 1
  )) %>%
  kableExtra::column_spec(2:6, width = "5em") %>%
  kableExtra::group_rows(
    "F-tests, p-value", 8, 10,
    bold = FALSE, italic = TRUE
  )
```

## Reply within $X$ days (Males aged more than 30)

```{r tab-reply-until-days-male-over30}
est_days_collapse %>%
  dplyr::filter(male == 1 & age30 == 0) %>%
  pull(est) %>%
  setNames(paste0("(", seq(length(.)), ")")) %>%
  modelsummary(
    stars = c("*" = 0.1, "**" = 0.05, "***" = 0.01),
    coef_map = c(
      "treatB" = "B",
      "treatC" = "C",
      "treatD" = "D"
    ),
    gof_omit = "R2|AIC|BIC|Log|Std|FE|se_type",
    add_rows = subset(bc_ftest, male == 1 & age30 == 0)$p.value %>%
      rbind(subset(bd_ftest, male == 1 & age30 == 0)$p.value) %>%
      rbind(subset(cd_ftest, male == 1 & age30 == 0)$p.value) %>%
      data.frame(term = c("B = C", "B = D", "C = D"), .)
  ) %>%
  kableExtra::kable_styling(font_size = 9) %>%
  kableExtra::add_header_above(c(
    " " = 1, "\u2266 10days" = 1,
    "\u2266 20days" = 1, "\u2266 30days" = 1,
    "\u2266 40days" = 1, "\u2266 85days" = 1
  )) %>%
  kableExtra::column_spec(2:6, width = "5em") %>%
  kableExtra::group_rows(
    "F-tests, p-value", 8, 10,
    bold = FALSE, italic = TRUE
  )
```

## Reply within $X$ days (Males aged 30 and younger)

```{r tab-reply-until-days-male-under30}
est_days_collapse %>%
  dplyr::filter(male == 1 & age30 == 1) %>%
  pull(est) %>%
  setNames(paste0("(", seq(length(.)), ")")) %>%
  modelsummary(
    stars = c("*" = 0.1, "**" = 0.05, "***" = 0.01),
    coef_map = c(
      "treatB" = "B",
      "treatC" = "C",
      "treatD" = "D"
    ),
    gof_omit = "R2|AIC|BIC|Log|Std|FE|se_type",
    add_rows = subset(bc_ftest, male == 1 & age30 == 1)$p.value %>%
      rbind(subset(bd_ftest, male == 1 & age30 == 1)$p.value) %>%
      rbind(subset(cd_ftest, male == 1 & age30 == 1)$p.value) %>%
      data.frame(term = c("B = C", "B = D", "C = D"), .)
  ) %>%
  kableExtra::kable_styling(font_size = 9) %>%
  kableExtra::add_header_above(c(
    " " = 1, "\u2266 10days" = 1,
    "\u2266 20days" = 1, "\u2266 30days" = 1,
    "\u2266 40days" = 1, "\u2266 85days" = 1
  )) %>%
  kableExtra::column_spec(2:6, width = "5em") %>%
  kableExtra::group_rows(
    "F-tests, p-value", 8, 10,
    bold = FALSE, italic = TRUE
  )
```