---
title: |
  Exploring Information Provision to Promote Stem Cell Donation:
  Evidence from a Field Experiment of the Japan Marrow Donor Program
author:
  - name: Hiroki Kato
    affil-id: a
    note: "Corresponding author. E-mail address: hkato.econ@aoyamagakuin.jp"
  - name: Fumio Ohtake
    affil-id: b
    note: "E-mail address: ohtake@cider.osaka-u.ac.jp"
  - name: Saiko Kurosawa
    affil-id: c
    note: "E-mail address: skurosaw@inahp.jp"
  - name: Kazuhiro Yoshiuchi
    affil-id: d
    note: "E-mail address: kyoshiuc-tky@umin.ac.jp "
  - name: Takahiro Fukuda
    affil-id: e
    note: "E-mail address: tafukuda@ncc.go.jp"
affiliations:
  - id: a
    name: School of International Politics, Economics and Communication, Aoyama Gakuin University, 4-4-25 Shibuya, Shibuya-ku, Tokyo 150-8366, Japan
  - id: b
    name: Center for Infectious Disease Education and Research (CiDER), Osaka University, 1-10 Yamadaoka, Suita, Osaka 565-0871, Japan​
  - id: c
    name: Department of Oncology, Ina Central Hospital, 1313-1, Koshirokubo, Ina, Nagano 396-8555, Japan
  - id: d
    name: Graduate School of Medicine, The University of Tokyo, 7-3-1 Hongo, Bunkyo, Tokyo 113-8655, Japan
  - id: e
    name: Department of Hematopoietic Stem Cell Transplantation, National Cancer Center Hospital, 5-1-1 Tsukiji, Chuo-ku, Tokyo 104-0045, Japan
abstract: |
  \revise{Registered potential donors in stem cell transplantation} may refuse to donate when matched with patients, causing supply shortages. \revise{To reduce such donor dropout}, we developed behavioral interventions comprising messages \revise{added to} the letters sent when donors are matched with patients \revise{, and} conducted a field experiment to \revise{evaluate} the effect of our intervention. The results demonstrate that our interventions can reduce donor dropout and increase donor availability for transplantation. Specifically, the message emphasizing the limited number of compatible donors per patient increased the probability of donors completing the confirmatory typing stage by \revise{$7.3$}%. Since physicians can choose the best donor for proceeding to donation from those who complete the confirmatory typing stage, this message increases donor availability for transplantation.

  \vspace{0.5em}
  \noindent
  \textit{Keywords}: prosocial behavior, field experiment, crowding-out, information provision, Japan Marrow Donor Program, stem cell transplantation

  \vspace{0.5em}
  \noindent
  \textit{JEL classification}: D64, D90, H41, I11
acknowledgements: |
  We would like to thank the Japan Marrow Donor Program office for managing the field experiment and providing us with the data. We thank Tsuneaki Hirakawa and two anonymous reviewers for their helpful comments and suggestions. This study was conducted with the approval of the institutional review boards of the Graduate School of Economics, Osaka University (approval number: R030305-2) and the Japan Marrow Donor Program (approval number: JMDP2021-04).

  \vspace{0.5em}
  \noindent
  Funding: This work was supported by the Japan Society for the Promotion of Science [grant number 20H05632] and the Ministry of Health, Labour and Welfare [grant number 19FF1001].

  \vspace{0.5em}
  \noindent
  Declarations of interest: none.
ai-declaration: |
  During the preparation of this work, we used Claude to improve the readability and language of the manuscript. After using these tools, we carefully reviewed and edited the content as needed and take full responsibility for the content of the published article.
bibliography: biblio.bib
biblio-style: elsarticle-harv.bst
output:
  bookdown::pdf_document2:
    latex_engine: pdflatex
    template: template/my-template-science-direct.tex
    keep_tex: true
    toc: false
    number_sections: true
    citation_package: natbib
base-strech: 2
fontsize: 12pt
---

```{r include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  error = FALSE,
  message = FALSE,
  dev = "pdf",
  fig.width = 15,
  fig.height = 10,
  fig.pos = "t",
  out.extra = ""
)
```

```{r option, include = FALSE}
options(
  knitr.table.format = "latex",
  knitr.kable.NA = "",
  kableExtra.auto_format = FALSE,
  modelsummary_factory_latex = "kableExtra",
  modelsummary_get = "broom"
)
```

\clearpage

# Introduction {#intro}

\revise{Similar to organ transplantation, allogeneic hematopoietic stem cell transplantation (HSCT), a treatment with the lowest relapse rate among available treatments for leukemia and other blood cancers, faces supply shortages in many countries. Existing evidence---especially from organ transplantation---has largely focused on increasing the number of registered donors \citep[e.g.,][]{Kessler2012}. In allogeneic hematopoietic stem cell transplantation, however, there is an additional challenge: even registered donors may refuse to donate once they are matched with a patient \citep[e.g.,][]{Switzer2018, Haylock2024}. Mitigating such donor dropout at the time of matching is therefore crucial for improving the effective supply of stem cell donations. This study examines how behavioral interventions delivered at the time of matching can prevent donor dropout and alleviate supply shortages.}

\revise{In this treatment, (1) anticancer drugs or radiation are used to kill tumor cells and (2) healthy hematopoietic stem cells are transplanted from a donor. The transplantation requires that the donor's white blood cell type (HLA) completely or partially matches the patient's HLA.}[^hapro] \revise{When patients cannot find a compatible donor among their relatives, who are more likely to be matched, in most developed countries, they can search for unrelated donors through donor registries such as the National Marrow Donor Program (NMDP) in the U.S., the Japan Marrow Donor Program (JMDP), and DKMS Germany.}[^match-probability]

[^hapro]: When HLA-identical or partially matched unrelated donors are unavailable, several options exist. The first option is haploidentical stem cell transplantation in which stem cells are transplanted from a close relative with semi-matched HLA. The second option is cord blood transplantation in which stem cells are transplanted from the umbilical cord or placenta of pregnant women. The HLA requirements for these transplants are weaker than those for bone marrow (or peripheral blood stem cell (PBSC)) transplants between unrelated individuals. Notably, in Japan, bone marrow and PBSC transplants between unrelated individuals accounted for 20% of all transplants in 2021 [@JDCHCT2022].

[^match-probability]: While the probability of a complete match between two randomly selected individuals is less than 1\%, the probability of a full match between siblings is 30\%.

\revise{However, donor registries worldwide face a common challenge: dropout among registered donors \citep{Switzer2004, Lown2014, Hamed2023}. Donor candidates matched with patients undergo confirmatory typing (CT) to assess their eligibility for transplantation. Because physicians select the most suitable donor based on CT results, dropout before CT reduces donor availability. For example, dropout at the CT stage is 23\% in DKMS Germany \citep{Haylock2024}, and} 56\% of transplant coordinations in JMDP do not reach the CT stage for donor-related reasons \citep{Hirakawa2018}. \revise{Donor dropout prolongs time to transplantation and worsens patient outcomes \citep{Lown2013}.}[^fact] Thus, \revise{interventions to reduce pre-CT donor dropout are needed while preserving individual autonomy.}[^donor-quantity]

[^fact]: In the JMDP, between 2004 and 2013, only 60\% of the patients registered with the JMDP end up receiving transplantation. Moreover, 58\% of patients who died (or had their transplantation interrupted because of poor health) passed away within 200 days [@Hirakawa2018].

[^donor-quantity]: \revise{One may think that expanding donor pool (i.e., recruiting new donors) is one solution. However, many registries have already undertaken such activities for a long time, so the marginal benefit of expanding the donor pool is limited.} Indeed, in the JMDP, the benefit of expanding the donor pool is limited because most patients do eventually find donor candidates [@Takanashi2016].

In this study, in collaboration with the JMDP, we developed information interventions to increase the number of donor candidates who reach the CT stage. The interventions added messages to the letters sent when donors are matched with patients. This letter informs \revise{donors of their compatibility with a specific patient} and requests their participation in the transplantation coordination. Upon responding to this so-called "HLA match letter," matched donors indicate their willingness to donate and proceed to the CT stage. We developed two intervention messages---\emph{matching difficulty} and \emph{early coordination}. \revise{The former emphasizes the limited number of HLA-compatible donors per patient to reduce motivational crowding-out among altruistic donors. The latter highlights the importance of early coordination for patient outcomes to increase the perceived value of responding now. This emphasis is motivated by the finding that present bias is positively associated with donation intention \citep{Ohtake2020}.}

\revise{To evaluate these interventions, we conducted a field experiment with the JMDP between September 2021 and February 2022. Our experimental participants comprised recipients of the 11,154 HLA match letters that were sent during the experimental period. To maintain randomness to the best of the JMDP office's abilities, we assigned treatment groups using weekly cluster randomization. After the experiment, we used coordination data provided by the JMDP to estimate the effects of the interventions.}

We \revise{found} that our intervention increases the probability of donors reaching the CT stage. Specifically, \revise{the matching difficulty message increased the probability of reaching CT by $7.3$\%, whereas the early coordination message did not have the intended effect. These findings are robust to several checks, including covariate adjustment, multiple-hypothesis testing across treatment groups, and logistic regression albeit without a prior pilot study or preregistration. Taken together, our field experiment suggests that perceived scarcity of compatible donors reduces motivational crowding-out of altruistic donors.}

\revise{We contribute to the literature on information provision in donor engagement. The key distinction with previous studies lies in both the intervention objective and the target population. Previous studies have mainly aimed to increase total supply and targeted the general population with lower baseline willingness to donate \citep{Li2016, Sallis2018, Robitaille2021, Goette2020, Goette2024}.}[^Heger2020] \revise{In contrast, our objective is to prevent dropout among registered donors rather than to increase the total supply. Accordingly, our target population consists of registered donors, who are more likely to have altruistic preferences \citep{Bergstrom2009, Ohtake2020}.}[^other-context]

[^Heger2020]: \citet{Heger2020} showed that establishing registries that collect potential donors beforehand is effective in increasing the supply of blood donation. In the case of HSCT, such registries already exist. Our motivation is to prevent dropout among registered donors when they are matched with patients.

[^other-context]: Previous studies have also examined the effects of behavioral interventions such as message and information provision in health and medical policy contexts, including vaccination [for example, @Dai2021; @Milkman2021], breast cancer screening [@Bertoni2020], and cord blood transplantation [@Grieco2018]. Unlike our study, these studies targeted the general population \revise{including people with low motivation to take action}.

\revise{However, a few studies share the same intervention goal as ours. \citet{Switzer2018} examined information provision interventions at the time of matching, but their study was not a randomized controlled trial. \citet{Haylock2024} examined the effects of commitment before matching, and thus the timing of their intervention differs from ours. To the best of our knowledge, we are the first to document the effects of information provision at the time of matching among an altruistic population through a randomized controlled trial.}

\revise{We also contribute to the literature on social norm messages by developing an effective message with content opposite to theirs. Social norm messages work best when actions are publicly observable \citep{Bursztyn2017} and when the target population has low intrinsic motivation \citep{Shang2009, Kessler2017}. When intrinsic motivation is already high, invoking social image concerns risks undermining prosocial behavior \citep{Ariely2009, Mellstrom2008, Gneezy2012a}. In the context of stem cell donation, however, neither condition holds: donations are unobservable, and the target population is altruistic individuals already motivated to donate, making social norm messages potentially counterproductive. We instead developed a scarcity message (only a small number of people can donate) and showed that it is effective in an altruistic population.}

The remainder of this paper is organized as follows. Section \@ref(experiment) provides an overview of the coordination process of the JMDP and describes our field experiment. Section \@ref(result) presents the results of our experiment. Section \ref{discussion} discusses the welfare implications. Finally, Section \ref{conclusion} concludes.

# Field Experiment {#experiment}

```{r library, include=FALSE}
library(here)
library(xfun)
source(here("R/R6_RawData.r"))
source(here("R/R6_Schedule.r"))

options(
  knitr.kable.NA = "",
  modelsummary_stars_note = FALSE
)

data_root <- "data"
```

## Background: Coordination Process of the JMDP {#background}

```{r flow-chart-coordination, fig.cap = "Flowchart of the JMDP Coordination Process and Sample Selection \\newline \\emph{Note}: The numbers in this figure are based on our experimental data."}
knitr::include_graphics(here("image/flowchart.pdf"))
```

\revise{We first describe who can register as donors with the JMDP and how the donor pool is composed.} Individuals eligible to register as donors with the JMDP must be between 18 and 54 years and in good health.[^weight] Individuals who can actually donate must be between 20 and 55 years. As of December 2024, approximately 560,000 donors were registered with the JMDP. Of these, 240,000 (42\%) were under 40 years and 280,000 (50\%) were male.[^reference]

[^weight]: Additionally, men must weigh at least 45 kg and women must weigh at least 40 kg. See \url{https://www.jmdp.or.jp/reg/requirement/} (Japanese; Accessed October 24, 2025).

[^reference]: Data source: \url{https://www.bs.jrc.or.jp/bmdc/donorregistrant/m2_03_00_statistics.html} (Japanese; Accessed October 24, 2025).

\revise{We next outline the coordination process leading to stem cell donation through the JMDP (see Figure \ref{fig:flow-chart-coordination} for a visual overview)}. After a patient's physician registers the patient with the JMDP, the JMDP compiles a list of candidates based on the physician's criteria (primarily HLA compatibility). The physician selects up to 10 matched donors from this list. Subsequently, the JMDP office sends each matched donor an HLA match letter, recommending a response within seven days.[^SMS] Our experimental participants are all matched donors who received HLA match letters between September 2021 and February 2022. Upon responding, matched donors complete a medical questionnaire and indicate their willingness to donate.

[^SMS]: Simultaneously, the JMDP office sends a short message to matched donors informing them that the JMDP has sent the HLA match letter.

A matched and willing donor undergoes CT within approximately one month. CT confirms whether the matched donor meets the criteria for transplantation set by the JMDP. The transplantation coordinator delegated by the JMDP explains the details of the donation process and asks matched donors and their families about their willingness to donate. Thereafter, the coordinating physician conducts medical interviews, examinations, and blood tests, including those for infectious disease markers. Collection methods (bone marrow or PBSC collection) are also determined based on the preferences of the matched donor and coordinating physician. CT can be skipped when a matched donor is eligible based on a previous CT result within one year.

\revise{The patient's physician selects the best donor from matched donors who have reached CT. Once the JMDP judges a matched donor to be eligible based on CT results, the physician must classify the donor within 40 days as best donor, backup donor, or rejection. Only the best donor proceeds to final consent and donation, while up to four backup donors are designated and ranked by priority. If coordination with the best donor is interrupted, the highest-priority backup donor is promoted to best donor.}[^late-arrival]

[^late-arrival]: Even after selecting the best donor, if the JMDP determines that additional matched donors are eligible, the physician must classify them as backup donors or rejections within 40 days. However, if the best donor has not yet provided final consent, the physician can change the best donor to a later-arriving matched donor.

The best donor must provide final consent after being informed of their selection by the coordinator and coordinating physician. Simultaneously, a representative of the donor's family must provide consent to the donation. After final consent is obtained, the donor cannot withdraw their decision to donate. They then undergo a surgical procedure to collect stem cells. The time from CT to collection is approximately three to four months. Importantly, throughout the coordination process, a matched donor cannot access any information about the matched patient (e.g., the number of other available potential donors), nor can the matched donor obtain this information from the transplantation coordinator or coordinating physician.

## Experimental Design {#design}

```{r list-message}
message_dt <- tribble(
  ~treat, ~contents,
  "Standard message",
  "We inform you that your HLA type (white blood cell type) matches that of a patient in our registry, and you have been selected as one of our potential donors. We are contacting you to ask if you would like to proceed with further testing and interviews for donation. Please read the enclosed materials carefully, consider whether coordination is possible, and return the form within seven days of receiving this information. [\\emph{Insert intervention messages here}] If we proceed with coordination after receiving your response, a coordinator will contact you by phone to discuss the details of your request.",
  "Matching difficulty message",
  "The number of registered donors whose HLA type matches that of a single registered patient is one in hundreds to tens of thousands. While we may find multiple potential donors, we hope you understand that the number is limited.",
  "Early coordination message",
  "Approximately 60\\% of patients receive a transplant through the JMDP. The earlier a donor is found, the higher this rate can be increased."
)

message_dt %>%
  knitr::kable(
    caption = "List of Intervention Messages",
    col.names = c("Message", "Content"),
    align = "ll",
    booktabs = TRUE,
    linesep = "",
    escape = FALSE
  ) %>%
  kableExtra::kable_styling(font_size = 8) %>%
  kableExtra::group_rows("Intervention message", 2, 3) %>%
  kableExtra::column_spec(2, width = "40em") %>%
  kableExtra::footnote(
    general_title = "",
    general = "\\\\emph{Note}: Translated by the authors.",
    threeparttable = TRUE,
    escape = FALSE
  )
```

Our intervention involved adding two messages into the HLA match letter.[^pressure] Table \@ref(tab:list-message) lists the content of the standard letter and the two intervention messages. The JMDP also encloses a handbook that describes the coordination process as well as the medical questionnaire and donor consent form.[^ref-handbook] We developed two messages based on the finding from our preliminary survey that the target population for our intervention includes more altruistic individuals than the general population [@Ohtake2020].

[^pressure]: In designing our intervention messages, we were careful to avoid placing undue psychological pressure on potential donors. Specifically, we avoided using language that sounded like an appeal. Additionally, we only used information publicly available from the JMDP. Finally, the risks of transplantation were explained in a typical manner. The intervention message was approved by the institutional review boards of the Graduate School of Economics, Osaka University and the JMDP.

[^ref-handbook]: The handbook can be found at [https://www.jmdp.or.jp/pdf/en/DonorHandBook201708.pdf](https://www.jmdp.or.jp/pdf/en/DonorHandBook201708.pdf) (Accessed December 9, 2024).

The matching difficulty message emphasizes the low number of matched donors per registered patient. If other potential donors with the same HLA type are in the pool, one donor's donation can be substituted with that of another compatible donor, and up to 10 donors can be simultaneously matched with a single patient. Therefore, transplantation through the JMDP represents a public good [@Bergstrom2009]. \revise{In this setting, self-interested individuals who do not care about the patient do not contribute. By contrast, individuals with altruistic preferences exhibit two types of behavior. First, purely altruistic individuals who care about transplant outcome may crowd out their motivation by donation from substitutable donors.}[^some-fact] \revise{Second, warm-glow individuals, who derive utility from the act of giving itself, may donate regardless of substitutable donors} [@Andreoni1990]. Thus, the matching difficulty message emphasizes the small number of possible substitutes and is expected to \revise{reduce motivational crowding-out} of purely altruistic individuals, thereby increasing their willingness to donate.[^other-mechanism]

[^some-fact]: \citet{Ohtake2020} found that 22\% of registrants had pure altruistic preferences. Moreover, @Kurosawa2022 interviewed previously matched donors and found that those with low donation intention felt that they were "one of several donors." This implies that some potential donors with low intention recognize that their donation could be substituted by others.

[^other-mechanism]: There are two additional mechanisms. First, since matched donors cannot know the number of substitutable donors, this uncertainty may reduce their willingness to donate [@Exley2016]. The matching difficulty message reduces this uncertainty. Second, the message makes the rarity of the opportunity to donate more salient, which may change donor behavior.


```{r experiment-data, include=FALSE}
rawdt <- RawData$new(
  here(data_root, "shape.csv"),
  treat_vars = "treat",
  treat_levels = LETTERS[1:4],
  treat_labels = c("StatusQuo", "MatchMessage", "CoordMessage", "BothMessage")
)

rawdt$add_cond_study_sample("prefecture != '海外'")
rawdt$add_cond_study_sample("ongoing == 0")

rawdt_noskip <- rawdt$clone()
rawdt_noskip$add_cond_study_sample("skip_test == 0")
```

```{r rct-setup, include=FALSE}
intervention <- list(
  "Standard message" = c(StatusQuo = "X", MatchMessage = "X", CoordMessage = "X", BothMessage = "X"),
  "Matching difficulty message" = c(StatusQuo = "", MatchMessage = "X", CoordMessage = "", BothMessage = "X"),
  "Early coordination message" = c(StatusQuo = "", MatchMessage = "", CoordMessage = "X", BothMessage = "X")
)

endpoint <- list(
  reply = "Response",
  positive = "Positive intention",
  test = "CT",
  candidate = "Donor selection",
  consent = "Final consent",
  donate = "Donation"
)

# main sample
rct <- rawdt$RCT()
rct$add_intervention(intervention)
rct$add_outcome(endpoint)
rct$set_default_cluster("RCTweek")
rct$set_default_se_type("stata")

# robust sample (remove those who skipped the CT)
rct_noskip <- rawdt_noskip$RCT()
rct_noskip$add_intervention(intervention)
rct_noskip$add_outcome(endpoint)
rct_noskip$set_default_cluster("RCTweek")
rct_noskip$set_default_se_type("stata")
```

```{r speed-CT-cond-response, fig.cap = "Binned Scatter Plot of CT vs. Response Speed among Those Who Responded with Positive Intention. \\newline \\emph{Note}: We used those who responded with positive intention to donate in the control group (StatusQuo group). The dashed line represents nonparametric fitting. The solid line represents a fitted line of the logistic regression."}
positive_dt <- rct$data %>%
  filter(positive == 1 & 0 < days_reply & treat == "StatusQuo")

plotdt <- positive_dt %>%
  mutate(ntile = ntile(days_reply, 20)) %>%
  group_by(ntile) %>%
  summarize(
    median_day = (max(days_reply) + min(days_reply)) / 2,
    mean_ct = mean(test)
  )

plotdt %>%
  ggplot(aes(x = median_day, y = mean_ct)) +
    geom_point(color = "grey40", size = 3) +
    geom_smooth(
      aes(x = days_reply, y = test),
      data = positive_dt,
      method = "glm",
      method.args = list(family = "binomial"),
      se = FALSE,
      alpha = 0.2,
      color = "black",
      linetype = 1
    ) +
    geom_smooth(
      aes(x = days_reply, y = test),
      data = positive_dt,
      se = FALSE,
      alpha = 0.2,
      color = "black",
      linetype = 2
    ) +
    labs(x = "Response days", y = "Proportion of Reaching CT", shape = "Outcome") +
    my_theme_classic(size = 25)
```

\revise{The early coordination message emphasizes that responding early can increase the patient's transplantation rate. Motivated by our preliminary finding that registered donors with present bias (placing higher value on immediate outcomes) are more likely to proceed with donations \citep{Ohtake2020}, we designed a message that highlights the value of responding now rather than postponing the response.}[^perceived-cost] \revise{Because earlier responses are associated with higher rates of reaching the CT stage (Figure \ref{fig:speed-CT-cond-response}), we expect this message to encourage early responses and increase the probability of donors undergoing CT.}

[^perceived-cost]: \citet{Haylock2024} showed that notifying registries in advance of the period during which donation is possible functions as a commitment and increases the perceived cost of refusing to donate. \revise{This message may also increase the perceived cost of refusing to donate by emphasizing the value of responding now.}

Four experimental groups were established to estimate the effects of the two intervention messages. The first group received the standard HLA match letter with neither of the intervention messages, serving as the control group (StatusQuo group). \revise{The second and third groups received the standard HLA match letter including only the matching difficulty (MatchMessage group) and early coordination (CoordMessage group) messages, respectively.} The last group received the standard HLA match letter with both intervention messages included to test the negative effect of information overload (BothMessage group).

```{r assignment}
schedule <- Schedule$new(
  here(data_root, "RCT-schedule.csv"),
  treat_labels = list(A = "StatusQuo", B = "MatchMessage", C = "CoordMessage", D = "BothMessage")
)
schedule$kable(
  title = "Assignment Schedule",
  notes = paste(
    "\\\\emph{Note}: The control group is the StatusQuo group. The experiment was not conducted during the week beginning December 27, 2021 and ending January 3, 2022 because the JMDP was closed for the New Year's holiday."
  ),
  font_size = 8
)
```

The experimental participants consisted of the recipients of the 11,154 letters sent out to matched donors between September 6, 2021 and February 27, 2022.[^duplicate] To maintain randomness to the best of the JMDP office's abilities, we assigned letters to the four experimental groups using weekly cluster randomization. Specifically, we created a cluster every seven days (a week starting from Monday) and randomly assigned one experimental group to each cluster (see Table \@ref(tab:assignment)). \revise{The assignment was designed to be balanced across weeks and months.}

[^duplicate]: In a few cases during our experimental period, the same registrant matched with more than one patient and received letters multiple times.

Before conducting the experiment, we obtained approval from the institutional review boards of the Graduate School of Economics, Osaka University (approval number: R030305) and the JMDP (approval number: JMDP2021-04) for the experimental design and empirical strategy. We did not conduct pilot studies and did not register the experiment with a pre-analysis plan.

## Data and Empirical Strategy {#data}

\revise{In the coordination data provided by the JMDP, the unit of observation was a coordination. The data included donor characteristics (sex, age, coordination experience, and residential prefecture) and information on the coordination process, such as whether each stage (response to the letter, CT, donor selection, final consent, and collection) had been completed, the number of days taken to respond to the HLA match letter, and willingness to donate at the time of response. If the coordination process was interrupted before donation, the reasons were recorded in three categories: patient-side reasons, donor non-health reasons, and donor health reasons. Unfortunately, the data contained no patient information on characteristics or prognosis.}

As additional data, we used the list of medical institutions published on the JMDP website.[^ref] This list includes complete addresses, the availability of bone marrow collection, and the availability of PBSC collection. We aggregated this list at the prefecture level and calculated the number of hospitals per 10 square kilometers.[^hospital-density] This aggregated dataset was merged with the coordination data using the prefecture as the merge key. We considered this variable as the traveling cost of coordination and donation.

[^ref]: Data source: <https://www.jmdp.or.jp/hospitals/view2/> (Accessed August 4, 2022).

[^hospital-density]: To calculate the density of the hospitals in each prefecture, we used the land area data provided by the Geospatial Information Authority of Japan.

```{r descriptive-stats, include=FALSE}
with(rct$data, prop.table(table(donate)))
with(rct$data, summary(age))
with(rct$data, prop.table(table(age < 40)))
with(rct$data, prop.table(table(male)))
with(rct$data, prop.table(table(coordinate1)))
with(rct$data, prop.table(table(prefecture)[order(table(prefecture))]))
with(subset(rct$data, prefecture %in% c("東京都", "大阪府")), table(prefecture, hospital_per_area))
with(rct$data, mean(unique(hospital_per_area)))
```

The analysis sample included 11,049 completed or interrupted coordinations involving matched donors living in Japan.[^exclude] Of these coordinations, \revise{$4.6$\% resulted in donation and $63.5$\% involved matched donors coordinating for the first time. The mean age of matched donors were 39 years (median $37.98$), and $62.4$\% of coordinations involved male donors. Compared with the overall donor pool, the analysis sample included slightly more young and male donors.}[^detail-descriptive-stats]

```{r ongoing-balance, include=FALSE}
ongoing_f <- rawdt$balance_attrition()
```

[^exclude]: One coordination involved a matched donor who lived abroad. \revise{There were 104 coordinations ongoing at the time of data collection, and their proportion was balanced across experimental groups} (`r ongoing_f[[2]]`).

[^detail-descriptive-stats]: Regarding geographic distribution, $17.1$\% of coordinations involved matched donors who lived in Tokyo or Osaka, where hospital density is well above the national average ($1.89$ and $1.36$, respectively compared with the national average of $0.21$).

The primary outcome was whether matched donors underwent CT. This outcome is important for two reasons. First, reaching the CT stage requires donors to respond to the HLA match letter, indicate their willingness to donate, and maintain their intentions. Additionally, late responses lead to coordination interruptions before the CT stage. Second, physicians can select the most appropriate donor for transplantation from among the matched donors who have undergone CT. Thus, showing up for CT represents both a costly prosocial behavior and an important practical indicator of coordination.

```{r reason-stop, include=FALSE}
mean_test <- subset(rct$data, treat == "StatusQuo") %>%
  with(prop.table(table(test)) * 100)

mean_positive <- subset(rct$data, treat == "StatusQuo") %>%
  with(prop.table(table(positive)) * 100)

mean_test_cond <- rct$data %>%
  filter(treat == "StatusQuo" & positive == 1) %>%
  with(prop.table(table(test)) * 100)

reason_classify <- rct$data %>%
  filter(positive == 1 & test == 0 & treat == "StatusQuo") %>%
  with(prop.table(table(exg_stop_test, useNA = "always")) * 100)
```

Two obstacles explain why only `r sprintf("$%1.2f$%%", mean_test["1"])` in the StatusQuo group reached CT. First, only `r sprintf("$%1.2f$%%", mean_positive["1"])` indicated their willingness to donate. Second, `r sprintf("$%1.2f$%%", mean_test_cond["0"])` of willing donors did not reach the CT stage (i.e., dropped out between the response and CT). Of these dropouts, `r sprintf("$%1.2f$%%", reason_classify["0"])` were due to donor-related reasons: \revise{health conditions such as lower back pain, scheduling conflicts, and the lack of family consent \citep{Hirakawa2018}}.[^imputed-rates] To examine how our intervention messages mitigate each obstacle, we construct two secondary outcomes: "positive intention at response" and "donor-related dropout".

[^imputed-rates]: Using values from @Hirakawa2018, `r sprintf("$%1.2f$%%", reason_classify["0"] * 0.69)` of dropouts was due to donor health conditions, `r sprintf("$%1.2f$%%", reason_classify["0"] * 0.16)` of dropouts was due to scheduling conflicts, and `r sprintf("$%1.2f$%%", reason_classify["0"] * 0.10)` of dropouts was due to the lack of family consent.

```{r summary}
rct$
  summary_experiment()$
  kable(
    title = "Summary of the Field Experiment",
    notes = paste(
      "\\\\emph{Note}: For the balance test, we regressed a covariate on treatment dummies and tested the null hypothesis that all coefficients are zero. We used standard errors clustered by the assigned week for the statistical inference. Abbreviation: PBSC = peripheral blood stem cell; BM = bone marrow."
    ),
    font_size = 8
  )
```

Table \@ref(tab:summary) summarizes our experiment. Panels A and B present the intervention and sample size for each experimental group, respectively. \revise{Panel C presents a balance test of whether the randomization was successful. Although we find statistically significant differences in average age and in the number of holidays in the assignment week and the following week across groups, these differences are either negligible in terms of standardized mean difference (average age: the CoordMessage group is only about one year younger than the StatusQuo group; see also Table A1 in Supplementary Material A) or mechanically explained by the New Year's holiday falling in the following week for one MatchMessage cluster in December (see Table \ref{tab:assignment}).}[^new-year-holidays]

[^new-year-holidays]: \revise{In Japan, the New Year's holiday is defined as December 29 to January 3, although it may be extended depending on individual circumstances.}

Although most covariates were balanced across the experimental groups, a few were unbalanced.[^cor] Therefore, in addition to a simple difference-in-means test, we estimated the following linear regression model for HLA match letter $i$ sent out in week $w$ of month $m$:

[^cor]: We confirmed that age and the number of holidays did not affect CT, which is our primary outcome, in the StatusQuo group. Therefore, the imbalance in some covariates is not a major concern.

\begin{equation}
  \begin{split}
  Y_{iwm} =& \alpha + \beta_1 \cdot \text{MatchMessage}_{wm}
  + \beta_2 \cdot \text{CoordMessage}_{wm} + \beta_3 \cdot \text{BothMessage}_{wm} \\
  &+ X'_{iwm} \gamma + u_{iwm},
  \end{split}(\#eq:reg)
\end{equation}

\noindent
where $X_{iwm}$ is a vector of observable characteristics, including donor age and the number of holidays. The parameters of interest are $(\beta_1, \beta_2, \beta_3)$.

\revise{There may be within-patient correlation because multiple donors can be matched with the same patient and physicians select one from among those who reach CT. Ideally, we would cluster standard errors at the patient level (or two-way by patient and assigned week), but we do not have patient IDs. Instead, we cluster standard errors by assigned week, the level of treatment assignment, which can also partially capture patient-level correlation when donors matched with the same patient receive letters in the same week.}

# Experimental Results {#result}
## Average Treatment Effects on Reaching CT {#main}

In this subsection, we present the estimated effects of the intervention messages on reaching the CT stage. We used a dummy variable coded one if a matched donor reached the CT stage.[^outcome-skipped-CT] \revise{As discussed in Section \ref{data}, the main barriers are low willingness to donate and donor-related dropout between the response and CT stages. We therefore expect that our intervention messages mitigate these barriers and increase the probability of reaching the CT stage.}

[^outcome-skipped-CT]: We also coded the CT dummy one if CT was skipped.

```{r test-lm}
rct$
  lm_effect("test", sample_drop = FALSE)$
  fit(scale = 100)$
  kable_reg(
    title = "Effect of the Intervention Messages on Reaching CT",
    coef_map_lm = c(
      "treatMatchMessage" = "MatchMessage group",
      "treatCoordMessage" = "CoordMessage group",
      "treatBothMessage" = "BothMessage group"
    ),
    notes = "Standard errors clustered by the assigned week are in parentheses. The unit of treatment effect is a percentage point. Covariates are sex, age, its squared term, the number of past coordinations, the number of public holidays in the assigned week and following week, the number of hospitals per 10 square kilometers, the number of hospitals with PBSC collection per 10 square kilometers, the number of hospitals with bone marrow collection per 10 square kilometers, and a dummy indicating that a candidate can skip CT. All the covariates except the sex dummy and dummy of skipped CT were demeaned."
  )
```

\revise{Table \ref{tab:test-lm} shows that the MatchMessage group increased the probability of coordinations reaching the CT stage by $1.63$ percentage point. This table reports the results of regression analyses. Because we observe some imbalance in covariates, we focus on column (3), which controls for covariates and month fixed effects. In all columns, standard errors are clustered at the week level. We obtain similar results under several alternative specifications: removing covariates (columns (1) and (2)), adjusting for multiple hypotheses testing following \citet{List2019} (Figure A1 in Supplementary Material A), and using logistic regression models (Table A2 in Supplementary Material A). Therefore, including the matching difficulty message in the HLA match letter is an effective intervention to accelerate transplant coordinations.}

```{r lm-test-decompose}
rct$
  lm_decompose_effect("test")$
  fit(scale = 100)$
  kable_reg(
    title = "Decomposition of the Effect on Reaching CT",
    outcome_label = c(
      "Positive intention at response" = "Positive intention",
      "Donor-related dropout" = "Endogenous dropout"
    ),
    coef_map_lm = c(
      "treatMatchMessage" = "MatchMessage group",
      "treatCoordMessage" = "CoordMessage group",
      "treatBothMessage" = "BothMessage group"
    ),
    notes = "Standard errors clustered by the assigned week are in parentheses. The unit of treatment effect is a percentage point. The outcome ``Donor-related dropout'' is a dummy variable that takes a value of 1 if candidates responded with a willingness to donate but did not reach the CT stage for donor-side health and non-health reasons. Covariates are gender, age and its squared term, the number of past coordinations, the number of public holidays in the assigned week and the following week, the number of hospitals per 10 square kilometers, the number of hospitals with PBSC collection per 10 square kilometers, the number of hospitals with BM collection per 10 square kilometers, and a dummy indicating that the candidate skipped CT. All the covariates except the gender dummy and dummy of skipped CT were demeaned.",
    font_size = 8
  )
```

As mentioned previously, \revise{the intervention was expected to increase CT completion through two channels: increasing positive intention at response and reducing donor-related dropout (health and non-health) between the response and CT stages. We therefore decomposed the message effects into these two components (Table \ref{tab:lm-test-decompose}). Overall, the evidence is suggestive: the intervention broadly worked as expected, except for the CoordMessage group, which may have reduced the willingness to donate.}

\revise{This table suggests that mechanisms differed across the intervention groups, though statistical tests are not robust. In the MatchMessage group, the willingness to donate rose by $1.27$ percentage points (column (3)) and donor-related dropout fell by $0.93$ percentage points (column (6)), with the former larger in magnitude. By contrast, the CoordMessage and BothMessage groups mainly reduced donor-related dropout (e.g., $1.92$ percentage points in the BothMessage group, significant at 10\%; column (6)) but did not sufficiently increase the willingness to donate, which limited their effect on reaching CT. Taken together, the matching difficulty message may help improve the willingness to donate, while the early coordination message may prevent donor-related dropout.}

## Effect on Response Speed {#response-speed}

\revise{Given that early responses accompanied by positive intention to donate had a higher probability of reaching CT (see Figure \ref{fig:speed-CT-cond-response}), we examined how our intervention messages affected the response speed. In particular, we asked whether the early coordination message—received by the CoordMessage and BothMessage groups—would at least encourage earlier responses, even though those groups did not show an overall increase in willingness to donate.}

```{r cumulative-response, fig.cap = "Cumulative Rate of Positive Intention at Response by Treatment \\newline \\emph{Note}: We excluded those who skipped CT. We only show the cumulative response rates up to 25 days after the HLA match letter was sent because there was no remarkable change in the response rate thereafter."}
rct_noskip$
  flow("positive", sample_drop = FALSE)$
  plot_cumulative(
    upper_days = 25,
    xbreaks = seq(0, 100, by = 7),
    ylim = c(0, 55),
    xlab = "Days after the HLA match letter being sent",
    ylab = "Cumulative rate of\npositive intention at response (%)",
    base_size = 25
  )
```

\revise{We obtain two findings about timing of positive intention expression from Figure \ref{fig:cumulative-response}. First, through the first two weeks (within and shortly after the JMDP's requested 7-day response period), the cumulative rates of the intervention groups were almost identical but lower than those of the StatusQuo group. This suggests that the early coordination message may not have had the expected effect. Second, after 14 days, the cumulative rates of the MatchMessage group became higher than that of the StatusQuo group. Thus, the willingness to donate of the MatchMessage group may have increased but this may have slowed response speed.}

\revise{To explain this, Figure A2 in Supplementary Material A shows how the timing of intention expression differs between the StatusQuo and MatchMessage groups. In the MatchMessage group, fewer declined within 0--7 days and more expressed positive intention after 7 days; slightly more also declined after 7 days.}[^another-dist] \revise{This pattern suggests that some candidates who would have declined early without the intervention had intentions that were changeable in response to it; after coordinating with family or workplace, they later expressed willingness to donate. A response delayed by about 7 days relative to the JMDP's requested window is unlikely to affect transplant outcomes, given a median of 125 days from the HLA match letter to donation \citep{Hirakawa2018}.}[^another-evidence]

[^another-dist]: Compared with the StatusQuo group, the distributions of the CoordMessage and BothMessage groups also change similarly, but the change is less pronounced than in the MatchMessage group (Figures A3 and A4 in Supplementary Material A).

[^another-evidence]: Given that 58\% of coordinations interrupted by patient death occur within 200 days \citep{Hirakawa2018}, the impact of response delay seems to be small.

```{r lm-positive-time-decompose}
rct$
  flow(outcome = "positive", sample_drop = FALSE)$
  lm_time_segment(cut_days = c(7, 13))$
  fit(scale = 100)$
  kable_reg(
    title = "Effect on Response Speed with Positive Intention",
    coef_map_lm = c(
      "treatMatchMessage" = "MatchMessage group",
      "treatCoordMessage" = "CoordMessage group",
      "treatBothMessage" = "BothMessage group"
    ),
    notes = "Standard errors clustered by the assigned week are in parentheses. The unit of treatment effect is a percentage point. The outcome is a dummy variable that takes a value of 1 if the candidate responded with positive intention within a specified time window after the HLA match letter being sent. Covariates are gender, age and its squared term, the number of past coordinations, the number of public holidays in the assigned week and the following week, the number of hospitals per 10 square kilometers, the number of hospitals with PBSC collection per 10 square kilometers, and the number of hospitals with BM collection per 10 square kilometers. All the covariates were demeaned.",
    font_size = 8
  )
```

\revise{We verified these findings by regression (Table \ref{tab:lm-positive-time-decompose}). In all intervention groups, positive intention was lower in the 0--7 day window but higher in the 8--13 day window than in the StatusQuo group; the sum of these effects is close to zero, suggesting no difference in cumulative rate up to 14 days. The MatchMessage group showed an increase in the 14+ day window, consistent with Figure \ref{fig:cumulative-response}. Although none of these differences were statistically significant, the pattern of point estimates suggests that the early coordination message did not have the intended effect on response speed, and that the matching difficulty message may have increased willingness but at the cost of slower response.}

# Policy and Welfare Implications of the Intervention {#discussion}

To discuss the policy and welfare implications of the intervention, we examine treatment effects on the post-CT stages: donor selection, final consent, and collection (donation). Because a physician selects one best donor from all who reach CT, welfare depends on both the number and the quality of donors in the pool. We argue that the intervention may have improved transplant quality despite null quantity effects and that targeting clinically valuable donors could improve welfare.

We first report treatment effects on post-CT outcomes. As a benchmark, when the JMDP sends HLA match letters to 10 donors and all reach CT, selection and donation rates reach a maximum of 10\%.[^other-benchmark] In the StatusQuo group, the selection and donation rates are $6.19$\% and $4.5$\%, respectively; the gap reflects dropout due to patient deterioration or failure to obtain final consent. Our intervention had no statistically significant effects on post-CT outcomes in terms of quantity (Figure A2 and Table A3 in Supplementary Material A). The estimated effects on all three stages are smaller than on the CT stage: donor selection and donation in the MatchMessage group fell by $0.29$ and $0.12$ percentage points, respectively, which were not statistically significant.[^logit]

[^other-benchmark]: When desirable donors are not found through the CT stage or when few matched donors complete the CT stage, a physician may be unable to find the best donor among matched donors. In this case, selection and donation rates fall below 10\%. Conversely, when the JMDP office sends HLA match letters to fewer than 10 matched donors, selection and donation rates exceed 10\%.

This need not imply, however, that patient welfare did not improve. Because more donors reached CT in the MatchMessage group, physicians could choose from a larger pool—potentially raising transplant quality even without raising quantity.

[^logit]: Logistic regression yielded similar results (see Table A4 in Supplementary Material A).

This view is supported by heterogeneous treatment effects by gender, age, and past coordination experience (Figure A3 in Supplementary Material A). The MatchMessage treatment encouraged young men with past coordination experience to reach CT (7 percentage points; $p = 0.05$) and increased their probability of being selected as the best donor (5 percentage points; $p < 0.01$). This result is desirable given evidence that young male donors improve patient prognosis \citep{Loren2006, Arai2016, Kollman2016, Shinohara2017}.[^our-data-analysis] The MatchMessage treatment may thus improve transplant quality by selectively attracting the most clinically valuable donors.

[^our-data-analysis]: Using those in the StatusQuo group who reached the CT stage, we examine which characteristics make candidates more likely to be selected as the best donor (Table A5 in Supplementary Material A). As a result, young men were more likely to be selected as the best donor, consistent with medical findings. We also find that donor selection and donation were unrelated to the speed of reaching the CT stage (those who responded to the HLA match letter quickly or could skip CT).

At the same time, the MatchMessage treatment promoted older men matched for the first time and young women with past coordination experience to reach CT, but did not increase their probability of selection, suggesting welfare costs for these donors.[^implication-to-ATE] From the perspectives of welfare and cost-effectiveness, interventions targeting young men may therefore be more appropriate than a uniform message to all matched donors.

[^implication-to-ATE]: The MatchMessage group changed the behavior of both those likely to be selected as donors and those unlikely to be selected, resulting in average treatment effects on donor selection and donation close to zero. This reflects the result that the MatchMessage treatment increased coordinations interrupted for exogenous reasons (donor health reasons such as disqualification because of the CT results and patient-side reasons) among those who reached the CT stage (Table A6 in Supplementary Material A).

# Conclusions {#conclusion}

This study examined how information provision at the time of matching affects donor availability in stem cell transplantation. \revise{Our} field experiment showed that providing information on the limited number of HLA-compatible donors per patient (i.e., the matching difficulty message) increased the probability of reaching CT \revise{by $1.63$ percentage points after adjusting for covariates and month fixed effects. Given the baseline CT completion rate of $22.25$\% in the StatusQuo group, this implies a $7.3\% (= 1.63/22.25)$ increase. This result is robust to several other checks (e.g., adjusting for multiple hypotheses testing across treatment groups, and using logistic regression models) albeit without a prior pilot study or preregistration. Overall, the message expands the pool from which physicians can select the best donor.}

\revise{To evaluate the cost-effectiveness, we translate the effect of the matching difficulty message into an equivalent number of additional donor registrations. A $7.3$\% increase in CT completion rate is equivalent to a $7.3$\% increase in matched donors.}[^proof] \revise{Since 40\% of registrants become matched donors, $224,000$ of the current $560,000$ registrants are potential matched donors.}[^data1] \revise{Therefore, the message effect implies an increase of $16,352$ ($= 224,000 \times 0.073$) in matched donors, or an increase of $40,880$ ($= 560,000 \times 0.073$) in registrants.}

\revise{This equivalence has direct policy relevance. In the current JMDP donor pool, $100,000$ donors in their 50s will exit within the next five years because of the age limit for donation (54 years).}[^data2] \revise{Since the message effect is equivalent to recruiting $40,880$ new donors, the matching difficulty message can therefore offset approximately $40.9\%$ ($= 40,880/100,000$) of the negative impact of this donor-pool shrinkage.}

\revise{Meanwhile, donor recruitment is costly. While the cost required to add one donor registration at the JMDP is unknown, NMDP spends approximately USD 150 per added registration.}[^data3] \revise{If the JMDP bears a similar cost, recruiting $40,880$ registrants would cost approximately USD $6.132$ million. Thus, adding the matching difficulty message could be a more cost-effective measure than recruiting new donors to address the shrinking donor pool.}

[^proof]: Let $N_m$ be the number of registrants who start the coordination process. Let $N_1(d)$ be the number of potential donors who reach CT under treatment $d$. Then, $N_1(d) = p(d)N_m$ holds, where $p(d)$ is the probability of reaching CT under treatment $d$. Note that $d = 1$ and $d = 0$ represent the treatment and control groups, respectively. We solve $N_1(1) = p(0)[N_m + \Delta N_m]$ for $\Delta N_m$, where $\Delta N_m$ represents the increase in registrants who start coordination. Therefore, we obtain $[p(1) - p(0)]/p(0) = \Delta N_m/N_m$.

[^data1]: The cumulative number of registrants since the JMDP's establishment is $980,000$. Among these registrants, $390,000$ have become potential donors who started the coordination process. Therefore, 40\% of registrants become potential donors who start coordination. Data source: <https://www.bs.jrc.or.jp/bmdc/donorregistrant/m2_03_00_statistics.html> (Accessed December 8, 2024).

[^data2]: <https://www.jmdp.or.jp/about/read/number/> (Accessed December 8, 2024).

[^data3]: <https://fundraise.nmdp.org/index.cfm?fuseaction=cms.page&id=1203&eventID=675> (Accessed March 29, 2025).

\revise{The matching difficuly message was attenuated when we simultaneously presented the early coordination message, possibly due to information overload. This suggests that effective behavioral information should be conveyed in a simple manner. Moreover, given the heterogeneous effects documented in the Section \ref{discussion}---where only young male donors both reached CT at higher rates and were more likely to be selected---targeted interventions directed at this subgroup may be more cost-effective than a uniform intervention.}

Finally, \revise{our intervention may apply to contexts beyond stem cell transplantation. The matching difficulty message emphasizes the scarcity of potential cooperators in public-goods settings. In our context, it may have corrected donors' overestimation of avairable substitutes and reduced motivational crowding-out. Alternatively, it may have made the rarity of cooperative opportunities more salient. Although our data cannot identify the dominant mechanism, communicating scarcity is likely to be effective in other cooperative settings such as rare-blood donation.}