---
title: |
  Exploring Information Provision to Promote Stem Cell Donation:
  Evidence from a Field Experiment of the Japan Marrow Donor Program
author:
  - name: Hiroki Kato
    affil-id: a
    note: "Corresponding author. E-mail address: hkato.econ@aoyamagakuin.jp"
  - name: Fumio Ohtake
    affil-id: b
    note: "E-mail address: ohtake@cider.osaka-u.ac.jp"
  - name: Saiko Kurosawa
    affil-id: c
    note: "E-mail address: skurosaw@inahp.jp"
  - name: Kazuhiro Yoshiuchi
    affil-id: d
    note: "E-mail address: kyoshiuc-tky@umin.ac.jp "
  - name: Takahiro Fukuda
    affil-id: e
    note: "E-mail address: tafukuda@ncc.go.jp"
affiliations:
  - id: a
    name: School of International Politics, Economics and Communication, Aoyama Gakuin University, 4-4-25 Shibuya, Shibuya-ku, Tokyo 150-8366, Japan
  - id: b
    name: Center for Infectious Disease Education and Research (CiDER), Osaka University, 1-10 Yamadaoka, Suita, Osaka 565-0871, Japan​
  - id: c
    name: Department of Oncology, Ina Central Hospital, 1313-1, Koshirokubo, Ina, Nagano 396-8555, Japan
  - id: d
    name: Graduate School of Medicine, The University of Tokyo, 7-3-1 Hongo, Bunkyo, Tokyo 113-8655, Japan
  - id: e
    name: Department of Hematopoietic Stem Cell Transplantation, National Cancer Center Hospital, 5-1-1 Tsukiji, Chuo-ku, Tokyo 104-0045, Japan
abstract: |
  \revise{In stem cell transplantation, registered potential donors may refuse to donate when matched with patients, causing supply shortages.} Thus, preventing such donor \revise{dropout} is crucial. To address this issue, we developed a behavioral intervention comprising adding messages into the letters sent when donors are matched with patients. We then conducted a field experiment to verify the effect of our intervention. The results demonstrate that \revise{our} behavioral interventions can prevent registered donor \revise{dropout} and increase donor availability for transplantation. Specifically, the message emphasizing the limited number of compatible donors per patient increased the probability of donors completing the confirmatory typing \revise{stage} by 11.5%. \revise{Since physicians can choose the best donor for proceeding to donation from those who complete the confirmatory typing stage, this message effect increases donor availability for transplantation.}

  \vspace{0.5em}
  \noindent
  \textit{Keywords}: prosocial behavior, field experiment, free-riding, information provision, Japan Marrow Donor Program, stem cell transplantation

  \vspace{0.5em}
  \noindent
  \textit{JEL classification}: D64, D90, H41, I11
acknowledgements: |
  We would like to thank the Japan Marrow Donor Program office for managing the field experiment and providing us with the data. We thank Tsuneaki Hirakawa and two anonymous reviewers for their helpful comments and suggestions. This study was conducted with the approval of the institutional review boards of the Graduate School of Economics, Osaka University (approval number: R030305-2) and the Japan Marrow Donor Program (approval number: JMDP2021-04).

  \vspace{0.5em}
  \noindent
  Funding: This work was supported by the Japan Society for the Promotion of Science [grant number 20H05632] and the Ministry of Health, Labour and Welfare [grant number 19FF1001].

  \vspace{0.5em}
  \noindent
  Declarations of interest: none.
ai-declaration: |
  During the preparation of this work, we used Claude to improve the readability and language of the manuscript. After using these tools, we carefully reviewed and edited the content as needed and take full responsibility for the content of the published article.
bibliography: biblio.bib
biblio-style: elsarticle-harv.bst
output:
  bookdown::pdf_document2:
    latex_engine: pdflatex
    template: template/my-template-science-direct.tex
    keep_tex: true
    toc: false
    number_sections: true
    citation_package: natbib
base-strech: 2
fontsize: 12pt
---

```{r include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  error = FALSE,
  message = FALSE,
  dev = "pdf",
  fig.width = 15,
  fig.height = 10,
  fig.pos = "t",
  out.extra = ""
)
```

```{r option, include = FALSE}
options(
  knitr.table.format = "latex",
  knitr.kable.NA = "",
  kableExtra.auto_format = FALSE,
  modelsummary_factory_latex = "kableExtra",
  modelsummary_get = "broom"
)
```

\clearpage

# Introduction {#intro}

\revise{Similar to organ transplantation,} allogeneic hematopoietic stem cell transplantation (HSCT) faces supply shortages in many countries. \revise{To resolve this issue, particularly in the context of organ transplantation from deceased donors,} many studies have examined interventions to increase donor registrations [for example, @Kessler2012]. \revise{In addition, HSCT faces another challenge: registered donors may refuse to donate when matched with patients} [for example, @Switzer2018; @Haylock2024]. \revise{Thus, developing interventions to mitigate such donor dropout is crucial. This study examines how behavioral interventions at the time of matching can prevent donor dropout and resolve the supply shortage issue.}

HSCT has the lowest relapse rate among all treatments for leukemia and other blood cancers. In this treatment, (1) anticancer drugs or radiation are used to kill tumor cells and (2) healthy hematopoietic stem cells are transplanted from a donor. The transplantation requires that the donor's white blood cell type (HLA) completely or partially matches the patient's HLA.[^hapro] \revise{When patients cannot find a compatible donor among their relatives, who are more likely to be matched, they can search for unrelated donors through the Japan Marrow Donor Program (JMDP).}[^match-probability]

[^hapro]: When HLA-identical or partially matched unrelated donors are unavailable, several options exist. The first option is haploidentical stem cell transplantation in which stem cells are transplanted from a close relative with semi-matched HLA. The second option is cord blood transplantation in which stem cells are transplanted from the umbilical cord or placenta of pregnant women. The HLA requirements for these transplants are weaker than those for bone marrow (or peripheral blood stem cell (PBSC)) transplants between unrelated individuals. Notably, in Japan, bone marrow and PBSC transplants between unrelated individuals accounted for 20% of all transplants in 2021 [@JDCHCT2022].

[^match-probability]: \revise{While the probability of a complete match between two randomly selected individuals is less than 1\%, the probability of a full match between siblings is 30\%.}

However, only \revise{60\%} of the patients registered with the JMDP \revise{end up receiving transplantation because of the time it takes to complete the process} [@Hirakawa2018].[^fact] \revise{One major factor is donor dropout before the confirmatory typing (CT) stage, which examines the donor's eligibility for transplantation.} Indeed, @Hirakawa2018 reported that \revise{56\%} of transplant coordinations do not reach the CT stage for donor-related reasons. Since physicians select the best donors to proceed to donation from candidates who undergo CT, donor \revise{dropout} before the CT stage reduces donor availability and can extend the time to transplantation. \revise{Other registries also face the same problem} [@Switzer2003; @Switzer2004; @Balassa2019; @Hamed2023; @Haylock2024]. Thus, we should explore and adopt interventions to increase the number of donor candidates who reach CT, thereby improving donor availability, while maintaining individuals' autonomy.[^donor-quantity]

[^fact]: According to @Hirakawa2018, \revise{between 2004 and 2013}, the median length of the transplantation process through the JMDP was 146 days (approximately five months) and 58\% of patients who died (or had their transplantation interrupted because of poor health) passed away within 200 days.

[^donor-quantity]: In the JMDP, the benefit of expanding the donor pool is limited because most patients do eventually find donor candidates [@Takanashi2016].

In this study, we \revise{developed information} interventions to prevent registered donor \revise{dropout}, that is, increase the number of donor candidates who progress to the CT stage, in collaboration with the JMDP. The interventions added messages to the letters sent when donors are matched with patients. This letter informs matched donors that they are compatible with a specific patient requiring HSCT owing to their matching HLA and requests their participation in the transplantation coordination. Upon responding to this so-called "HLA match letter," matched donors indicate their willingness to donate and proceed to the next coordination stage, namely, the CT stage. \revise{We developed two intervention messages---\emph{matching difficulty} and \emph{early coordination}---based on insights from behavioral economics, the details of which are explained in Section} \@ref(design). In collaboration with the JMDP, we then conducted a field experiment to examine the effect of our intervention on progressing the CT stage. Our experimental \revise{participants comprised} recipients of the 11,154 HLA match letters that were sent between September 2021 and February 2022.

Using coordination data provided by the JMDP, we demonstrate that our intervention increases the probability of donors reaching the CT stage. Specifically, the \revise{matching difficulty} message increased the likelihood of donors reaching CT by 12%. \revise{This message informs matched donors that the number of HLA-compatible donors per patient is limited and emphasizes the scarcity of compatible donors.} A back-of-the-envelope calculation suggests that this positive effect may partially mitigate the negative impact of the shrinkage of the future donor pool due to aging (as discussed in Section \@ref(conclusion)). However, the early coordination message did not have the intended effect of \revise{increasing} the probability of donors reaching the CT stage. Our field experiment suggests that messages regarding patient compatibility can prevent donor \revise{dropout}.

\revise{This study contributes to a series of studies on donor engagement. Many studies have examined interventions increasing the number of donors in the context of organ donation and blood donation. Such interventions primarily include providing monetary or material benefits \citep{Lacetera2010a, Kessler2012, Li2013, Lacetera2014, Stoler2017} and providing information on altruistic benefits and peer effects \citep{Li2016, Sallis2018, Robitaille2021, Goette2020, Goette2024}.}[^Heger2020] \revise{While our intervention is of the latter type, its purpose differs significantly. Our study aims to prevent the dropout of registered donors rather than increasing supply quantity. This creates a difference in the target population between our intervention and previous studies. Previous studies targeted the general population with various preferences. By contrast, since our experimental participants are registered donors who matched with patients, our target population contains a higher proportion of altruistic individuals than the general population \citep{Bergstrom2009, Ohtake2020}. Few studies are similar to ours. \citet{Switzer2018} examined the effect of informing fully HLA-matched donors that they had been fully matched with patients. This intervention is very similar to ours in terms of timing and content of interventions. However, their study compared fully matched donors with partially matched donors; therefore, it was not a randomized controlled trial. \citet{Haylock2024} examined the effect of commitment (e.g., planning when to be available) before being matched with patients. Thus, the timing of this intervention is different from ours. To the best of our knowledge, we document the effects of information provision at the time of matching with patients among an altruistic population through the first randomized controlled trial.}[^other-context]

[^Heger2020]: \revise{\citet{Heger2020} showed that establishing registries that collect potential donors beforehand is effective in increasing the supply of blood donation. In the case of HSCT, such registries already exist. Our motivation is to prevent dropout among registered donors when they are matched with patients.}

[^other-context]: Previous studies have also examined the effects of behavioral interventions such as message and information provision in health and medical policy contexts, including vaccination [for example, @Dai2021; @Milkman2021], breast cancer screening [@Bertoni2020], and cord blood transplantation [@Grieco2018]. \revise{Unlike our study, these studies targeted the general population.}

\revise{More broadly, our paper also contributes to the literature on social norm messages. Social norm messages provide information on the actions that many people take, that is, social norms. According to behavioral economic theories, individuals want to act in accordance with social norms \citep{Bernheim1994, Bursztyn2017}. In the context of charitable giving, presenting information that many people have donated has been shown to promote individual contributions \citep{Shang2009, Kessler2017}. However, according to the standard economic theory of public goods, such information may provide individuals with incentives to free-ride on others' contributions, suppressing individual contributions. Indeed, \citet{Lau2019} and \citet{Galizzi2022} showed that information about high flu vaccination coverage may reduce individuals' willingness to be vaccinated. Similarly, in Wikipedia's donation campaigns, providing information that only a few people have donated increases contributions \citep{BIT2024}. Our study shows that information indicating that only a few people can contribute (the matching difficulty message) is effective in altruistic groups. This result suggests that the effectiveness of social norm messages varies by context and group characteristics, providing new insights into the heterogeneous effects of such messages.}[^Brekke2011]

[^Brekke2011]: \revise{\citet{Brekke2011} showed that free-riding in public goods provision is eliminated when altruistic groups are formed through individual choice. This study also provides important implications for the heterogeneous effects of social norm messages.}

The remainder of this paper is organized as follows. Section \@ref(experiment) provides an overview of the coordination process of the JMDP and describes our field experiment. Section \@ref(result) presents the results of our experiment. \revise{Section \ref{discussion} discusses the welfare implications. Finally, Section \ref{conclusion} concludes.}

# Field Experiment {#experiment}

```{r library, include=FALSE}
library(here)
library(xfun)
source(here("R/R6_RawData.r"))
source(here("R/R6_Schedule.r"))

options(
  knitr.kable.NA = "",
  modelsummary_stars_note = FALSE
)

data_root <- "data"
```

## Background: Coordination Process of the JMDP {#background}

```{r flow-chart-coordination, fig.cap = "Flowchart of the JMDP Coordination Process and Sample Selection \\newline \\emph{Note}: The numbers in this figure are based on our experimental data."}
knitr::include_graphics(here("image/flowchart.pdf"))
```

To allow readers to better understand our intervention and data, we first outline the coordination process leading to \revise{stem cell donation through the JMDP} (see Figure \@ref(fig:flow-chart-coordination) for a visual overview). \revise{Individuals eligible to register as donors with the JMDP must be between 18 and 54 years and in good health.}[^weight] \revise{Individuals who can actually donate must be between 20 and 55 years. As of December 2024, approximately 560,000 donors were registered with the JMDP. Of these, 240,000 (42\%) were under 40 years and 280,000 (50\%) were male.}[^reference]

[^weight]: \revise{Additionally, men must weigh at least 45 kg and women must weigh at least 40 kg. See \url{https://www.jmdp.or.jp/reg/requirement/} (Japanese; Accessed October 24, 2025).}

[^reference]: \revise{Data source: \url{https://www.bs.jrc.or.jp/bmdc/donorregistrant/m2_03_00_statistics.html} (Japanese; Accessed October 24, 2025).}

\revise{After a patient's physician registers the patient with the JMDP, the JMDP compiles a list of candidates based on the physician's criteria (primarily HLA compatibility). The physician selects up to 10 matched donors from this list. Subsequently,} the JMDP office sends each matched donor an HLA match letter, recommending a response within seven days.[^SMS] \revise{Our experimental participants are all matched donors who received HLA match letters between September 2021 and February 2022.} Upon responding, matched donors complete a medical questionnaire and indicate their willingness to donate.

[^SMS]: Simultaneously, the JMDP office sends a \revise{short message} to matched donors informing them that the JMDP has sent the HLA match letter.

A matched and willing donor undergoes CT within approximately one month. CT confirms whether the matched donor meets the criteria for transplantation set by the JMDP. The transplantation coordinator delegated by the JMDP explains the details of the donation process and asks matched donors and their families about their willingness to donate. Thereafter, the coordinating physician conducts medical interviews, examinations, and blood tests, including those for infectious disease markers. Collection methods (bone marrow or PBSC collection) are also determined based on the preferences of the matched donor and coordinating physician. CT can be skipped when \revise{a matched donor is eligible based on a previous CT result within one year}.

\revise{The patient's physician selects the best donor from matched donors who have reached CT. When the JMDP determines that a matched donor is eligible based on their CT results, the physician receives those results and must classify the donor into three categories within 40 days: best donor, backup donor, or rejection. The physician selects only the best donor to proceed to final consent and donation but can select up to four backup donors, who are ranked by priority. When coordination with the best donor is interrupted, the highest-priority backup donor becomes the best donor.}[^late-arrival]

[^late-arrival]: \revise{Even after selecting the best donor, if the JMDP determines that additional matched donors are eligible, the physician must classify them as backup donors or rejections within 40 days. However, if the best donor has not yet provided final consent, the physician can change the best donor to a later-arriving matched donor.}

\revise{The best} donor must provide final consent after being informed of their selection by the coordinator and coordinating physician. Simultaneously, a representative of the donor's family must provide consent to the donation. After final consent is obtained, the donor cannot withdraw their decision to donate. They then undergo a surgical procedure to collect stem cells. The time from CT to collection is approximately three to four months. Importantly, \revise{throughout the coordination process}, a matched donor cannot access any information about the matched patient (e.g., the number of other available potential donors), nor can the matched donor obtain this information from the transplantation coordinator or coordinating physician.

## Experimental Design {#design}

```{r list-message}
message_dt <- tribble(
  ~treat, ~contents,
  "Standard message",
  "We inform you that your HLA type (white blood cell type) matches that of a patient in our registry, and you have been selected as one of our potential donors. We are contacting you to ask if you would like to proceed with further testing and interviews for donation. Please read the enclosed materials carefully, consider whether coordination is possible, and return the form within seven days of receiving this information. [\\emph{Insert intervention messages here}] If we proceed with coordination after receiving your response, a coordinator will contact you by phone to discuss the details of your request.",
  "\\revise{Matching difficulty} message",
  "The number of registered donors whose HLA type matches that of a single registered patient is one in hundreds to tens of thousands. While we may find multiple potential donors, we hope you understand that the number is limited.",
  "Early coordination message",
  "Approximately 60\\% of patients receive a transplant through the JMDP. The earlier a donor is found, the higher this rate can be increased."
)

message_dt %>%
  knitr::kable(
    caption = "List of Intervention Messages",
    col.names = c("Message", "Content"),
    align = "ll",
    booktabs = TRUE,
    linesep = "",
    escape = FALSE
  ) %>%
  kableExtra::kable_styling(font_size = 8) %>%
  kableExtra::group_rows("Intervention message", 2, 3) %>%
  kableExtra::column_spec(2, width = "40em") %>%
  kableExtra::footnote(
    general_title = "",
    general = "\\\\emph{Note}: Translated by the authors.",
    threeparttable = TRUE,
    escape = FALSE
  )
```

Our intervention involved adding two messages into the HLA match letter.[^pressure] Table \@ref(tab:list-message) lists the content of the standard letter and the two intervention messages. The JMDP also encloses a handbook that describes the coordination process as well as the medical questionnaire and donor consent form.[^ref-handbook] \revise{We developed two messages based on the finding from our preliminary survey that the target population for our intervention includes more altruistic individuals than the general population} [@Ohtake2020].

[^pressure]: In designing our intervention messages, we were careful to avoid placing undue psychological pressure on potential donors. Specifically, we avoided using language that sounded like an appeal. Additionally, we only used information publicly available from the JMDP. Finally, the risks of transplantation were explained in a typical manner. The intervention message was approved by the institutional review boards of the Graduate School of Economics, Osaka University and the JMDP.

[^ref-handbook]: The handbook can be found at [https://www.jmdp.or.jp/pdf/en/DonorHandBook201708.pdf](https://www.jmdp.or.jp/pdf/en/DonorHandBook201708.pdf) (Accessed December 9, 2024).

The \revise{matching difficulty} message emphasizes the low number of matched donors per registered patient. If other potential donors with the same HLA type are in the pool, one donor's donation can be substituted with that of another compatible donor. Additionally, multiple matched donors (up to 10) can be simultaneously matched with a single patient. Therefore, transplantation through the JMDP \revise{represents a public good} [@Bergstrom2009]. \revise{Therefore, purely altruistic individuals who care about public good outcomes may free-ride on the provision by alternative donors.}[^size-pure-altruist] In fact, @Kurosawa2022 interviewed previously matched donors and found that those with low donation intention felt that they were "one of several donors." This implies that some potential donors with low intention recognize that their donation could be substituted by others. \revise{Additionally, since matched donors cannot know the number of substitutable donors, this uncertainty may reduce their willingness to donate} [@Exley2016]. \revise{Therefore, the matching difficulty message emphasizes the small number of possible substitutes and is expected to discourage free-riding and increase the willingness to donate.}[^rarelity]

[^size-pure-altruist]: \revise{\citet{Ohtake2020} found that 22\% of registrants had pure altruistic preferences.}

[^rarelity]: Alternatively, the \revise{matching difficulty} message makes the rarity of the opportunity to donate more salient, which may change donor behavior.

\revise{The matching difficulty message is related to social norm messages. According to behavioral economic theories, individuals want to act in accordance with social norms \citep{Bernheim1994, Bursztyn2017}. Thus, the matching difficulty message, which indicates that only a few people can contribute, discourages the willingness to donate if matched donors have conformity and social image concerns. However, according to the standard economic theory of public goods, such information may provide individuals with incentives to free-ride on others' contributions, suppressing individual contributions. As stated above, if this is the case, the matching difficulty message increases the willingness to donate.}

```{r experiment-data, include=FALSE}
rawdt <- RawData$new(
  here(data_root, "shape.csv"),
  treat_vars = "treat",
  treat_levels = LETTERS[1:4],
  treat_labels = c("StatusQuo", "MatchMessage", "CoordMessage", "BothMessage")
)

rawdt$add_cond_study_sample("prefecture != '海外'")
rawdt$add_cond_study_sample("ongoing == 0")

rawdt_noskip <- rawdt$clone()
rawdt_noskip$add_cond_study_sample("skip_test == 0")
```

```{r rct-setup, include=FALSE}
intervention <- list(
  "Standard message" = c(StatusQuo = "X", MatchMessage = "X", CoordMessage = "X", BothMessage = "X"),
  "\\revise{Matching difficulty} message" = c(StatusQuo = "", MatchMessage = "X", CoordMessage = "", BothMessage = "X"),
  "Early coordination message" = c(StatusQuo = "", MatchMessage = "", CoordMessage = "X", BothMessage = "X")
)

endpoint <- list(
  reply = "Response",
  positive = "Positive intention",
  test = "CT",
  candidate = "Donor selection",
  consent = "Final consent",
  donate = "Donation"
)

# main sample
rct <- rawdt$RCT()
rct$add_intervention(intervention)
rct$add_outcome(endpoint)
rct$set_default_cluster("RCTweek")
rct$set_default_se_type("stata")

# robust sample (remove those who skipped the CT)
rct_noskip <- rawdt_noskip$RCT()
rct_noskip$add_intervention(intervention)
rct_noskip$add_outcome(endpoint)
rct_noskip$set_default_cluster("RCTweek")
rct_noskip$set_default_se_type("stata")
```

```{r speed-CT-cond-response, fig.cap = "Binned Scatter Plot of CT vs. Response Speed among Those Who Responded with Positive Intention. \\newline \\emph{Note}: We used those who responded with positive intention to donate in the control group (StatusQuo group). The dashed line represents nonparametric fitting. The solid line represents a fitted line of the logistic regression."}
positive_dt <- rct$data %>%
  filter(positive == 1 & 0 < days_reply & treat == "StatusQuo")

plotdt <- positive_dt %>%
  mutate(ntile = ntile(days_reply, 20)) %>%
  group_by(ntile) %>%
  summarize(
    median_day = (max(days_reply) + min(days_reply)) / 2,
    mean_ct = mean(test)
  )

plotdt %>%
  ggplot(aes(x = median_day, y = mean_ct)) +
    geom_point(color = "grey40", size = 3) +
    geom_smooth(
      aes(x = days_reply, y = test),
      data = positive_dt,
      method = "glm",
      method.args = list(family = "binomial"),
      se = FALSE,
      alpha = 0.2,
      color = "black",
      linetype = 1
    ) +
    geom_smooth(
      aes(x = days_reply, y = test),
      data = positive_dt,
      se = FALSE,
      alpha = 0.2,
      color = "black",
      linetype = 2
    ) +
    labs(x = "Response days", y = "Proportion of Reaching CT", shape = "Outcome") +
    my_theme_classic(size = 25)
```

The early coordination message emphasizes that early coordination would increase the patient's transplantation rate. Our preliminary survey found that registered donors who place higher value on immediate outcomes (higher time discount rates) were more likely to proceed with donations [@Ohtake2020]. Motivated by this finding, we created a message that emphasized the value of responding now, rather than postponing the response. \revise{Conversely, this message increases the perceived cost of refusing to donate \citep{Haylock2024}.}[^perceived-cost] Furthermore, earlier responses are associated with higher rates of reaching the CT stage (\revise{Figure} \@ref(fig:speed-CT-cond-response)). Therefore, this message is expected to \revise{encourage early responses and} increase the probability of donors undergoing CT.

[^perceived-cost]: \revise{\citet{Haylock2024} showed that notifying registries in advance of the period during which donation is possible functions as a commitment and increases the perceived cost of refusing to donate.}

Four experimental groups were established to estimate the effects of the two intervention messages. The first group received the standard HLA match letter with neither of the intervention messages, serving as the control group (\revise{StatusQuo} group). The second and third groups received the standard HLA match letter including only the \revise{matching difficulty} and early coordination messages, respectively (\revise{MatchMessage} and \revise{CoordMessage} groups, respectively). The last group received the standard HLA match letter with both intervention messages included to test the negative effect of information overload (\revise{BothMessage} group).

```{r assignment}
schedule <- Schedule$new(
  here(data_root, "RCT-schedule.csv"),
  treat_labels = list(A = "StatusQuo", B = "MatchMessage", C = "CoordMessage", D = "BothMessage")
)
schedule$kable(
  title = "Assignment Schedule",
  notes = paste(
    "\\\\emph{Note}: The control group is the StatusQuo group. The experiment was not conducted during the week beginning December 27, 2021 and ending January 3, 2022 because the JMDP was closed for the New Year's holiday."
  ),
  font_size = 8
)
```

\revise{The experimental participants consisted of the recipients of the 11,154 letters sent out to matched donors between September 6, 2021 and February 27, 2022.}[^duplicate] To maintain randomness to the best of the JMDP office's abilities, we assigned letters to the four experimental groups using weekly cluster randomization. Specifically, we created a cluster every seven days (a week starting from Monday) and randomly assigned one experimental group to each cluster (see \revise{Table} \@ref(tab:assignment)). The assignment of the experimental groups was designed to be as balanced across weeks and months as possible.

[^duplicate]: In a few cases during our experimental period, the same registrant matched with more than one patient and received letters multiple times.

\revise{Before conducting the experiment, we obtained approval from the institutional review boards of the Graduate School of Economics, Osaka University (approval number: R030305) and the JMDP (approval number: JMDP2021-04) for the experimental design and empirical strategy. We did not conduct pilot studies and did not register the experiment with a pre-analysis plan.}

## Data and Empirical Strategy

In the coordination data provided by the JMDP, the unit of observation was a \revise{coordination}. The data included \revise{donor} characteristics such as sex, age, number of coordination experiences, and prefecture-level residential area. The data on the coordination process included whether each \revise{coordination} stage (response to the letter, CT, donor selection, final consent, and collection) had been completed. Additionally, the data included the number of days taken to respond \revise{to the HLA match letter} and willingness to donate \revise{at the time of responding to the letter}. If the coordination process was interrupted \revise{before donation}, the reasons for the interruption were recorded in three categories\revise{:} patient-side reasons, donor non-health reasons, and donor health reasons. \revise{Unfortunately, the data included no information on patients such as their characteristics or prognosis.}

As additional data, we used the list of medical institutions published on the JMDP website.[^ref] This list includes complete addresses, the availability of bone marrow collection, and the availability of PBSC collection. We aggregated this list at the prefecture level and calculated the number of hospitals per 10 square kilometers.[^hospital-density] \revise{This aggregated dataset was} merged with the coordination data using the prefecture as the merge key. We considered this variable as the traveling cost of coordination and donation.

[^ref]: Data source: <https://www.jmdp.or.jp/hospitals/view2/> (Accessed August 4, 2022).

[^hospital-density]: \revise{To calculate the density of the hospitals in each prefecture, we used the land area data provided by the Geospatial Information Authority of Japan.}

```{r descriptive-stats, include=FALSE}
with(rct$data, prop.table(table(donate)))
with(rct$data, summary(age))
with(rct$data, prop.table(table(age < 40)))
with(rct$data, prop.table(table(male)))
with(rct$data, prop.table(table(coordinate1)))
with(rct$data, prop.table(table(prefecture)[order(table(prefecture))]))
with(subset(rct$data, prefecture %in% c("東京都", "大阪府")), table(prefecture, hospital_per_area))
with(rct$data, mean(unique(hospital_per_area)))
```

The analysis \revise{sample} included 11,049 \revise{completed or interrupted coordinations involving} matched donors living in Japan.[^exclude] \revise{Of these coordinations, $4.6$\% were completed (donation was made) and $63.5$\% involved matched donors coordinating for the first time. The mean and median age of matched donors were 39 and $37.98$ years, respectively, while $62.4$\% of coordinations involved male donors. There were slightly more young donors and male donors than in the donor pool.}[^detail-descriptive-stats]

```{r ongoing-balance, include=FALSE}
ongoing_f <- rawdt$balance_attrition()
```

[^exclude]: \revise{One coordination involved a matched donor who lived abroad}. There were 104 \revise{coordinations} with ongoing coordination at the time of data collection. The proportion of \revise{ongoing coordinations} was balanced across the experimental groups (`r ongoing_f[[2]]`).

[^detail-descriptive-stats]: \revise{Regarding geographic distribution, $17.1$\% of coordinations involved matched donors who lived in Tokyo or Osaka, where hospital density is well above the national average ($1.89$ and $1.36$, respectively compared with the national average of $0.21$).}

The primary outcome was whether matched donors underwent CT. \revise{This outcome is important for two reasons. First, reaching the CT stage requires donors to respond to the HLA match letter, indicate their willingness to donate, and maintain their intentions. Additionally, late responses lead to coordination interruptions before the CT stage. Second, physicians can select the most appropriate donor for transplantation from among the matched donors who have undergone CT. Thus, showing up for CT represents both a costly prosocial behavior and an important practical indicator of coordination.}

```{r summary}
rct$
  summary_experiment()$
  kable(
    title = "Summary of the Field Experiment",
    notes = paste(
      "\\\\emph{Note}: For the balance test, we regressed a covariate on treatment dummies and tested the null hypothesis that all coefficients are zero. We used standard errors clustered by the assigned week for the statistical inference. Abbreviation: PBSC = peripheral blood stem cell; BM = bone marrow."
    ),
    font_size = 8
  )
```

Table \@ref(tab:summary) summarizes our experiment. Panels A and B present the intervention and sample size for each experimental group, respectively. Panel C presents a balance test of whether the randomization was successful. There were statistically significant differences in the average age and number of holidays in the assignment week and the following week between the experimental groups. The average age of \revise{the CoordMessage group} was approximately one year younger than that of the \revise{StatusQuo} group. However, this difference was negligible from a standardized mean difference perspective (see Table \revise{A1} in Supplementary Material A). The average number of holidays for \revise{the MatchMessage group} was higher than that of the \revise{StatusQuo} group. This occurred because \revise{for a cluster of the MatchMessage group assigned in December}, the week following their assignment week included the New Year's holiday (see Table \@ref(tab:assignment)).[^new-year-holidays]

[^new-year-holidays]: In Japan, the New Year's holiday is set by the government to run from December 29 to January 3. While we follow this definition, this holiday may be extended depending on individual circumstances.

Although most covariates were balanced across the experimental groups, a few were unbalanced.[^cor] Therefore, in addition to a simple difference-in-means test, we estimated the following linear regression model for HLA match letter $i$ sent out in week $w$ of month $m$:

\begin{equation}
  \begin{split}
  Y_{iwm} =& \alpha + \beta_1 \cdot \text{MatchMessage}_{wm}
  + \beta_2 \cdot \text{CoordMessage}_{wm} + \beta_3 \cdot \text{BothMessage}_{wm} \\
  &+ X'_{iwm} \gamma + u_{iwm},
  \end{split}(\#eq:reg)
\end{equation}

\noindent
where $X_{iwm}$ is a vector of observable characteristics, including donor age and the number of holidays. The parameters of interest are $(\beta_1, \beta_2, \beta_3)$. \revise{We used standard errors clustered by the assigned week for statistical inference because all donors who matched with the same patient could have received the letter in the same week.}

[^cor]: \revise{We confirmed that age and the number of holidays did not affect CT, which is our primary outcome, in the StatusQuo group. Therefore, the imbalance in some covariates is not a major concern. We present the results of a regression analysis that adjusts for these effects in Supplementary Material A.}

# Experimental Results {#result}
## Average Treatment Effects on Reaching CT {#main}

```{r reason-stop, include=FALSE}
mean_test <- subset(rct$data, treat == "StatusQuo") %>%
  with(prop.table(table(test)) * 100)

mean_positive <- subset(rct$data, treat == "StatusQuo") %>%
  with(prop.table(table(positive)) * 100)

positive_clasify <- rct$data %>%
  filter(treat == "StatusQuo" & positive == 1) %>%
  with(prop.table(table(test, exg_stop_test)) * 100)

reason_clasify <- rct$data %>%
  filter(positive == 1 & test == 0 & treat == "StatusQuo") %>%
  with(prop.table(table(exg_stop_test, useNA = "always")) * 100)
```

\revise{In this subsection, we present the estimated effects of the intervention messages on reaching the CT stage.} We used a dummy variable coded one if a matched donor reached the CT stage.[^outcome-skipped-CT] In the \revise{StatusQuo} group, only `r sprintf("$%1.2f$%%", mean_test["1"])` of matched donors underwent CT.

[^outcome-skipped-CT]: We also coded the CT dummy one if CT was skipped.

There are two reasons for the low probability of reaching CT. First, only `r sprintf("$%1.2f$%%", mean_positive["1"])` of the donors in the \revise{StatusQuo} group indicated their willingness to donate. Second, \revise{$59.48$\% of those who expressed a willingness to donate did not reach the CT stage (i.e., they dropped out between the response and CT stages) and 86\% of these dropouts occurred for donor-related reasons.}[^endogenous-dropout-rate] According to @Hirakawa2018, \revise{the top three donor-related reasons are health conditions such as lower back pain (imputed rates: 59\%), scheduling conflicts (imputed rates: 14\%), and the lack of family consent (imputed rates: 9\%).}[^calculate-percentage] Our intervention messages are expected to increase the probability of reaching CT by both improving the willingness to donate and preventing dropouts between the response and CT stages.

[^endogenous-dropout-rate]: \revise{Thus, $51.15$\% ($=59.48 \times 0.86$) of those who expressed a willingness to donate did not reach the CT stage for donor-related reasons.}

[^calculate-percentage]: @Hirakawa2018 \revise{found that the top three donor-related reasons are health conditions (69\%), scheduling conflicts (16\%), and the lack of family consent (10\%). Using these values, we imputed the percentages of donor-related reasons in our data. For example, the percentage of health conditions is $86 \times 0.69 = 48$\%.}

```{r test-diff-mean, fig.height=10, fig.cap = "Sample Proportion of Reaching CT by Experimental Group.\\newline \\emph{Note}: Error bars show the standard errors of the mean. For the statistical test, we used standard errors clustered by the assigned week."}
rct$
  lm_effect("test", sample_drop = FALSE)$
  fit(scale = 100)$
  plot_ate(
    xlab = "Experimental group",
    ylab = "Share of participants (%)",
    p_text_margin = 4,
    add_segment_margin = 12,
    segment_margin = 5,
    show_p = 1,
    edge_length = 2,
    p_text_size = 7,
    avg_text_size = 7,
    avg_text_pos = 10,
    avg_digit = 1,
    base_size = 25,
    ylim = c(0, 100),
    ybreaks = seq(0, 100, by = 10)
  )
```

The proportions of donors reaching the CT stage for each of the experimental groups are presented in Figure \@ref(fig:test-diff-mean). \revise{The MatchMessage group, which received the matching difficulty message, had a $3.2$ percentage point higher probability of reaching CT than the \revise{StatusQuo} group. This effect was} statistically significant. We obtained the same results when we adjusted for multiple \revise{hypotheses} testing, as proposed by @List2019 (see Column (1) of \revise{Table A2 in Supplementary Material A}). The effect of \revise{the MatchMessage group} remained statistically significant when controlling for the covariates \revise{and month fixed effects} using a linear probability model (see Column (2) of \revise{Table A2 in Supplementary Material A}). \revise{In addition, this result was} robust to using logistic regression models instead of linear probability models (see Table \revise{A3} in Supplementary Material A). In summary, the \revise{matching difficulty} message included in the HLA match letter sent to \revise{the MatchMessage group} increased the probability of \revise{coordinations} reaching the CT stage.

```{r lm-test-decompose}
rct$
  lm_decompose_effect("test")$
  fit(scale = 100)$
  kable_reg(
    title = "Decomposition of the Effect on Reaching CT",
    coef_map_lm = c(
      "treatMatchMessage" = "MatchMessage group",
      "treatCoordMessage" = "CoordMessage group",
      "treatBothMessage" = "BothMessage group"
    ),
    notes = "Robust standard errors are in parentheses. The unit of treatment effect is a percentage point. The outcome ``Endogenous dropout'' is a dummy variable that takes a value of 1 if candidates responded with a willingness to donate but did not reach the CT stage for donor-side health and non-health reasons . Covariates are gender, age and its squared term, the number of past coordinations, the number of public holidays in the assigned week and the following week, the number of hospitals per 10 square kilometers, the number of hospitals with PBSC collection per 10 square kilometers, the number of hospitals with BM collection per 10 square kilometers, and a dummy indicating that the candidate skipped CT. All the covariates except the gender dummy and dummy of skipped CT were demeaned.",
    font_size = 8
  )
```

As mentioned previously, our intervention is expected to increase the probability of reaching CT by improving the willingness to donate and preventing dropout between the response and CT stages. Therefore, we decomposed the intervention message effects into two components: responses with a willingness to donate and prevention of \revise{dropout} for donor-side reasons (endogenous \revise{dropout}). The results are presented in \revise{Table} \@ref(tab:lm-test-decompose). \revise{Although the evidence is suggestive, our intervention worked as expected, except for the CoordMessage group.}

\revise{However, the mechanisms differed slightly across the intervention groups. The willingness to donate increased primarily in the MatchMessage group. As shown in column (1), the willingness to donate in this group increased by $2.31$ percentage points, statistically significant at the 10\% level. Endogenous dropout in the MatchMessage group also fell by approximately 1 percentage point, although this was not statistically significant. Combining these effects, the probability of reaching CT increased in the MatchMessage group. By contrast, the CoordMessage and BothMessage groups primarily contributed to preventing endogenous dropout. In particular, as shown in column (4), endogenous dropout fell by $2.27$ percentage points in the BothMessage group, statistically significant at the 5\% level. However, the willingness to donate of these groups did not sufficiently increase, limiting the increase in the probability of reaching CT in both groups. Therefore, these findings suggest that the matching difficulty message may help improve the willingness to donate, while the early coordination message may prevent endogenous dropout.}

## Effect on Response Speed {#response-speed}

The early coordination message \revise{is} expected to increase the CT completion rate by encouraging early responses. Among donors who indicated a willingness to donate, those who responded earlier had a higher probability of reaching CT (see Figure \@ref(fig:speed-CT-cond-response)). Therefore, we examined whether \revise{the CoordMessage and BothMessage groups}, which did not show an overall increase in their willingness to donate, may have shown increased early responses accompanied by a willingness to donate.


```{r cumulative-response, fig.cap = "Cumulative Rate of Response with Positive Intention by Treatment \\newline \\emph{Note}: We excluded those who skipped CT. We only show the cumulative response rates up to 25 days after the HLA match letter was sent because there was no remarkable change in the response rate thereafter."}
rct_noskip$
  flow("positive", sample_drop = FALSE)$
  plot_cumulative(
    upper_days = 25,
    xbreaks = seq(0, 100, by = 4),
    ylim = c(0, 60),
    xlab = "Response days",
    ylab = "Cumulative rate of\nresponse with positive intention (%)",
    base_size = 25
  )
```

```{r lm-positive-time-decompose}
rct$
  flow(outcome = "positive", sample_drop = FALSE)$
  lm_time_segment(cut_days = c(7, 12))$
  fit(scale = 100)$
  kable_reg(
    title = "Effect on Response Speed with Positive Intention",
    coef_map_lm = c(
      "treatMatchMessage" = "MatchMessage group",
      "treatCoordMessage" = "CoordMessage group",
      "treatBothMessage" = "BothMessage group"
    ),
    notes = "Robust standard errors are in parentheses. The unit of treatment effect is a percentage point. The outcome is a dummy variable that takes a value of 1 if the candidate responded with positive intention within a specified time after the HLA match letter being sent. We excluded those who skipped CT. Covariates are gender, age and its squared term, the number of past coordinations, the number of public holidays in the assigned week and the following week, the number of hospitals per 10 square kilometers, the number of hospitals with PBSC collection per 10 square kilometers, and the number of hospitals with BM collection per 10 square kilometers. All the covariates were demeaned.",
    font_size = 8
  )
```

\revise{First, Figure} \@ref(fig:cumulative-response) \revise{shows the cumulative response rates of the willingness to donate over time for the experimental groups.} \revise{We obtain two notable findings. First, up to approximately 10 days, the cumulative response rates of the intervention groups were almost identical but lower than those of the StatusQuo group. This suggests that the early coordination message may not have had the expected effect. Second, after 14 days, the cumulative response rate of the MatchMessage group became higher than that of the StatusQuo group. Thus, the willingness to donate of the MatchMessage group increased but this may have slowed response speed.}

\revise{Next, we verified these findings through regression analysis. Since the JMDP requests responses within seven days, we defined early responses as responses with a willingness to donate within seven days. We created dummy variables for responses with a willingness to donate within 7 days, 8--12 days, and after 13 days. We then estimated linear probability models using these dummy variables as outcomes. Table} \@ref(tab:lm-positive-time-decompose) \revise{presents the estimation results. The results were consistent with the descriptive findings but the differences from the StatusQuo group were not statistically significant. Therefore, the early coordination message did not have the expected effect.}

# Welfare Implications of the Intervention {#discussion}

\revise{In this section, we discuss how the MatchMessage group, which increases coordination to reach the CT stage, affects welfare. Specifically, we examine how increasing the number of candidates reaching the CT stage affects patient welfare and assess whether the intervention simply encourages candidates unlikely to be selected as a donor to arrive at CT, thereby wasting their time. Through this analysis, we obtain insights into the welfare effects of the intervention.}

## Patient Welfare: Intervention Effects on Donation and Donor Quality {#patient-welfare}

\revise{We first examine the treatment effects on the post-CT stages: donor selection, final consent, and collection (donation). Reaching these stages is influenced not only by our intervention but also by patient-side demand. As a benchmark, suppose that the JMDP office sends HLA match letters to 10 donors matched with a patient and all matched donors reach the CT stage. Since a physician selects the best donor from the 10 matched donors, the donor selection and donation rates reach a maximum of 10\% of matched donors who received HLA match letters. However, when desirable donors are not found through the CT stage or when few matched donors complete the CT stage, a physician may be unable to find the best donor among matched donors. In this case, selection and donation rates fall below 10\%. Conversely, when the JMDP office sends HLA match letters to fewer than 10 matched donors, selection and donation rates exceed 10\%. In the StatusQuo group, the donor selection rate is $6.19$\% and the donor donation rate is $4.5$\%. The difference between these rates indicates the dropout between selection and donation attributable to patient deterioration or the failure to obtain final consent from a donor.}

\revise{Figure A1 and Table A4 in Supplementary Material A show the treatment effects on the post-CT stages. The estimated effects on all three stages are smaller than the effects on the CT stage. Specifically, when controlling for the covariates, donor selection and donation in the MatchMessage group reduced by $0.29$ and $0.12$ percentage points, respectively. These effects on the post-CT stages were not statistically significant. Logistic regression yielded similar results (see Table A5 in Supplementary Material A). We did not obtain results showing that our intervention has positive effects on donor selection or donation.}

\revise{We should not conclude from this result alone that patient welfare did not improve. Since coordinations to reach the CT stage increased in the MatchMessage group, physicians became able to select the best donor from many matched donors. Therefore, the positive effect of the MatchMessage group on the CT stage may enable physicians to select higher-quality donors and improve patient prognosis. That is, while the MatchMessage group may not affect transplant quantity, it may have a positive effect on transplant quality. However, we cannot verify this hypothesis because of a lack of patient data.}

## Donor Welfare: Does the Intervention Encourage Action by Candidates Unlikely to Be Selected as Donors? {#donor-welfare}

\revise{The finding that the probability of donation did not increase suggests that our intervention may simply encourage matched donors unlikely to become the best donor for transplantation to arrive at CT. This possibility can be explained by two hypotheses. The first hypothesis is that matched donors lose their intention to donate after reaching the CT stage. The second hypothesis is that people who responded to the intervention (particularly, those in the MatchMessage group) had characteristics that made them less likely to be selected as the best donor. We obtained results supporting the second hypothesis through the following set of analyses.}

\revise{To test the first hypothesis, we examined the reasons for the dropout between the CT stage and selection. Among those who reached the CT stage in the StatusQuo group, 26\% were selected as the best donor and 70\% dropped out for exogenous reasons, including patient-side reasons and donor health reasons. According to \citet{Hirakawa2018}, the main donor health reason is disqualification because of the CT results. That is, dropout for exogenous reasons strongly reflects not being selected as the best donor. The remaining coordinations (4\%) were interrupted for donor non-health reasons. According to \citet{Hirakawa2018}, these reasons include scheduling conflicts, an inability to make contact with the potential donor, and a lack of family consent.}

\revise{We tested whether our intervention increased coordinations interrupted for donor non-health reasons among those who reached the CT stage (Table A6 in Supplementary Material A). In the MatchMessage group, cases interrupted for exogenous reasons increased by $3.6$ percentage points ($p = 0.08$). Conversely, in this group, which showed an increased probability of reaching the CT stage, coordinations interrupted for donor non-health reasons slightly reduced between the CT stage and selection by $0.5$ percentage points, which was not statistically significant ($p = 0.59$). Therefore, those who received the matching difficulty message and reached the CT stage continued to maintain their intention to donate after CT, which does not support the first hypothesis.}

\revise{To test the second hypothesis, we focused on those in the StatusQuo group who reached the CT stage to examine which characteristics make candidates more likely to be selected as the best donor (Table A7 in Supplementary Material A). Overall, young men were more likely to be selected as the best donor, consistent with medical findings that relying on young and male donors improves patient prognosis \citep{Loren2006, Arai2016, Kollman2016, Shinohara2017}. Donor selection and donation were unrelated to the speed of reaching the CT stage (those who responded to the HLA match letter quickly or could skip CT). Those who arrive at the CT stage early may need to wait for other candidates to complete CT because physicians select the best donor from among a group of candidates. Similarly, past coordination experience was unrelated to selection or donation. However, physicians could know the last coordination results (interrupted for donor reasons, interrupted for patient reasons, or collection) for those with past coordination experience when selecting donors. According to \citet{Hirakawa2018}, those whose last coordination was interrupted for patient reasons or experienced donation were more likely to donate than those whose last coordination was interrupted for donor reasons. Given this, physicians may have been less likely to select those whose last coordination was interrupted for donor reasons. Therefore, important factors in donor selection are gender, age, and past coordination experience (particularly the results of the last coordination).}

\revise{Next, we explored the heterogeneity of the treatment effects by gender, age, and past coordination experience (Figure A2 in Supplementary Material A). We found that the MatchMessage group encouraged young men with past coordination experience (7 percentage points; $p = 0.05$) and older men matched for the first time (7 percentage points; $p = 0.02$) to arrive at CT. In particular, the MatchMessage group increased the probability of being selected as the best donor for the former group (5 percentage points; $p < 0.01$). This reflects the medical preference for young men. Among young women with past coordination experience, the probability of reaching the CT stage increased in all the intervention groups but this did not increase their probability of selection. This result may reflect the influence of physician selection for reasons for past coordination termination. Therefore, the MatchMessage group changed the behavior of both those likely to be selected as donors and those unlikely to be selected, resulting in average treatment effects on donor selection and donation close to zero.}

## Policy and Welfare Implications {#discussion-summary}

\revise{The discussion so far can be summarized as follows. While receiving the matching difficulty message promoted reaching the CT stage overall, it did not increase selection or donation rates. This finding stems from the result that those who responded to the message included both individuals likely to be selected as the best donor and those unlikely to be selected. Specifically, receiving the matching difficulty message not only encouraged  young men with past coordination experience to arrive at CT but also increased their probability of being selected as the best donor. This result is desirable given medical evidence that relying on young men improves patient prognosis. At the same time, among those in the MatchMessage group, the probability of reaching the CT stage increased for older men matched for the first time and for young women with past coordination experience; however, this did not increase their probability of selection. Thus, they may have simply wasted their time. In this sense, our intervention may have reduced donor welfare. Therefore, rather than a uniform intervention in which all matched donors receive messages, interventions targeting young men may be more appropriate from the perspectives of welfare and cost-effectiveness.}

\revise{However, the welfare-reducing effects of the uniform intervention may be mitigated in three ways. First, some people with past coordination experience can skip the CT tests. Those who respond indicating donation intention automatically reach the CT stage. In our data, 19\% of young women with past coordination experience could skip the CT tests, meaning they would not waste time in coordination. Second, even if not selected as the best donor in the current coordination, those who reach the CT stage may be able to skip the CT stage in future coordinations. From a long-term perspective, reaching the CT stage can mitigate welfare losses. Third, increasing the number of people reaching the CT stage may enable physicians to select higher-quality donors, which could have positive effects on patient prognosis. Future work is needed to verify these points and accurately obtain the welfare implications of the intervention.}

# Conclusions {#conclusion}

This study examined how information provision \revise{at the time of matching} affects donor availability in stem cell transplantation. The results of our field experiment demonstrated that providing information on the limited number of HLA-compatible donors per patient (i.e., the \revise{matching difficulty} message) increased the probability of reaching CT. This result suggests that physicians can select \revise{the best donor} for transplantation from a larger pool of matched donors. However, when presented simultaneously with an ineffective early coordination message, the positive effect of the \revise{matching difficulty} message was diminished. We speculate this is because of the negative effect of information overload. Therefore, it is important to convey effective information in a simple manner.

To evaluate the cost effectiveness of the intervention, we assess the impact of the \revise{matching difficulty} message on donor recruitment. The \revise{matching difficulty} message increased the CT completion rate by $11.5\% (= 2.56/22.25)$. We can then calculate how many additional donor registrations would be needed to achieve this same 11.5\% increase in the CT completion rate. First, the positive effect of the \revise{matching difficulty} message on CT is equivalent to increasing the number of \revise{matched donors} by 11.5\%.[^proof] Since 40% of registrants become matched donors, $224,000$ of the current $560,000$ registrants are potential matched donors.[^data1] Therefore, the effect of the \revise{matching difficulty} message on CT is equivalent to increasing the number of matched donors from $224,000$ to $249,760 (= 224,000 \times 1.115)$, an increase of $25,760$. Alternatively, the effect of the \revise{matching difficulty} message on CT is equivalent to increasing the number of registrants from $560,000$ to $624,400 (= 560,000 \times 1.115)$, an increase of $64,400$. The current JMDP donor pool includes $100,000$ registered donors in their 50s.[^data2] Owing to the age limit for donation (54 years), donors in their 50s will exit the pool within the next five years. This back-of-the-envelope calculation suggests that the \revise{matching difficulty} message can prevent approximately 64.4\% of the negative effects caused by the shrinking donor pool. Donor recruitment efforts are costly. While the cost required to increase one donor registration at the JMDP is unknown, the National Marrow Donor Program incurs approximately USD 150 when adding one donor registration.[^data3] If the JMDP bears a similar cost, recruiting $64,400$ donor candidates would cost USD $9.66$ million. Therefore, adding messages could be a more cost-effective measure than recruiting donors.

[^proof]: Let $N_m$ be the number of registrants who start the coordination process. Let $N_1(d)$ be the number of potential donors who reach CT under treatment $d$. Then, $N_1(d) = p(d)N_m$ holds, where $p(d)$ is the probability of reaching CT under treatment $d$. Note that $d = 1$ and $d = 0$ represent the treatment and control groups, respectively. We solve $N_1(1) = p(0)[N_m + \Delta N_m]$ for $\Delta N_m$, where $\Delta N_m$ represents the increase in registrants who start coordination. Therefore, we obtain $[p(1) - p(0)]/p(0) = \Delta N_m/N_m$.

[^data1]: The cumulative number of registrants since the JMDP's establishment is $980,000$. Among these registrants, $390,000$ have become potential donors who started the coordination process. Therefore, 40\% of registrants become potential donors who start coordination. Data source: <https://www.bs.jrc.or.jp/bmdc/donorregistrant/m2_03_00_statistics.html> (Accessed December 8, 2024).

[^data2]: <https://www.jmdp.or.jp/about/read/number/> (Accessed December 8, 2024).

[^data3]: <https://fundraise.nmdp.org/index.cfm?fuseaction=cms.page&id=1203&eventID=675> (Accessed March 29, 2025).

Finally, our intervention can be applied to contexts beyond stem cell transplantation. The essence of the \revise{matching difficulty} message is to emphasize the scarcity of investors or potential cooperators for public goods. In our context, this message corrected donors' overestimation of substitutable other donors and discouraged free-riding. Alternatively, this message made the rarity of opportunities to cooperate salient. Unfortunately, our data cannot identify which mechanism drove donors. Nevertheless, communicating the scarcity of cooperators is likely to be effective in other cooperative environments such as donations of rare blood types.