---
title: |
  Exploring Information Provision to Promote Stem Cell Donation:
  Evidence from a Field Experiment of the Japan Marrow Donor Program
author:
  - name: Hiroki Kato
    affil-id: a
    note: "Corresponding author. E-mail address: hkato.econ@aoyamagakuin.jp"
  - name: Fumio Ohtake
    affil-id: b
    note: "E-mail address: ohtake@cider.osaka-u.ac.jp"
  - name: Saiko Kurosawa
    affil-id: c
    note: "E-mail address: skurosaw@inahp.jp"
  - name: Kazuhiro Yoshiuchi
    affil-id: d
    note: "E-mail address: kyoshiuc-tky@umin.ac.jp "
  - name: Takahiro Fukuda
    affil-id: e
    note: "E-mail address: tafukuda@ncc.go.jp"
affiliations:
  - id: a
    name: School of International Politics, Economics and Communication, Aoyama Gakuin University, 4-4-25 Shibuya, Shibuya-ku, Tokyo 150-8366, Japan
  - id: b
    name: Center for Infectious Disease Education and Research (CiDER), Osaka University, 1-10 Yamadaoka, Suita, Osaka 565-0871, Japan​
  - id: c
    name: Department of Oncology, Ina Central Hospital, 1313-1, Koshirokubo, Ina, Nagano 396-8555, Japan
  - id: d
    name: Graduate School of Medicine, The University of Tokyo, 7-3-1 Hongo, Bunkyo, Tokyo 113-8655, Japan
  - id: e
    name: Department of Hematopoietic Stem Cell Transplantation, National Cancer Center Hospital, 5-1-1 Tsukiji, Chuo-ku, Tokyo 104-0045, Japan
abstract: |
  In stem cell transplantation, registered potential donors may refuse to donate when matched with patients, causing supply shortages. Thus, preventing such donor dropout is crucial. To address this issue, we developed a behavioral intervention comprising adding messages into the letters sent when donors are matched with patients \revise{and} conducted a field experiment to verify the effect of our intervention. The results demonstrate that our behavioral interventions can prevent registered donor dropout and increase donor availability for transplantation. Specifically, the message emphasizing the limited number of compatible donors per patient increased the probability of donors completing the confirmatory typing stage by 11.5%. Since physicians can choose the best donor for proceeding to donation from those who complete the confirmatory typing stage, this message effect increases donor availability for transplantation.

  \vspace{0.5em}
  \noindent
  \textit{Keywords}: prosocial behavior, field experiment, free-riding, information provision, Japan Marrow Donor Program, stem cell transplantation

  \vspace{0.5em}
  \noindent
  \textit{JEL classification}: D64, D90, H41, I11
acknowledgements: |
  We would like to thank the Japan Marrow Donor Program office for managing the field experiment and providing us with the data. We thank Tsuneaki Hirakawa and two anonymous reviewers for their helpful comments and suggestions. This study was conducted with the approval of the institutional review boards of the Graduate School of Economics, Osaka University (approval number: R030305-2) and the Japan Marrow Donor Program (approval number: JMDP2021-04).

  \vspace{0.5em}
  \noindent
  Funding: This work was supported by the Japan Society for the Promotion of Science [grant number 20H05632] and the Ministry of Health, Labour and Welfare [grant number 19FF1001].

  \vspace{0.5em}
  \noindent
  Declarations of interest: none.
ai-declaration: |
  During the preparation of this work, we used Claude to improve the readability and language of the manuscript. After using these tools, we carefully reviewed and edited the content as needed and take full responsibility for the content of the published article.
bibliography: biblio.bib
biblio-style: elsarticle-harv.bst
output:
  bookdown::pdf_document2:
    latex_engine: pdflatex
    template: template/my-template-science-direct.tex
    keep_tex: true
    toc: false
    number_sections: true
    citation_package: natbib
base-strech: 2
fontsize: 12pt
---

```{r include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  error = FALSE,
  message = FALSE,
  dev = "pdf",
  fig.width = 15,
  fig.height = 10,
  fig.pos = "t",
  out.extra = ""
)
```

```{r option, include = FALSE}
options(
  knitr.table.format = "latex",
  knitr.kable.NA = "",
  kableExtra.auto_format = FALSE,
  modelsummary_factory_latex = "kableExtra",
  modelsummary_get = "broom"
)
```

\clearpage

# Introduction {#intro}

Similar to organ transplantation, allogeneic hematopoietic stem cell transplantation (HSCT) faces supply shortages in many countries. To resolve this issue, particularly in the context of organ transplantation from deceased donors, many studies have examined interventions to increase donor registrations [for example, @Kessler2012]. In addition, HSCT faces another challenge: registered donors may refuse to donate when matched with patients [for example, @Switzer2018; @Haylock2024]. Thus, developing interventions to mitigate such donor dropout is crucial. This study examines how behavioral interventions at the time of matching can prevent donor dropout and resolve the supply shortage issue.

HSCT has the lowest relapse rate among all treatments for leukemia and other blood cancers. In this treatment, (1) anticancer drugs or radiation are used to kill tumor cells and (2) healthy hematopoietic stem cells are transplanted from a donor. The transplantation requires that the donor's white blood cell type (HLA) completely or partially matches the patient's HLA.[^hapro] When patients cannot find a compatible donor among their relatives, who are more likely to be matched, they can search for unrelated donors through \revise{donor registries such as National Marrow Donor Program (NMDP) and Japan Marrow Donor Program (JMDP).}[^match-probability]

[^hapro]: When HLA-identical or partially matched unrelated donors are unavailable, several options exist. The first option is haploidentical stem cell transplantation in which stem cells are transplanted from a close relative with semi-matched HLA. The second option is cord blood transplantation in which stem cells are transplanted from the umbilical cord or placenta of pregnant women. The HLA requirements for these transplants are weaker than those for bone marrow (or peripheral blood stem cell (PBSC)) transplants between unrelated individuals. Notably, in Japan, bone marrow and PBSC transplants between unrelated individuals accounted for 20% of all transplants in 2021 [@JDCHCT2022].

[^match-probability]: While the probability of a complete match between two randomly selected individuals is less than 1\%, the probability of a full match between siblings is 30\%.

<!-- *Note: 一般論からJMDPへの展開
しかしながら、世界中のdonor registriesはレジストリに登録したドナーの脱落という共通の課題を抱えている\citep{Switzer2004; Lown2014; Hamed2023}。患者とマッチしたドナー候補者は移植の適格性を調べるconfirmatory typing (CT)を受ける。医者はこの結果に基づいて最適なドナーを選ぶので、CT以前のドナー脱落はdonor availabilityを低下させる。たとえば、大規模なレジストリの一つであるDKMS Germanyでは、CTステージにおけるドナー脱落率を23\%であった\citep{Haylock2014}。また、日本のレジストリであるJMDPでは、56\% of transplant coordinations do not reach the CT stage for donor-related reasons \citep{Hirakawa2018}.この問題は移植までの時間を引き延ばし、結果として、患者のアウトカムに悪影響をもたらす\citep{Lown2013}。[^fact]Thus, we should explore and adopt interventions to increase the number of donor candidates who reach CT, thereby improving donor availability, while maintaining individuals' autonomy.[^donor-quantity]
-->

\revise{However, donor registries worldwide face a common challenge: dropout among registered donors \citep{Switzer2004, Lown2014, Hamed2023}. Donor candidates matched with patients undergo confirmatory typing (CT) to assess their eligibility for transplantation. Because physicians select the most suitable donor based on CT results, dropout before CT reduces donor availability. For example, dropout at the CT stage is 23\% in DKMS Germany \citep{Haylock2024}, and} 56\% of transplant coordinations in JMDP do not reach the CT stage for donor-related reasons \citep{Hirakawa2018}. \revise{Donor dropout prolongs time to transplantation and worsens patient outcomes \citep{Lown2013}.}[^fact] Thus, \revise{interventions to reduce pre-CT donor dropout are needed while preserving individual autonomy.}[^donor-quantity]


[^fact]: In the JMDP, between 2004 and 2013, only 60\% of the patients registered with the JMDP end up receiving transplantation. Moreover, 58\% of patients who died (or had their transplantation interrupted because of poor health) passed away within 200 days [@Hirakawa2018].

[^donor-quantity]: \revise{One may think that expanding donor pool (i.e., recruiting new donors) is one solution. However, many registries have already undertaken such activities for a long time, so the marginal benefit of expanding the donor pool is limited.} Indeed, in the JMDP, the benefit of expanding the donor pool is limited because most patients do eventually find donor candidates [@Takanashi2016].

In this study, we developed information interventions to increase the number of donor candidates who progress to the CT stage, in collaboration with the JMDP. The interventions added messages to the letters sent when donors are matched with patients. This letter informs \revise{donors of their compatibility with a specific patient} and requests their participation in the transplantation coordination. Upon responding to this so-called "HLA match letter," matched donors indicate their willingness to donate and proceed to the CT stage. We developed two intervention messages---\emph{matching difficulty} and \emph{early coordination}. \revise{The former emphasizes the limited number of HLA-compatible donors per patient to prevent motivational crowding-out of altruistic donors. The latter emphasizes the importance of early coordination for patient outcomes to prevent delayed response to the HLA match letter.} Our experimental participants comprised recipients of the 11,154 HLA match letters that were sent between September 2021 and February 2022.

Using coordination data provided by the JMDP, we \revise{find} that our intervention increases the probability of donors reaching the CT stage. Specifically, \revise{the matching difficulty message increased the likelihood of donors reaching CT by $7.3$\%.} A back-of-the-envelope calculation suggests that this positive effect may partially \revise{offset the future shrinkage of the donor pool due to aging} (as discussed in Section \@ref(conclusion)). However, the early coordination message did not have the intended effect of increasing the probability of donors reaching the CT stage. \revise{Taken together, our field experiment suggests that perceived scarcity of compatible donors prevents motivational crowding-out of altruistic donors.}

<!-- *Note：貢献
この研究は二つの貢献をもたらす。第一に、異なるターゲットにおける情報提供の実験エビデンスを追加することでdonor engagementにおける情報提供に関する研究に貢献する。これまでの研究では、供給量を増やすことを目的に社会的便益やピア効果を引き出す情報提供の介入を検討してきた\citep{Li2016, Sallis2018, Robitaille2021, Goette2020, Goette2024}。[^Heger2020]そのため、既存研究はドナー登録や経験のない人（すなわち、寄付の意欲が低い利己的な人）も含まれる一般層をターゲットにしてきた。これに対して、我々の研究は既存研究と似た介入を検討するが、その目的が大きく異なる。我々は供給量を増やすよりも登録したドナーの脱落を防ぐことを目的とする。したがって、このターゲットは寄付の意欲の高い利他的な人を相対的に多く含んでおり\citep{Bergstrom2009, Ohtake2020}、既存研究の介入対象とは異なる。[^other-context]

しかしながら、いくつかの研究は我々の介入目的を共有している。\citet{Switzer2018}はマッチング時における情報提供の介入を検討しているが、ランダム化比較試験ではなかった。\citet{Haylock2024}はマッチング前のコミットメントの効果を検証しており、我々の介入のタイミングとは異なる。我々の知る限りでは、我々ははじめて、ランダム化比較試験を通して、利他的な集団におけるマッチング時の情報提供の効果を記録する。

第二に、社会規範メッセージに関する研究に、それと対照的なメッセージの有効性を示すことで貢献する。社会規範メッセージは大多数の人の行動に関する情報を提供し、社会的イメージや同調性を刺激する\citep{Bernheim1994, Bursztyn2017}。実際に、金銭的寄付の文脈で、このメッセージの有効性が報告されている\citep{Shang2009, Kessler2017}。一方で、我々のメッセージは少数の人しか行動できないという希少性を強調しており、社会規範メッセージと対照的である。公共財の標準的な経済理論によれば、大多数の人がすでに行動しているという情報は個人の行動を抑制する可能性がある。実際に、ワクチン接種の文脈では、そのような情報が個人の接種意欲を下げることが報告されている\citep{Lau2019, Galizzi2022}。その場合、社会的規範メッセージではなく、希少性や少数の人しか行動していないという情報が有効である。我々の実験は利他的な集団においてこのメッセージが有効であることを示す。[^brekke2011]
-->

\revise{We contribute to the literature on information provision in donor engagement. The key distinction with previous studies lies in both the intervention objective and the target population. Previous studies have mainly aimed to increase total supply and targeted the general population, including individuals who have not registered as donors (i.e., individuals with lower willingness to donate) \citep{Li2016, Sallis2018, Robitaille2021, Goette2020, Goette2024}.}[^Heger2020] \revise{In contrast, our objective is to prevent dropout among registered donors rather than to increase the total supply. Accordingly, our target population consists of registered donors, who are more likely to have altruistic preferences \citep{Bergstrom2009, Ohtake2020}.}[^other-context]

[^Heger2020]: \citet{Heger2020} showed that establishing registries that collect potential donors beforehand is effective in increasing the supply of blood donation. In the case of HSCT, such registries already exist. Our motivation is to prevent dropout among registered donors when they are matched with patients.

[^other-context]: Previous studies have also examined the effects of behavioral interventions such as message and information provision in health and medical policy contexts, including vaccination [for example, @Dai2021; @Milkman2021], breast cancer screening [@Bertoni2020], and cord blood transplantation [@Grieco2018]. Unlike our study, these studies targeted the general population \revise{including peoplw with low motivation to take action}.

\revise{However, a few studies share the same intervention goal as ours. \citet{Switzer2018} examined information provision interventions at the time of matching, but their study was not a randomized controlled trial. \citet{Haylock2024} examined the effects of commitment before matching, and thus the timing of their intervention differs from ours. To the best of our knowledge, we are the first to document the effects of information provision at the time of matching among an altruistic population through a randomized controlled trial.}

\revise{We also contribute to the literature on social norm messages by demonstrating the effectiveness of a message that is contrasted with social norm messages. Social norm messages describe majority behavior and can induce social image concerns and conformity \citep{Bernheim1994, Bursztyn2017}. Their effectiveness has been shown in the context of monetary donations \citep{Shang2009, Kessler2017}. By contrast, our message emphasizes that only a small number of people can act. In standard economic theory of public goods, information that many others have already acted may discourage individual behavior. In the vaccination context, such information reduces individuals' willingness to be vaccinated \citep{Lau2019, Galizzi2022}. Consistent with these findings, our experiment shows that scarcity information is effective in an altruistic population.}[^Brekke2011]

[^Brekke2011]: \citet{Brekke2011} showed that free-riding in public goods provision is eliminated when altruistic groups are formed through individual choice. \revise{This result is consistent with our finding.}

The remainder of this paper is organized as follows. Section \@ref(experiment) provides an overview of the coordination process of the JMDP and describes our field experiment. Section \@ref(result) presents the results of our experiment. Section \ref{discussion} discusses the welfare implications. Finally, Section \ref{conclusion} concludes.

# Field Experiment {#experiment}

```{r library, include=FALSE}
library(here)
library(xfun)
source(here("R/R6_RawData.r"))
source(here("R/R6_Schedule.r"))

options(
  knitr.kable.NA = "",
  modelsummary_stars_note = FALSE
)

data_root <- "data"
```

## Background: Coordination Process of the JMDP {#background}

```{r flow-chart-coordination, fig.cap = "Flowchart of the JMDP Coordination Process and Sample Selection \\newline \\emph{Note}: The numbers in this figure are based on our experimental data."}
knitr::include_graphics(here("image/flowchart.pdf"))
```

To allow readers to better understand our intervention and data, we first outline the coordination process leading to stem cell donation through the JMDP (see Figure \@ref(fig:flow-chart-coordination) for a visual overview). Individuals eligible to register as donors with the JMDP must be between 18 and 54 years and in good health.[^weight] Individuals who can actually donate must be between 20 and 55 years. As of December 2024, approximately 560,000 donors were registered with the JMDP. Of these, 240,000 (42\%) were under 40 years and 280,000 (50\%) were male.[^reference]

[^weight]: Additionally, men must weigh at least 45 kg and women must weigh at least 40 kg. See \url{https://www.jmdp.or.jp/reg/requirement/} (Japanese; Accessed October 24, 2025).

[^reference]: Data source: \url{https://www.bs.jrc.or.jp/bmdc/donorregistrant/m2_03_00_statistics.html} (Japanese; Accessed October 24, 2025).

After a patient's physician registers the patient with the JMDP, the JMDP compiles a list of candidates based on the physician's criteria (primarily HLA compatibility). The physician selects up to 10 matched donors from this list. Subsequently, the JMDP office sends each matched donor an HLA match letter, recommending a response within seven days.[^SMS] Our experimental participants are all matched donors who received HLA match letters between September 2021 and February 2022. Upon responding, matched donors complete a medical questionnaire and indicate their willingness to donate.

[^SMS]: Simultaneously, the JMDP office sends a short message to matched donors informing them that the JMDP has sent the HLA match letter.

A matched and willing donor undergoes CT within approximately one month. CT confirms whether the matched donor meets the criteria for transplantation set by the JMDP. The transplantation coordinator delegated by the JMDP explains the details of the donation process and asks matched donors and their families about their willingness to donate. Thereafter, the coordinating physician conducts medical interviews, examinations, and blood tests, including those for infectious disease markers. Collection methods (bone marrow or PBSC collection) are also determined based on the preferences of the matched donor and coordinating physician. CT can be skipped when a matched donor is eligible based on a previous CT result within one year.

The patient's physician selects the best donor from matched donors who have reached CT. When the JMDP determines that a matched donor is eligible based on their CT results, the physician receives those results and must classify the donor into three categories within 40 days: best donor, backup donor, or rejection. The physician selects only the best donor to proceed to final consent and donation but can select up to four backup donors, who are ranked by priority. When coordination with the best donor is interrupted, the highest-priority backup donor becomes the best donor.[^late-arrival]

[^late-arrival]: Even after selecting the best donor, if the JMDP determines that additional matched donors are eligible, the physician must classify them as backup donors or rejections within 40 days. However, if the best donor has not yet provided final consent, the physician can change the best donor to a later-arriving matched donor.

The best donor must provide final consent after being informed of their selection by the coordinator and coordinating physician. Simultaneously, a representative of the donor's family must provide consent to the donation. After final consent is obtained, the donor cannot withdraw their decision to donate. They then undergo a surgical procedure to collect stem cells. The time from CT to collection is approximately three to four months. Importantly, throughout the coordination process, a matched donor cannot access any information about the matched patient (e.g., the number of other available potential donors), nor can the matched donor obtain this information from the transplantation coordinator or coordinating physician.

## Experimental Design {#design}

```{r list-message}
message_dt <- tribble(
  ~treat, ~contents,
  "Standard message",
  "We inform you that your HLA type (white blood cell type) matches that of a patient in our registry, and you have been selected as one of our potential donors. We are contacting you to ask if you would like to proceed with further testing and interviews for donation. Please read the enclosed materials carefully, consider whether coordination is possible, and return the form within seven days of receiving this information. [\\emph{Insert intervention messages here}] If we proceed with coordination after receiving your response, a coordinator will contact you by phone to discuss the details of your request.",
  "Matching difficulty message",
  "The number of registered donors whose HLA type matches that of a single registered patient is one in hundreds to tens of thousands. While we may find multiple potential donors, we hope you understand that the number is limited.",
  "Early coordination message",
  "Approximately 60\\% of patients receive a transplant through the JMDP. The earlier a donor is found, the higher this rate can be increased."
)

message_dt %>%
  knitr::kable(
    caption = "List of Intervention Messages",
    col.names = c("Message", "Content"),
    align = "ll",
    booktabs = TRUE,
    linesep = "",
    escape = FALSE
  ) %>%
  kableExtra::kable_styling(font_size = 8) %>%
  kableExtra::group_rows("Intervention message", 2, 3) %>%
  kableExtra::column_spec(2, width = "40em") %>%
  kableExtra::footnote(
    general_title = "",
    general = "\\\\emph{Note}: Translated by the authors.",
    threeparttable = TRUE,
    escape = FALSE
  )
```

Our intervention involved adding two messages into the HLA match letter.[^pressure] Table \@ref(tab:list-message) lists the content of the standard letter and the two intervention messages. The JMDP also encloses a handbook that describes the coordination process as well as the medical questionnaire and donor consent form.[^ref-handbook] We developed two messages based on the finding from our preliminary survey that the target population for our intervention includes more altruistic individuals than the general population [@Ohtake2020].

[^pressure]: In designing our intervention messages, we were careful to avoid placing undue psychological pressure on potential donors. Specifically, we avoided using language that sounded like an appeal. Additionally, we only used information publicly available from the JMDP. Finally, the risks of transplantation were explained in a typical manner. The intervention message was approved by the institutional review boards of the Graduate School of Economics, Osaka University and the JMDP.

[^ref-handbook]: The handbook can be found at [https://www.jmdp.or.jp/pdf/en/DonorHandBook201708.pdf](https://www.jmdp.or.jp/pdf/en/DonorHandBook201708.pdf) (Accessed December 9, 2024).

The matching difficulty message emphasizes the low number of matched donors per registered patient. If other potential donors with the same HLA type are in the pool, one donor's donation can be substituted with that of another compatible donor. Additionally, multiple matched donors (up to 10) can be simultaneously matched with a single patient. Therefore, transplantation through the JMDP represents a public good [@Bergstrom2009]. \revise{In this setting, self-interested individuals who do not care about the patient do not contribute, regardless of the presence of substitutable donors. By contrast, individuals with altruistic preferences exhibit two types of behavior. First, purely altruistic individuals who care about transplant outcome may crowd out their motivation by donation from substitutable donors.}[^some-fact] \revise{Second, warm-glow individuals who derive utility from the act of giving itself may donate regardless of the presence of substitutable donors} [@Andreoni1990]. Thus, the matching difficulty message emphasizes the small number of possible substitutes and is expected to \revise{prevent motivational crowding-out} of purely altruistic individuals and increase their willingness to donate.[^other-mechanism]

[^some-fact]: \citet{Ohtake2020} found that 22\% of registrants had pure altruistic preferences. Moreover, @Kurosawa2022 interviewed previously matched donors and found that those with low donation intention felt that they were "one of several donors." This implies that some potential donors with low intention recognize that their donation could be substituted by others.

[^other-mechanism]: There are other two mechanisms. First, since matched donors cannot know the number of substitutable donors, this uncertainty may reduce their willingness to donate [@Exley2016]. The matching difficulty message reduces this uncertainty. Second, the message makes the rarity of the opportunity to donate more salient, which may change donor behavior.


```{r experiment-data, include=FALSE}
rawdt <- RawData$new(
  here(data_root, "shape.csv"),
  treat_vars = "treat",
  treat_levels = LETTERS[1:4],
  treat_labels = c("StatusQuo", "MatchMessage", "CoordMessage", "BothMessage")
)

rawdt$add_cond_study_sample("prefecture != '海外'")
rawdt$add_cond_study_sample("ongoing == 0")

rawdt_noskip <- rawdt$clone()
rawdt_noskip$add_cond_study_sample("skip_test == 0")
```

```{r rct-setup, include=FALSE}
intervention <- list(
  "Standard message" = c(StatusQuo = "X", MatchMessage = "X", CoordMessage = "X", BothMessage = "X"),
  "Matching difficulty message" = c(StatusQuo = "", MatchMessage = "X", CoordMessage = "", BothMessage = "X"),
  "Early coordination message" = c(StatusQuo = "", MatchMessage = "", CoordMessage = "X", BothMessage = "X")
)

endpoint <- list(
  reply = "Response",
  positive = "Positive intention",
  test = "CT",
  candidate = "Donor selection",
  consent = "Final consent",
  donate = "Donation"
)

# main sample
rct <- rawdt$RCT()
rct$add_intervention(intervention)
rct$add_outcome(endpoint)
rct$set_default_cluster("RCTweek")
rct$set_default_se_type("stata")

# robust sample (remove those who skipped the CT)
rct_noskip <- rawdt_noskip$RCT()
rct_noskip$add_intervention(intervention)
rct_noskip$add_outcome(endpoint)
rct_noskip$set_default_cluster("RCTweek")
rct_noskip$set_default_se_type("stata")
```

```{r speed-CT-cond-response, fig.cap = "Binned Scatter Plot of CT vs. Response Speed among Those Who Responded with Positive Intention. \\newline \\emph{Note}: We used those who responded with positive intention to donate in the control group (StatusQuo group). The dashed line represents nonparametric fitting. The solid line represents a fitted line of the logistic regression."}
positive_dt <- rct$data %>%
  filter(positive == 1 & 0 < days_reply & treat == "StatusQuo")

plotdt <- positive_dt %>%
  mutate(ntile = ntile(days_reply, 20)) %>%
  group_by(ntile) %>%
  summarize(
    median_day = (max(days_reply) + min(days_reply)) / 2,
    mean_ct = mean(test)
  )

plotdt %>%
  ggplot(aes(x = median_day, y = mean_ct)) +
    geom_point(color = "grey40", size = 3) +
    geom_smooth(
      aes(x = days_reply, y = test),
      data = positive_dt,
      method = "glm",
      method.args = list(family = "binomial"),
      se = FALSE,
      alpha = 0.2,
      color = "black",
      linetype = 1
    ) +
    geom_smooth(
      aes(x = days_reply, y = test),
      data = positive_dt,
      se = FALSE,
      alpha = 0.2,
      color = "black",
      linetype = 2
    ) +
    labs(x = "Response days", y = "Proportion of Reaching CT", shape = "Outcome") +
    my_theme_classic(size = 25)
```

The early coordination message emphasizes that early coordination would increase the patient's transplantation rate. Our preliminary survey found that registered donors who place higher value on immediate outcomes (higher time discount rates) were more likely to proceed with donations [@Ohtake2020]. Motivated by this finding, we created a message that emphasized the value of responding now, rather than postponing the response. Conversely, this message increases the perceived cost of refusing to donate \citep{Haylock2024}.[^perceived-cost] Furthermore, earlier responses are associated with higher rates of reaching the CT stage (Figure \@ref(fig:speed-CT-cond-response)). Therefore, this message is expected to encourage early responses and increase the probability of donors undergoing CT.

[^perceived-cost]: \citet{Haylock2024} showed that notifying registries in advance of the period during which donation is possible functions as a commitment and increases the perceived cost of refusing to donate.

Four experimental groups were established to estimate the effects of the two intervention messages. The first group received the standard HLA match letter with neither of the intervention messages, serving as the control group (StatusQuo group). The second and third groups received the standard HLA match letter including only the matching difficulty and early coordination messages, respectively (MatchMessage and CoordMessage groups, respectively). The last group received the standard HLA match letter with both intervention messages included to test the negative effect of information overload (BothMessage group).

```{r assignment}
schedule <- Schedule$new(
  here(data_root, "RCT-schedule.csv"),
  treat_labels = list(A = "StatusQuo", B = "MatchMessage", C = "CoordMessage", D = "BothMessage")
)
schedule$kable(
  title = "Assignment Schedule",
  notes = paste(
    "\\\\emph{Note}: The control group is the StatusQuo group. The experiment was not conducted during the week beginning December 27, 2021 and ending January 3, 2022 because the JMDP was closed for the New Year's holiday."
  ),
  font_size = 8
)
```

The experimental participants consisted of the recipients of the 11,154 letters sent out to matched donors between September 6, 2021 and February 27, 2022.[^duplicate] To maintain randomness to the best of the JMDP office's abilities, we assigned letters to the four experimental groups using weekly cluster randomization. Specifically, we created a cluster every seven days (a week starting from Monday) and randomly assigned one experimental group to each cluster (see Table \@ref(tab:assignment)). The assignment of the experimental groups was designed to be as balanced across weeks and months as possible.

[^duplicate]: In a few cases during our experimental period, the same registrant matched with more than one patient and received letters multiple times.

Before conducting the experiment, we obtained approval from the institutional review boards of the Graduate School of Economics, Osaka University (approval number: R030305) and the JMDP (approval number: JMDP2021-04) for the experimental design and empirical strategy. We did not conduct pilot studies and did not register the experiment with a pre-analysis plan.

## Data and Empirical Strategy {#data}

In the coordination data provided by the JMDP, the unit of observation was a coordination. The data included donor characteristics such as sex, age, number of coordination experiences, and prefecture-level residential area. The data on the coordination process included whether each coordination stage (response to the letter, CT, donor selection, final consent, and collection) had been completed. Additionally, the data included the number of days taken to respond to the HLA match letter and willingness to donate at the time of responding to the letter. If the coordination process was interrupted before donation, the reasons for the interruption were recorded in three categories: patient-side reasons, donor non-health reasons, and donor health reasons. Unfortunately, the data included no information on patients such as their characteristics or prognosis.

As additional data, we used the list of medical institutions published on the JMDP website.[^ref] This list includes complete addresses, the availability of bone marrow collection, and the availability of PBSC collection. We aggregated this list at the prefecture level and calculated the number of hospitals per 10 square kilometers.[^hospital-density] This aggregated dataset was merged with the coordination data using the prefecture as the merge key. We considered this variable as the traveling cost of coordination and donation.

[^ref]: Data source: <https://www.jmdp.or.jp/hospitals/view2/> (Accessed August 4, 2022).

[^hospital-density]: To calculate the density of the hospitals in each prefecture, we used the land area data provided by the Geospatial Information Authority of Japan.

```{r descriptive-stats, include=FALSE}
with(rct$data, prop.table(table(donate)))
with(rct$data, summary(age))
with(rct$data, prop.table(table(age < 40)))
with(rct$data, prop.table(table(male)))
with(rct$data, prop.table(table(coordinate1)))
with(rct$data, prop.table(table(prefecture)[order(table(prefecture))]))
with(subset(rct$data, prefecture %in% c("東京都", "大阪府")), table(prefecture, hospital_per_area))
with(rct$data, mean(unique(hospital_per_area)))
```

The analysis sample included 11,049 completed or interrupted coordinations involving matched donors living in Japan.[^exclude] Of these coordinations, $4.6$\% were completed (donation was made) and $63.5$\% involved matched donors coordinating for the first time. The mean and median age of matched donors were 39 and $37.98$ years, respectively, while $62.4$\% of coordinations involved male donors. There were slightly more young donors and male donors than in the donor pool.[^detail-descriptive-stats]

```{r ongoing-balance, include=FALSE}
ongoing_f <- rawdt$balance_attrition()
```

[^exclude]: One coordination involved a matched donor who lived abroad. There were 104 coordinations with ongoing coordination at the time of data collection. The proportion of ongoing coordinations was balanced across the experimental groups (`r ongoing_f[[2]]`).

[^detail-descriptive-stats]: Regarding geographic distribution, $17.1$\% of coordinations involved matched donors who lived in Tokyo or Osaka, where hospital density is well above the national average ($1.89$ and $1.36$, respectively compared with the national average of $0.21$).

The primary outcome was whether matched donors underwent CT. This outcome is important for two reasons. First, reaching the CT stage requires donors to respond to the HLA match letter, indicate their willingness to donate, and maintain their intentions. Additionally, late responses lead to coordination interruptions before the CT stage. Second, physicians can select the most appropriate donor for transplantation from among the matched donors who have undergone CT. Thus, showing up for CT represents both a costly prosocial behavior and an important practical indicator of coordination.

```{r reason-stop, include=FALSE}
mean_test <- subset(rct$data, treat == "StatusQuo") %>%
  with(prop.table(table(test)) * 100)

mean_positive <- subset(rct$data, treat == "StatusQuo") %>%
  with(prop.table(table(positive)) * 100)

mean_test_cond <- rct$data %>%
  filter(treat == "StatusQuo" & positive == 1) %>%
  with(prop.table(table(test)) * 100)

reason_classify <- rct$data %>%
  filter(positive == 1 & test == 0 & treat == "StatusQuo") %>%
  with(prop.table(table(exg_stop_test, useNA = "always")) * 100)
```

In the StatusQuo group, only `r sprintf("$%1.2f$%%", mean_test["1"])` of matched donors underwent CT. Two factors explain this low rate. First, only `r sprintf("$%1.2f$%%", mean_positive["1"])` indicated their willingness to donate. Second, `r sprintf("$%1.2f$%%", mean_test_cond["0"])` of those who expressed a willingness to donate did not reach the CT stage (i.e., dropped out between the response and CT), and `r sprintf("$%1.2f$%%", reason_classify["0"])` of these dropouts were donor-related reasons. According to @Hirakawa2018, \revise{the top donor-related reasons are health conditions such as lower back pain, scheduling conflicts, and the lack of family consent.}[^imputed-rates] \revise{Thus, major obstacles are low willingness to donate and donor-related dropout between the response and CT.}

[^imputed-rates]: Using values from @Hirakawa2018, `r sprintf("$%1.2f$%%", reason_classify["0"] * 0.69)` of dropouts was due to donor health conditions, `r sprintf("$%1.2f$%%", reason_classify["0"] * 0.16)` of dropouts was due to scheduling conflicts, and `r sprintf("$%1.2f$%%", reason_classify["0"] * 0.10)` of dropouts was due to the lack of family consent.

```{r summary}
rct$
  summary_experiment()$
  kable(
    title = "Summary of the Field Experiment",
    notes = paste(
      "\\\\emph{Note}: For the balance test, we regressed a covariate on treatment dummies and tested the null hypothesis that all coefficients are zero. We used standard errors clustered by the assigned week for the statistical inference. Abbreviation: PBSC = peripheral blood stem cell; BM = bone marrow."
    ),
    font_size = 8
  )
```

Table \@ref(tab:summary) summarizes our experiment. Panels A and B present the intervention and sample size for each experimental group, respectively. Panel C presents a balance test of whether the randomization was successful. There were statistically significant differences in the average age and number of holidays in the assignment week and the following week between the experimental groups. The average age of the CoordMessage group was approximately one year younger than that of the StatusQuo group. However, this difference was negligible from a standardized mean difference perspective (see Table A1 in Supplementary Material A). The average number of holidays for the MatchMessage group was higher than that of the StatusQuo group. This occurred because for a cluster of the MatchMessage group assigned in December, the week following their assignment week included the New Year's holiday (see Table \@ref(tab:assignment)).[^new-year-holidays]

[^new-year-holidays]: In Japan, the New Year's holiday is set by the government to run from December 29 to January 3. While we follow this definition, this holiday may be extended depending on individual circumstances.

Although most covariates were balanced across the experimental groups, a few were unbalanced.[^cor] Therefore, in addition to a simple difference-in-means test, we estimated the following linear regression model for HLA match letter $i$ sent out in week $w$ of month $m$:

[^cor]: We confirmed that age and the number of holidays did not affect CT, which is our primary outcome, in the StatusQuo group. Therefore, the imbalance in some covariates is not a major concern. We present the results of a regression analysis that adjusts for these effects in Supplementary Material A.

\begin{equation}
  \begin{split}
  Y_{iwm} =& \alpha + \beta_1 \cdot \text{MatchMessage}_{wm}
  + \beta_2 \cdot \text{CoordMessage}_{wm} + \beta_3 \cdot \text{BothMessage}_{wm} \\
  &+ X'_{iwm} \gamma + u_{iwm},
  \end{split}(\#eq:reg)
\end{equation}

\noindent
where $X_{iwm}$ is a vector of observable characteristics, including donor age and the number of holidays. The parameters of interest are $(\beta_1, \beta_2, \beta_3)$.

\revise{There may be intra-cluster correlation among donors matched with the same patient because multiple donors can be matched with the same patient (and physicians later select one from among those who reach CT). Therefore, it is desirable to use standard errors clustered at the \emph{patient} level or two-way at the patient and assigned week levels. However, we do not have patient IDs or information that identifies which patient each donor (or coordination) was matched with. Instead, we used standard errors clustered by the \emph{assigned week} for statistical inference, as treatment was assigned at the week level; this may also partially capture patient-level correlation when donors matched with the same patient received letters in the same week.}

# Experimental Results {#result}
## Average Treatment Effects on Reaching CT {#main}

In this subsection, we present the estimated effects of the intervention messages on reaching the CT stage. We used a dummy variable coded one if a matched donor reached the CT stage.[^outcome-skipped-CT] \revise{As discussed in Section \ref{data}, the main barriers are low willingness to donate and donor-related dropout between the response and CT stages. We therefore expect that our intervention messages mitigate these barriers and increase the probability of reaching the CT stage.}

[^outcome-skipped-CT]: We also coded the CT dummy one if CT was skipped.

```{r test-lm}
rct$
  lm_effect("test", sample_drop = FALSE)$
  fit(scale = 100)$
  kable_reg(
    title = "Effect of the Intervention Messages on Reaching CT",
    coef_map_lm = c(
      "treatMatchMessage" = "MatchMessage group",
      "treatCoordMessage" = "CoordMessage group",
      "treatBothMessage" = "BothMessage group"
    ),
    notes = "Standard errors clustered by the assigned week are in parentheses. The unit of treatment effect is a percentage point. Covariates are sex, age, its squared term, the number of past coordinations, the number of public holidays in the assigned week and following week, the number of hospitals per 10 square kilometers, the number of hospitals with PBSC collection per 10 square kilometers, the number of hospitals with bone marrow collection per 10 square kilometers, and a dummy indicating that a candidate can skip CT. All the covariates except the sex dummy and dummy of skipped CT were demeaned."
  )
```

\revise{Table \ref{tab:test-lm} shows that the MatchMessage group increased the probability of coordinations reaching the CT stage by $1.63$ percentage point. This table reports the results of regression analyses. Because we observe some imbalance in covariates, we focus on column (3), which controls for covariates and month fixed effects. In all columns, standard errors are clustered at the week level. We obtain similar results under several alternative specifications: removing covariates (columns (1) and (2)), adjusting for multiple hypotheses testing following \citet{List2019} (Figure A1 in Supplementary Material A), and using logistic regression models (Table A2 in Supplementary Material A). Therefore, including the matching difficulty message in the HLA match letter is an effective intervention to accelerate transplant coordinations.}

```{r lm-test-decompose}
rct$
  lm_decompose_effect("test")$
  fit(scale = 100)$
  kable_reg(
    title = "Decomposition of the Effect on Reaching CT",
    coef_map_lm = c(
      "treatMatchMessage" = "MatchMessage group",
      "treatCoordMessage" = "CoordMessage group",
      "treatBothMessage" = "BothMessage group"
    ),
    notes = "Robust standard errors are in parentheses. The unit of treatment effect is a percentage point. The outcome ``Endogenous dropout'' is a dummy variable that takes a value of 1 if candidates responded with a willingness to donate but did not reach the CT stage for donor-side health and non-health reasons . Covariates are gender, age and its squared term, the number of past coordinations, the number of public holidays in the assigned week and the following week, the number of hospitals per 10 square kilometers, the number of hospitals with PBSC collection per 10 square kilometers, the number of hospitals with BM collection per 10 square kilometers, and a dummy indicating that the candidate skipped CT. All the covariates except the gender dummy and dummy of skipped CT were demeaned.",
    font_size = 8
  )
```

As mentioned previously, our intervention is expected to increase the probability of reaching CT by improving the willingness to donate and preventing dropout between the response and CT stages. Therefore, we decomposed the intervention message effects into two components: responses with a willingness to donate and prevention of dropout for donor-side reasons (endogenous dropout). The results are presented in Table \@ref(tab:lm-test-decompose). Although the evidence is suggestive, our intervention worked as expected, except for the CoordMessage group.

However, the mechanisms differed slightly across the intervention groups. The willingness to donate increased primarily in the MatchMessage group. As shown in column (1), the willingness to donate in this group increased by $2.31$ percentage points, statistically significant at the 10\% level. Endogenous dropout in the MatchMessage group also fell by approximately 1 percentage point, although this was not statistically significant. Combining these effects, the probability of reaching CT increased in the MatchMessage group. By contrast, the CoordMessage and BothMessage groups primarily contributed to preventing endogenous dropout. In particular, as shown in column (4), endogenous dropout fell by $2.27$ percentage points in the BothMessage group, statistically significant at the 5\% level. However, the willingness to donate of these groups did not sufficiently increase, limiting the increase in the probability of reaching CT in both groups. Therefore, these findings suggest that the matching difficulty message may help improve the willingness to donate, while the early coordination message may prevent endogenous dropout.

## Effect on Response Speed {#response-speed}

The early coordination message is expected to increase the CT completion rate by encouraging early responses. Among donors who indicated a willingness to donate, those who responded earlier had a higher probability of reaching CT (see Figure \@ref(fig:speed-CT-cond-response)). Therefore, we examined whether the CoordMessage and BothMessage groups, which did not show an overall increase in their willingness to donate, may have shown increased early responses accompanied by a willingness to donate.


```{r cumulative-response, fig.cap = "Cumulative Rate of Response with Positive Intention by Treatment \\newline \\emph{Note}: We excluded those who skipped CT. We only show the cumulative response rates up to 25 days after the HLA match letter was sent because there was no remarkable change in the response rate thereafter."}
rct_noskip$
  flow("positive", sample_drop = FALSE)$
  plot_cumulative(
    upper_days = 25,
    xbreaks = seq(0, 100, by = 4),
    ylim = c(0, 60),
    xlab = "Response days",
    ylab = "Cumulative rate of\nresponse with positive intention (%)",
    base_size = 25
  )
```

```{r lm-positive-time-decompose}
rct$
  flow(outcome = "positive", sample_drop = FALSE)$
  lm_time_segment(cut_days = c(7, 12))$
  fit(scale = 100)$
  kable_reg(
    title = "Effect on Response Speed with Positive Intention",
    coef_map_lm = c(
      "treatMatchMessage" = "MatchMessage group",
      "treatCoordMessage" = "CoordMessage group",
      "treatBothMessage" = "BothMessage group"
    ),
    notes = "Robust standard errors are in parentheses. The unit of treatment effect is a percentage point. The outcome is a dummy variable that takes a value of 1 if the candidate responded with positive intention within a specified time after the HLA match letter being sent. We excluded those who skipped CT. Covariates are gender, age and its squared term, the number of past coordinations, the number of public holidays in the assigned week and the following week, the number of hospitals per 10 square kilometers, the number of hospitals with PBSC collection per 10 square kilometers, and the number of hospitals with BM collection per 10 square kilometers. All the covariates were demeaned.",
    font_size = 8
  )
```

First, Figure \@ref(fig:cumulative-response) shows the cumulative response rates of the willingness to donate over time for the experimental groups. We obtain two notable findings. First, up to approximately 10 days, the cumulative response rates of the intervention groups were almost identical but lower than those of the StatusQuo group. This suggests that the early coordination message may not have had the expected effect. Second, after 14 days, the cumulative response rate of the MatchMessage group became higher than that of the StatusQuo group. Thus, the willingness to donate of the MatchMessage group increased but this may have slowed response speed.

Next, we verified these findings through regression analysis. Since the JMDP requests responses within seven days, we defined early responses as responses with a willingness to donate within seven days. We created dummy variables for responses with a willingness to donate within 7 days, 8--12 days, and after 13 days. We then estimated linear probability models using these dummy variables as outcomes. Table \@ref(tab:lm-positive-time-decompose) presents the estimation results. The results were consistent with the descriptive findings but the differences from the StatusQuo group were not statistically significant. Therefore, the early coordination message did not have the expected effect.

# Policy and Welfare Implications of the Intervention {#discussion}

To discuss the policy and welfare implications of the intervention, we examine treatment effects on the post-CT stages: donor selection, final consent, and collection (donation). These stages are influenced by both our intervention and patient-side demand. As a benchmark, when the JMDP sends HLA match letters to 10 donors and all reach the CT stage, selection and donation rates reach a maximum of 10\% because a physician selects one best donor.[^other-benchmark] In the StatusQuo group, the selection and donation rates are $6.19$\% and $4.5$\%, respectively; the gap reflects dropout due to patient deterioration or failure to obtain final consent.

[^other-benchmark]: When desirable donors are not found through the CT stage or when few matched donors complete the CT stage, a physician may be unable to find the best donor among matched donors. In this case, selection and donation rates fall below 10\%. Conversely, when the JMDP office sends HLA match letters to fewer than 10 matched donors, selection and donation rates exceed 10\%.

Our intervention had no statistically significant effects on post-CT outcomes (Figure A2 and Table A3 in Supplementary Material A). The estimated effects on all three stages are smaller than on the CT stage: donor selection and donation in the MatchMessage group fell by $0.29$ and $0.12$ percentage points, respectively, which were not statistically significant.[^logit] In sum, the matching difficulty message promoted reaching the CT stage but did not increase selection or donation rates.

[^logit]: Logistic regression yielded similar results (see Table A4 in Supplementary Material A).

We should not conclude from this result alone that patient welfare did not improve. Because more matched donors reached CT in the MatchMessage group, physicians could choose the best donor from a larger pool. The intervention may thus raise transplant quality (e.g., better donor selection and patient prognosis) even if it does not raise quantity.

Heterogeneous treatment effects by gender, age, and past coordination experience support this possibility (Figure A3 in Supplementary Material A). The MatchMessage treatment encouraged young men with past coordination experience to reach CT (7 percentage points; $p = 0.05$) and increased their probability of being selected as the best donor (5 percentage points; $p < 0.01$). This result is desirable given evidence that young male donors improve patient prognosis \citep{Loren2006, Arai2016, Kollman2016, Shinohara2017}.[^our-data-analysis] Thus, the MatchMessage treatment may improve transplant quality by encouraging such donors to reach CT.

[^our-data-analysis]: Using those in the StatusQuo group who reached the CT stage, we examine which characteristics make candidates more likely to be selected as the best donor (Table A5 in Supplementary Material A). As a result, young men were more likely to be selected as the best donor, consistent with medical findings. We also find that donor selection and donation were unrelated to the speed of reaching the CT stage (those who responded to the HLA match letter quickly or could skip CT).

At the same time, the MatchMessage treatment promoted older men matched for the first time and young women with past coordination experience to reach CT, but did not increase their probability of selection.[^implication-to-ATE] They may thus have wasted their time, and the intervention may have reduced donor welfare in this sense. Therefore, interventions targeting young men may be more appropriate than a uniform message to all matched donors, from the perspectives of welfare and cost-effectiveness.

[^implication-to-ATE]: The MatchMessage group changed the behavior of both those likely to be selected as donors and those unlikely to be selected, resulting in average treatment effects on donor selection and donation close to zero. This reflects the result that the MatchMessage treatment increased coordinations interrupted for exogenous reasons (donor health reasons such as disqualification because of the CT results and patient-side reasons) among those who reached the CT stage (Table A6 in Supplementary Material A).

# Conclusions {#conclusion}

This study examined how information provision at the time of matching affects donor availability in stem cell transplantation. The results of our field experiment demonstrated that providing information on the limited number of HLA-compatible donors per patient (i.e., the matching difficulty message) increased the probability of reaching CT. This result suggests that physicians can select the best donor for transplantation from a larger pool of matched donors. However, when presented simultaneously with an ineffective early coordination message, the positive effect of the matching difficulty message was diminished. We speculate this is because of the negative effect of information overload. Therefore, it is important to convey effective information in a simple manner.

\revise{To evaluate the cost effectiveness of the intervention, we translate the effect of the matching difficulty message into an equivalent number of additional donor registrations. The matching difficulty message increased the CT completion rate by $7.3\% (= 1.63/22.25)$. This effect is equivalent to increasing the number of matched donors by $7.3$\%.}[^proof] \revise{Since 40\% of registrants become matched donors, $224,000$ of the current $560,000$ registrants are potential matched donors.}[^data1] \revise{Therefore, the effect is equivalent to increasing the number of matched donors from $224,000$ to $240,352$ ($=224,000 \times 1.073$) (an increase of $16,352$), or equivalently, to increasing the number of registrants from $560,000$ to $600,880$ ($=560,000 \times 1.073$) (an increase of $40,880$).}

\revise{This equivalence has direct policy relevance. In the current JMDP donor pool, owing to the age limit for donation (54 years), $100,000$ donors in their 50s will exit the pool within the next five years.}[^data2] \revise{Given the message effect is equivalent to recruiting $40,880$ new donors, the matching difficulty message can therefore offset approximately $40.9\%$ ($= 40,880/100,000$) of the negative effects caused by this shrinking donor pool.}

\revise{However, donor recruitment is costly. While the cost required to add one donor registration at the JMDP is unknown, the National Marrow Donor Program incurs approximately USD 150 per additional registration.}[^data3] \revise{If the JMDP bears a similar cost, recruiting $40,880$ donor candidates would cost approximately USD $6.132$ million. Thus, adding the matching difficulty message could be a more cost-effective measure than recruiting new donors to address the shrinking donor pool.}

[^proof]: Let $N_m$ be the number of registrants who start the coordination process. Let $N_1(d)$ be the number of potential donors who reach CT under treatment $d$. Then, $N_1(d) = p(d)N_m$ holds, where $p(d)$ is the probability of reaching CT under treatment $d$. Note that $d = 1$ and $d = 0$ represent the treatment and control groups, respectively. We solve $N_1(1) = p(0)[N_m + \Delta N_m]$ for $\Delta N_m$, where $\Delta N_m$ represents the increase in registrants who start coordination. Therefore, we obtain $[p(1) - p(0)]/p(0) = \Delta N_m/N_m$.

[^data1]: The cumulative number of registrants since the JMDP's establishment is $980,000$. Among these registrants, $390,000$ have become potential donors who started the coordination process. Therefore, 40\% of registrants become potential donors who start coordination. Data source: <https://www.bs.jrc.or.jp/bmdc/donorregistrant/m2_03_00_statistics.html> (Accessed December 8, 2024).

[^data2]: <https://www.jmdp.or.jp/about/read/number/> (Accessed December 8, 2024).

[^data3]: <https://fundraise.nmdp.org/index.cfm?fuseaction=cms.page&id=1203&eventID=675> (Accessed March 29, 2025).

Finally, our intervention can be applied to contexts beyond stem cell transplantation. The essence of the matching difficulty message is to emphasize the scarcity of investors or potential cooperators for public goods. In our context, this message corrected donors' overestimation of substitutable other donors and discouraged free-riding. Alternatively, this message made the rarity of opportunities to cooperate salient. Unfortunately, our data cannot identify which mechanism drove donors. Nevertheless, communicating the scarcity of cooperators is likely to be effective in other cooperative environments such as donations of rare blood types.