---
title: |
  Online Supplementary Material
  "Field experiment Using Text Messages to Promote Stem Cell Donation in Japan Marrow Donor Program"
bibliography: biblio.bib
biblio-style: agsm
output:
  bookdown::pdf_document2:
    latex_engine: pdflatex
    template: template/my-template.tex
    keep_tex: true
    toc: false
    number_sections: true
    citation_package: natbib
base-strech: 1.5
fontsize: 12pt
params:
  is_fe: TRUE
  is_cluster: FALSE
  se_type: stata
---

\listoftables
\clearpage

```{r include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  error = FALSE,
  message = FALSE,
  dev = "pdf",
  fig.width = 15,
  fig.height = 10,
  fig.pos = "t",
  out.extra = ""
)
```

```{r option, include = FALSE}
options(
  knitr.table.format = "latex",
  kableExtra.auto_format = FALSE
)
```

\appendix

\setcounter{figure}{0}
\setcounter{table}{0}
\renewcommand\thefigure{\thesection\arabic{figure}}
\renewcommand{\thetable}{\thesection\arabic{table}}
\renewcommand{\theHfigure}{\thesection\arabic{figure}}
\renewcommand{\theHtable}{\thesection\arabic{table}}
# Additional Figures and Tables {#figtab}

```{r library, include=FALSE}
library(here)
library(xfun)
source(here("R/R6_RawData.r"))
source(here("R/R6_Schedule.r"))

options(
  knitr.kable.NA = "",
  modelsummary_stars_note = FALSE
)

data_root <- "E:/JMDPフィールド実験"
```

```{r assignment}
schedule <- Schedule$new(here(data_root, "RCT-schedule.csv"))
schedule$kable(
  title = "Assignment Schedule",
  notes = paste(
    "\\\\emph{Note}: See Table 1 in the main manuscrpit for a detailed description of the intervention of each experimental arm. The control arm is experimental arm A. The experiment was not conducted during the week beginning December 27, 2021, and ending January 3, 2022, because JMDP was closed for the New Year's holiday."
  ),
  hold = TRUE,
  font_size = 8
)
```

```{r data, include=FALSE}
rawdt <- RawData$new(
  here(data_root, "shape.csv"),
  treat_vars = "treat",
  treat_levels = LETTERS[1:4]
)

# main sample
rawdt$add_cond_study_sample("ongoing == 0")

# robust sample (initially matched candidates)
rawdt_initial <- rawdt$clone()
rawdt_initial$add_cond_study_sample("coordinate == 1")

# robust sample (remove those who skipped the CT)
rawdt_noskip <- rawdt$clone()
rawdt_noskip$add_cond_study_sample("reply == 0 | days_reply > 0")
```

```{r set-rct-class, include=FALSE}
intervention <- list(
  "Standard notification" = c(A = "X", B = "X", C = "X", D = "X"),
  "Probability message" = c(A = "", B = "X", C = "", D = "X"),
  "Early coordination message" = c(A = "", B = "", C = "X", D = "X")
)

endpoint <- list(
  reply = "Response",
  positive = "Positive Intention",
  test = "CT",
  candidate = "Candidate Selection",
  consent = "Final Consent",
  donate = "Donation"
)

# main sample
rct <- rawdt$RCT()
rct$add_intervention(intervention)
rct$add_outcome(endpoint)
if (params$is_cluster) rct$set_default_cluster("RCTweek")
rct$set_default_se_type(params$se_type)

# robust sample (initially matched candidate)
rct_initial <- rawdt_initial$RCT()
rct_initial$add_intervention(intervention)
rct_initial$add_outcome(endpoint)
if (params$is_cluster) rct_initial$set_default_cluster("RCTweek")
rct_initial$set_default_se_type(params$se_type)

# robust sample (remove those who skipped the CT)
rct_noskip <- rawdt_noskip$RCT()
rct_noskip$add_intervention(intervention)
rct_noskip$add_outcome(endpoint)
if (params$is_cluster) rct_noskip$set_default_cluster("RCTweek")
rct_noskip$set_default_se_type(params$se_type)
```

## Balance Test

```{r summary}
rct$
  summary_experiment()$
  kable(
  title = "Summary of Field Experiment",
  notes = paste(
    "\\\\emph{Note}: For the balance test, we regressed a covariate on treatment dummies and tested the null hypothesis that all coefficients are zero. We used robust standard errors for statistical inference."
  ),
  hold = TRUE,
  font_size = 8
)
```

```{r smd-balance}
rct$
  smd_balance()$
  kable(
    title = "Assessing Balance by Standaridized Mean Difference",
    notes = "\\\\emph{Note}: These values represent the standardized mean differences (SMD) with the control arm (experimental arm A). Generally, covariates between two groups are balanced if the SMD is less than $0.1$.",
    hold = TRUE,
    font_size = 8
  )
```

## Effect on the CT
### Average Treatment Effects

```{r lm-test}
rct$
  lm_effect("test", sample_drop = FALSE)$
  fit(scale = 100)$
  kable_reg(
    title = "Linear Probability Model of the CT",
    notes = "The robust standard errors are in parentheses. The unit of treatment effect is a percentage point. Covariates are gender, (demeaned) age, its squared term, the number of past coordinations, the number of public holidays in the assigned week and the following week, the number of hospitals per 10 square kilometers, the number of hospitals with PBSC collection per 10 square kilometers and the number of hospitals with BM collection per 10 square kilometers. All covariates except gender were demeaned.",
    hold = TRUE,
    font_size = 8
  ) %>%
  column_spec(1, width = "20em")
```

```{r logit-test}
rct$
  logit_effect("test", sample_drop = FALSE)$
  fit()$
  kable(
    title = "Logit Model of the CT",
    notes = "Covariates are gender, (demeaned) age, its squared term, the number of past coordinations, the number of public holidays in the assigned week and the following week, the number of hospitals per 10 square kilometers, the number of hospitals with PBSC collection per 10 square kilometers and the number of hospitals with BM collection per 10 square kilometers. All covariates except gender were demeaned.",
    fmt = "%.2f",
    hold = TRUE,
    font_size = 8
  ) %>%
  column_spec(1, width = "20em")
```

```{r lm-test-initial}
rct_initial$
  lm_effect("test", sample_drop = FALSE)$
  fit(scale = 100)$
  kable_reg(
    title = "Linear Probability Model of the CT (Only First-time Matched Candidates)",
    notes = "The robust standard errors are in parentheses. The unit of treatment effect is a percentage point. We restricted the analysis sample to those who matched the first time. Covariates are gender, (demeaned) age, its squared term, the number of past coordinations, the number of public holidays in the assigned week and the following week, the number of hospitals per 10 square kilometers, the number of hospitals with PBSC collection per 10 square kilometers and the number of hospitals with BM collection per 10 square kilometers. All covariates except gender were demeaned.",
    hold = TRUE,
    font_size = 8
  ) %>%
  column_spec(1, width = "20em")
```

```{r lm-test-noskip}
rct_noskip$
  lm_effect("test", sample_drop = FALSE)$
  fit(scale = 100)$
  kable_reg(
    title = "Linear Probability Model of the CT (Excluding Those Who Skipped the CT)",
    notes = "The robust standard errors are in parentheses. The unit of treatment effect is a percentage point. We excluded those who skipped the CT. Covariates are gender, (demeaned) age, its squared term, the number of past coordinations, the number of public holidays in the assigned week and the following week, the number of hospitals per 10 square kilometers, the number of hospitals with PBSC collection per 10 square kilometers and the number of hospitals with BM collection per 10 square kilometers. All covariates except gender were demeaned.",
    hold = TRUE,
    font_size = 8
  ) %>%
  column_spec(1, width = "20em")
```

### Heterogeneous Treatment Effects

```{r set-lm-interaction-test, include=FALSE}
test_interaction_gender <- rct$
  lm_effect("test", sample_drop = FALSE)$
  fit(scale = 100, interaction_of_gender = TRUE)

test_interaction_gender_age <- rct$
  lm_effect("test", sample_drop = FALSE)$
  fit(scale = 100, interaction_of_gender_age = TRUE, age_cut = 40)
```

```{r lm-interaction-gender-test}
test_interaction_gender$
  kable_reg(
    title = "Heterogenous Message Effects on CT by Gender",
    notes = "The robust standard errors are in parentheses. This table tests heterogenous message effects by gender. The unit of treatment effect is a percentage point. Covariates are age, the number of past coordinations, the number of public holidays in the assigned week and the following week, the number of hospitals per 10 square kilometers, the number of hospitals with PBSC collection per 10 square kilometers and the number of hospitals with BM collection per 10 square kilometers. All covariates were demeaned. We also controlled cross terms of each covariate and gender.",
    hold = TRUE,
    font_size = 8
  ) %>%
  column_spec(1, width = "20em")
```

```{r lh-interaction-gender-test}
test_interaction_gender$
  kable_lh(
    title = "Linear Combination Test: Message Effects on the CT for Specific Gender Group",
    notes = "The robust standard errors are in parentheses. We performed a linear combination test on the coefficients of the linear probability model presented in Table \\\\ref{tab:lm-interaction-gender-test}. The null hypothesis for females is that the treatment dummy is zero. The null hypothesis for males is that the sum of the treatment dummy and the cross term of the treatment dummy and the gender dummy is zero.",
    hold = TRUE,
    font_size = 8
  ) %>%
  column_spec(1:2, width = "8em")
```

```{r mh-adjust-gender-test}
mha_gender_test <- cache_rds(
  {
    rct$
      multiple_hypotheses_adjust("test")$
      estimate(scale = 100, B = 3000)$
      get_result()
  },
  file = "mh-adjust-gender-test.rds"
)

mha_gender_test %>%
  select(Subgroup.id, Treated.id, Diff, Single.p, List.p) %>%
  knitr::kable(
    caption = "Adjustment of p-values for Multiple Testing of Effect on the CT for Specific Gender Group",
    col.names = c(
      "Group", "Treatment", "Diff-in-mean", "Unadjusted", "Adjusted"
    ),
    digits = 3,
    align = "llccc",
    booktabs = TRUE,
    linesep = ""
  ) %>%
  kableExtra::kable_styling(font_size = 8, latex_options = "HOLD_position") %>%
  kableExtra::add_header_above(c(" " = 3, "p-values" = 2)) %>%
  kableExtra::footnote(
    general_title = "",
    general = "\\\\emph{Note}: To adjust p-values for multiple testing, we employed the method proposed by List et al. (2019). For calculation of p-values, we used the bootstrapping with 3,000 boostrap samples.",
    threeparttable = TRUE,
    escape = FALSE
  )
```

```{r lm-interaction-gender-age-test}
test_interaction_gender_age$
  kable_reg(
    title = "Heterogenous Message Effects on CT by Gender-Age Group",
    notes = "The robust standard errors are in parentheses. This tabel tests heterogenous message effects by gender and age. We created two age groups (Younger/Older) based on age 40. The unit of treatment effect is a percentage point. Covariates are the number of past coordinations, the number of public holidays in the assigned week and the following week, the number of hospitals per 10 square kilometers, the number of hospitals with PBSC collection per 10 square kilometers and the number of hospitals with BM collection per 10 square kilometers. All covariates were demeaned. We also controlled cross terms of each covariate and gender-age group dummies.",
    hold = TRUE,
    font_size = 8
  ) %>%
  column_spec(1, width = "20em")
```

```{r lh-interaction-gender-age-test}
test_interaction_gender_age$
  kable_lh(
    title = "Linear Combination Test: Message Effects on CT for Specific Gender-Age Group",
    notes = "The robust standard errors are in parentheses. We performed a linear combination test on the coefficients of the linear probability model presented in Table \\\\ref{tab:lm-interaction-gender-age-test}. The null hypothesis for young women is that the treatment dummy is zero. The null hypothesis for the other gender-age groups is that the sum of the treatment dummy and the cross term of the treatment dummy and the gender-age group dummy is zero.",
    hold = TRUE,
    font_size = 8
  ) %>%
  column_spec(1:2, width = "8em")
```

```{r mh-adjust-gender-age-test}
mha_gender_age_test <- cache_rds(
  {
    rct$
      multiple_hypotheses_adjust("test", gender_age = TRUE, age_cut = 40)$
      estimate(scale = 100, B = 3000)$
      get_result()
  },
  file = "mh-adjust-gender-age-test.rds"
)

mha_gender_age_test %>%
  select(Subgroup.id, Treated.id, Diff, Single.p, List.p) %>%
  knitr::kable(
    caption = "Adjustment of p-values for Multiple Testing of Effect on the CT for Specific Gender-Age Group",
    col.names = c(
      "Group", "Treatment", "Diff-in-mean", "Unadjusted", "Adjusted"
    ),
    digits = 3,
    align = "llccc",
    booktabs = TRUE,
    linesep = ""
  ) %>%
  kableExtra::kable_styling(font_size = 8, latex_options = "HOLD_position") %>%
  kableExtra::add_header_above(c(" " = 3, "p-values" = 2)) %>%
  kableExtra::footnote(
    general_title = "",
    general = "\\\\emph{Note}: To adjust p-values for multiple testing, we employed the method proposed by List et al. (2019). For calculation of p-values, we used the bootstrapping with 3,000 boostrap samples.",
    threeparttable = TRUE,
    escape = FALSE
  )
```

### Decompose Effects: Intention and Attrition Perspectives

```{r lm-test-decompose}
rct$
  lm_decompose_effect("test")$
  fit(scale = 100)$
  kable_reg(
    title = "Decompose Effect on the CT: Intention and Attrition Perspectives",
    notes = "The robust standard errors are in parentheses. The unit of treatment effect is a percentage point. The outcome ``No exogenous attrition'' is a dummy variable that takes a value of 1 if coordination was not interrupted due to exogenous reasons (patient-side reasons) between reply with positive intention and CT. The outcome ``No endogenous attrition'' is a dummy variable that takes a value of 1 if coordination was not interrupted due to other reasons (mainly donor-side reasons). Covariates are gender, age, its squared term, the number of past coordinations, the number of public holidays in the assigned week and the following week, the number of hospitals per 10 square kilometers, the number of hospitals with PBSC collection per 10 square kilometers and the number of hospitals with BM collection per 10 square kilometers. All covariates were demeaned.",
    hold = TRUE,
    font_size = 8
  )
```

```{r lm-test-decompose-noskip}
rct_noskip$
  lm_decompose_effect("test")$
  fit(scale = 100)$
  kable_reg(
    title = "Decompose Effect on the CT: Intention and Attrition Perspectives (Excluding Those Who Skipped the CT)",
    notes = "The robust standard errors are in parentheses. The unit of treatment effect is a percentage point. We excluded those who skipped the CT. The outcome ``No exogenous attrition'' is a dummy variable that takes a value of 1 if coordination was not interrupted due to exogenous reasons (patient-side reasons) between reply with positive intention and CT. The outcome ``No endogenous attrition'' is a dummy variable that takes a value of 1 if coordination was not interrupted due to other reasons (mainly donor-side reasons). Covariates are gender, age, its squared term, the number of past coordinations, the number of public holidays in the assigned week and the following week, the number of hospitals per 10 square kilometers, the number of hospitals with PBSC collection per 10 square kilometers and the number of hospitals with BM collection per 10 square kilometers. All covariates were demeaned.",
    hold = TRUE,
    font_size = 8
  )
```

```{r set-lm-interaction-test-decompose-noskip, include=FALSE}
test_decompose_interaction_gender <- rct_noskip$
  lm_decompose_effect("test")$
  fit(scale = 100, interaction_of_gender = TRUE)

test_decompose_interaction_gender_age <- rct_noskip$
  lm_decompose_effect("test")$
  fit(scale = 100, interaction_of_gender_age = TRUE, age_cut = 40)
```

```{r lm-interaction-gender-test-decompose-noskip}
test_decompose_interaction_gender$
  kable_reg(
    title = "Heterogenity of Decomposition of Effect on the CT by Gender: Intention and Attrition Perspectives (Excluding Those Who Skipped the CT)",
    notes = "The robust standard errors are in parentheses. The unit of treatment effect is a percentage point. We excluded those who skipped the CT. The outcome ``No exogenous attrition'' is a dummy variable that takes a value of 1 if coordination was not interrupted due to exogenous reasons (patient-side reasons) between reply with positive intention and CT. The outcome ``No endogenous attrition'' is a dummy variable that takes a value of 1 if coordination was not interrupted due to other reasons (mainly donor-side reasons). Covariates are age, its squared term, the number of past coordinations, the number of public holidays in the assigned week and the following week, the number of hospitals per 10 square kilometers, the number of hospitals with PBSC collection per 10 square kilometers and the number of hospitals with BM collection per 10 square kilometers. All covariates were demeaned. We also controlled cross terms of each covariate and gender."
  )
```

```{r lh-interaction-gender-test-decompose-noskip}
test_decompose_interaction_gender$
  kable_lh(
    title = "Linear Combination Test: Decomposition of Effects on CT for Specific Gender Group (Intention and Attrition Perspectives; Excluding Those Who Skipped the CT)",
    notes = "The robust standard errors are in parentheses. We performed a linear combination test on the coefficients of the linear probability model presented in Table \\\\ref{tab:lm-interaction-gender-test-decompose-noskip}. The null hypothesis for females is that the treatment dummy is zero. The null hypothesis for males is that the sum of the treatment dummy and the cross term of the treatment dummy and the gender dummy is zero.",
    hold = TRUE,
    font_size = 8
  )
```

```{r lm-interaction-gender-age-test-decompose-noskip}
test_decompose_interaction_gender_age$
  kable_reg(
    title = "Heterogenity of Decomposition of Effect on the CT by Gender-Age Groups: Intention and Attrition Perspectives (Excluding Those Who Skipped the CT)",
    notes = "The robust standard errors are in parentheses. The unit of treatment effect is a percentage point. We created two age groups (Younger/Older) based on age 40. We excluded those who skipped the CT. The outcome ``No exogenous attrition'' is a dummy variable that takes a value of 1 if coordination was not interrupted due to exogenous reasons (patient-side reasons) between reply with positive intention and CT. The outcome ``No endogenous attrition'' is a dummy variable that takes a value of 1 if coordination was not interrupted due to other reasons (mainly donor-side reasons). Covariates are age, its squared term, the number of past coordinations, the number of public holidays in the assigned week and the following week, the number of hospitals per 10 square kilometers, the number of hospitals with PBSC collection per 10 square kilometers and the number of hospitals with BM collection per 10 square kilometers. All covariates were demeaned. We also controlled cross terms of each covariate and gender-age group."
  )
```

```{r lh-interaction-gender-age-test-decompose-noskip}
test_decompose_interaction_gender_age$
  kable_lh(
    title = "Linear Combination Test: Decomposition of Effects on CT for Specific Gender-Age Group (Intention and Attrition Perspectives; Excluding Those Who Skipped the CT)",
    notes = "The robust standard errors are in parentheses. We performed a linear combination test on the coefficients of the linear probability model presented in Table \\\\ref{tab:lm-interaction-gender-age-test-decompose-noskip}. The null hypothesis for young women is that the treatment dummy is zero. The null hypothesis for the other gender-age groups is that the sum of the treatment dummy and the cross term of the treatment dummy and the gender-age group dummy is zero.",
    hold = TRUE,
    font_size = 8
  )
```

### Decompose Effects: Response Timing Perspective

```{r response-speed-CT, fig.cap = "Binned Scatter Plot of CT (or Response with Positive Intention) vs. Response Days. \\newline \\emph{Note}: We run logistic regression of the CT (or response with positive intention) on response days. We excluded those who skipped the CT and used control arm. We show the regression lines and its 95 percent confidence interval.", fig.pos = "H"}
reply_dt <- rct$data %>%
  filter(reply == 1 & 0 < days_reply & treat == "A")

plotdt <- reply_dt %>%
  mutate(ntile = ntile(days_reply, 20)) %>%
  group_by(ntile) %>%
  summarize(
    median_day = (max(days_reply) + min(days_reply)) / 2,
    mean_intention = mean(positive),
    mean_ct = mean(test)
  ) %>%
  pivot_longer(
    mean_intention:mean_ct,
    names_to = "outcome",
    names_prefix = "mean_",
    values_to = "mean"
  ) %>%
  mutate(
    outcome = factor(
      outcome,
      levels = c("intention", "ct"),
      labels = c("Positive intention", "CT")
    )
  )

plotdt %>%
  ggplot(aes(x = median_day, y = mean)) +
    geom_point(aes(shape = outcome), color = "grey40", size = 3) +
    geom_smooth(
      aes(x = days_reply, y = positive),
      data = reply_dt,
      method = "glm",
      method.args = list(family = "binomial"),
      se = TRUE,
      alpha = 0.2,
      color = "black",
      linetype = 2
    ) +
    geom_smooth(
      aes(x = days_reply, y = test),
      data = reply_dt,
      method = "glm",
      method.args = list(family = "binomial"),
      se = TRUE,
      alpha = 0.2,
      color = "black",
      linetype = 1
    ) +
    labs(x = "Response days", y = "Proportion", shape = "Outcome") +
    my_theme_classic(size = 20) +
    theme(legend.position = "bottom")
```

```{r dist-response-speed, fig.cap = "Density of Number of Days Required for Response with Positive Intention. \\newline \\emph{Note}: We excluded those who did not respond and skipped the CT. We also excluded those who responded after 50 days due to outliers.", fig.pos = "H"}
rct_noskip$
  flow(outcome = "positive", sample_drop = FALSE)$
  plot_density(
    upper_days = 50,
    x_breaks = seq(0, 100, by = 4)
  )
```

```{r lm-positive-time-decompose-noskip}
rct_noskip$
  flow(outcome = "positive", sample_drop = FALSE)$
  lm_time_segment(cut_days = c(4, 9))$
  fit(scale = 100)$
  kable_reg(
    title = "Effect on Speed of Response with Positive Intention (Excluding Those Who Skipped the CT)",
    notes = "The robust standard errors are in parentheses. The unit of treatment effect is a percentage point. The outcome is a dummy variable that takes a value of 1 if candidate responded with positive intention within a specified time after mailing. We excluded those who skipped the CT. Covariates are gender, age, its squared term, the number of past coordinations, the number of public holidays in the assigned week and the following week, the number of hospitals per 10 square kilometers, the number of hospitals with PBSC collection per 10 square kilometers and the number of hospitals with BM collection per 10 square kilometers. All covariates were demeaned.",
    hold = TRUE,
    font_size = 8
  )
```

```{r lm-test-time-decompose-noskip}
rct_noskip$
  flow(outcome = "test", sample_drop = FALSE)$
  lm_time_segment(cut_days = c(4, 9))$
  fit(scale = 100)$
  kable_reg(
    title = "Decomposition of Effect on the CT: Response Speed Perspectives (Excluding Those Who Skipped the CT)",
    notes = "The robust standard errors are in parentheses. The unit of treatment effect is a percentage point. The outcome is a dummy variable that takes a value of 1 if candidate responded with positive intention within a specified time after mailing and reached the CT. Covariates are gender, age, its squared term, the number of past coordinations, the number of public holidays in the assigned week and the following week, the number of hospitals per 10 square kilometers, the number of hospitals with PBSC collection per 10 square kilometers and the number of hospitals with BM collection per 10 square kilometers. All covariates were demeaned.",
    hold = TRUE,
    font_size = 8
  )
```

```{r dist-response-speed-by-gender, fig.cap = "Density of Number of Days Required for Response with Positive Intention by Gender. \\newline \\emph{Note}: We excluded those who did not respond and skipped the CT. We also excluded those who responded after 50 days due to outliers.", fig.pos = "H"}
rct_noskip$
  flow(outcome = "positive", sample_drop = FALSE)$
  plot_density(
    upper_days = 50,
    subset_by_gender = TRUE,
    x_breaks = seq(0, 100, by = 4)
  )
```

```{r set-lm-interaction-int-time-decompose-noskip,include=FALSE}
int_t_decompose_gender <- rct_noskip$
  flow(outcome = "positive", sample_drop = FALSE)$
  lm_time_segment(cut_days = c(4, 9))$
  fit(scale = 100, interaction_of_gender = TRUE)

int_t_decompose_gender_age <- rct_noskip$
  flow(outcome = "positive", sample_drop = FALSE)$
  lm_time_segment(cut_days = c(4, 9))$
  fit(scale = 100, interaction_of_gender_age = TRUE, age_cut = 40)
```

```{r lm-interaction-gender-int-time-decompose-noskip}
int_t_decompose_gender$
  kable_reg(
    title = "Heterogenity of Effect on Speed of Response with Positive Intention by Gender (Excluding Those Who Skipped the CT)",
    notes = "The robust standard errors are in parentheses. The unit of treatment effect is a percentage point. The outcome is a dummy variable that takes a value of 1 if candidate responded with positive intention within a specified time after mailing. We excluded those who skipped the CT. Covariates are age, its squared term, the number of past coordinations, the number of public holidays in the assigned week and the following week, the number of hospitals per 10 square kilometers, the number of hospitals with PBSC collection per 10 square kilometers and the number of hospitals with BM collection per 10 square kilometers. All covariates were demeaned. We also controlled cross term of each covariate and gender dummy.",
    hold = TRUE,
    font_size = 8
  )
```

```{r lh-interaction-gender-int-time-decompose-noskip}
int_t_decompose_gender$
  kable_lh(
    title = "Effect on Speed of Response with Positive Intention for Specific Gender Group (Excluding Those Who Skipped the CT)",
    notes = "The robust standard errors are in parentheses. We performed a linear combination test on the coefficients of the linear probability model presented in Table \\\\ref{tab:lm-interaction-gender-int-time-decompose-noskip}. The null hypothesis for females is that the treatment dummy is zero. The null hypothesis for males is that the sum of the treatment dummy and the cross term of the treatment dummy and the gender dummy is zero.",
    hold = TRUE,
    font_size = 8
  )
```

```{r dist-response-speed-by-gender-age, fig.cap = "Density of Number of Days Required for Response with Positive Intention by Gender. \\newline \\emph{Note}: We excluded those who did not respond and skipped the CT. We also excluded those who responded after 50 days due to outliers.", fig.pos = "H"}
rct_noskip$
  flow(outcome = "positive", sample_drop = FALSE)$
  plot_density(
    upper_days = 50,
    subset_by_gender_age = TRUE,
    age_cut = 40,
    x_breaks = seq(0, 100, by = 4)
  )
```

```{r lm-interaction-gender-age-int-time-decompose-noskip}
int_t_decompose_gender_age$
  kable_reg(
    title = "Heterogenity of Effect on Speed of Response with Positive Intention by Gender and Age (Excluding Those Who Skipped the CT)",
    notes = "The robust standard errors are in parentheses. The unit of treatment effect is a percentage point. The outcome is a dummy variable that takes a value of 1 if candidate responded with positive intention within a specified time after mailing. We excluded those who skipped the CT. We created two age groups (Younger/Older) based on age 40. Covariates are age, its squared term, the number of past coordinations, the number of public holidays in the assigned week and the following week, the number of hospitals per 10 square kilometers, the number of hospitals with PBSC collection per 10 square kilometers and the number of hospitals with BM collection per 10 square kilometers. All covariates were demeaned. We also controlled cross term of each covariate and gender-age group dummies.",
    hold = TRUE,
    font_size = 8
  )
```

```{r lh-interaction-gender-age-int-time-decompose-noskip}
int_t_decompose_gender_age$
  kable_lh(
    title = "Effect on Speed of Response with Positive Intention for Specific Gender-Age Group (Excluding Those Who Skipped the CT)",
    notes = "The robust standard errors are in parentheses. We performed a linear combination test on the coefficients of the linear probability model presented in Table \\\\ref{tab:lm-interaction-gender-age-int-time-decompose-noskip}. The null hypothesis for young women is that the treatment dummy is zero. The null hypothesis for the other gender-age groups is that the sum of the treatment dummy and the cross term of the treatment dummy and the gender-age group dummy is zero.",
    hold = TRUE,
    font_size = 8
  )
```

```{r set-lm-interaction-test-time-decompose-noskip, include=FALSE}
# gender-age groupはRunできない

test_t_decompose_gender <- rct_noskip$
  flow(outcome = "test", sample_drop = FALSE)$
  lm_time_segment(cut_days = c(4, 9))$
  fit(scale = 100, interaction_of_gender = TRUE)
```

```{r lm-interaction-gender-test-time-decompose-noskip}
test_t_decompose_gender$
  kable_reg(
    title = "Heterogeneity of Decomposition of Effect on the CT: Response Speed Perspectives (Excluding Those Who Skipped the CT)",
    notes = "The robust standard errors are in parentheses. The unit of treatment effect is a percentage point. The outcome is a dummy variable that takes a value of 1 if candidate responded with positive intention within a specified time after mailing and reached the CT. Covariates are age, its squared term, the number of past coordinations, the number of public holidays in the assigned week and the following week, the number of hospitals per 10 square kilometers, the number of hospitals with PBSC collection per 10 square kilometers and the number of hospitals with BM collection per 10 square kilometers. All covariates were demeaned. We also controlled cross term of each covariate and geder dummy.",
    hold = TRUE,
    font_size = 8
  )
```

```{r lh-interaction-gender-test-time-decompose-noskip}
test_t_decompose_gender$
  kable_lh(
    title = "Decomposition of Effect on the CT for Specific Gender Group: Response Speed Perspectives (Excluding Those Who Skipped the CT)",
    notes = "The robust standard errors are in parentheses. We performed a linear combination test on the coefficients of the linear probability model presented in Table \\\\ref{tab:lm-interaction-gender-test-time-decompose-noskip}. The null hypothesis for females is that the treatment dummy is zero. The null hypothesis for males is that the sum of the treatment dummy and the cross term of the treatment dummy and the gender dummy is zero.",
    hold = TRUE,
    font_size = 8
  )
```

## Effect on Remaining Coordination Process
### Average Treatment Effects

```{r lm-coordinate}
rct$
  lm_effect(c("candidate", "consent", "donate"), sample_drop = FALSE)$
  fit(scale = 100)$
  kable_reg(
    title = "Linear Probability Model of Coordination Process After CT",
    notes = "The robust standard errors are in parentheses. The unit of treatment effect is a percentage point. Covariates are gender, (demeaned) age, its squared term, the number of past coordinations, the number of public holidays in the assigned week and the following week, the number of hospitals per 10 square kilometers, the number of hospitals with PBSC collection per 10 square kilometers and the number of hospitals with BM collection per 10 square kilometers. All covariates except gender were demeaned.",
    hold = TRUE,
    font_size = 8
  )
```

```{r logit-coordinate}
rct$
  logit_effect(c("candidate", "consent", "donate"), sample_drop = FALSE)$
  fit()$
  kable(
    title = "Logit Model of Coordination Process After CT",
    notes = "Covariates are gender, (demeaned) age, its squared term, the number of past coordinations, the number of public holidays in the assigned week and the following week, the number of hospitals per 10 square kilometers, the number of hospitals with PBSC collection per 10 square kilometers and the number of hospitals with BM collection per 10 square kilometers. All covariates except gender were demeaned.",
    fmt = "%.2f",
    hold = TRUE,
    font_size = 8
  )
```

```{r lm-coordinate-initial}
rct_initial$
  lm_effect(c("candidate", "consent", "donate"), sample_drop = FALSE)$
  fit(scale = 100)$
  kable_reg(
    title = "Linear Probability Model of Coordination Process After CT (Only First-time Matched Candidates)",
    notes = "The robust standard errors are in parentheses. The unit of treatment effect is a percentage point. We restricted the analysis sample to those who matched the first time. Covariates are gender, (demeaned) age, its squared term, the number of past coordinations, the number of public holidays in the assigned week and the following week, the number of hospitals per 10 square kilometers, the number of hospitals with PBSC collection per 10 square kilometers and the number of hospitals with BM collection per 10 square kilometers. All covariates except gender were demeaned.",
    hold = TRUE,
    font_size = 8
  )
```

```{r lm-coordinate-noskip}
rct_noskip$
  lm_effect(c("candidate", "consent", "donate"), sample_drop = FALSE)$
  fit(scale = 100)$
  kable_reg(
    title = "Linear Probability Model of Coordination Process After CT (Excluding Those Who Skipped the CT)",
    notes = "The robust standard errors are in parentheses. The unit of treatment effect is a percentage point. We excluded those who skipped the CT. Covariates are gender, (demeaned) age, its squared term, the number of past coordinations, the number of public holidays in the assigned week and the following week, the number of hospitals per 10 square kilometers, the number of hospitals with PBSC collection per 10 square kilometers and the number of hospitals with BM collection per 10 square kilometers. All covariates except gender were demeaned.",
    hold = TRUE,
    font_size = 8
  )
```

### Heterogenous Treatment Effects

```{r set-lm-interaction-coordinate, include=FALSE}
coordinate_interaction_gender <- rct$
  lm_effect(c("candidate", "consent", "donate"), sample_drop = FALSE)$
  fit(scale = 100, interaction_of_gender = TRUE)

coordinate_interaction_gender_age <- rct$
  lm_effect(c("candidate", "consent", "donate"), sample_drop = FALSE)$
  fit(scale = 100, interaction_of_gender_age = TRUE)
```

```{r lm-interaction-gender-coordinate}
coordinate_interaction_gender$
  kable_reg(
    title = "Heterogeneity of Message Effects on Coordination Process After CT by Gender",
    notes = "The robust standard errors are in parentheses. This table tests heterogenous message effects by gender. The unit of treatment effect is a percentage point. Covariates are age, the number of past coordinations, the number of public holidays in the assigned week and the following week, the number of hospitals per 10 square kilometers, the number of hospitals with PBSC collection per 10 square kilometers and the number of hospitals with BM collection per 10 square kilometers. All covariates were demeaned. We also controlled cross terms of each covariate and gender.",
    hold = TRUE,
    font_size = 8
  )
```

```{r lh-interaction-gender-coordinate}
coordinate_interaction_gender$
  kable_lh(
    title = "Linear Combination Test: Message Effects on Coordination Process After CT for Specific Gender Group",
    notes = "The robust standard errors are in parentheses. We performed a linear combination test on the coefficients of the linear probability model presented in Table \\\\ref{tab:lm-interaction-gender-coordinate}. The null hypothesis for females is that the treatment dummy is zero. The null hypothesis for males is that the sum of the treatment dummy and the cross term of the treatment dummy and the gender dummy is zero.",
    hold = TRUE,
    font_size = 8
  )
```

```{r lm-interaction-gender-age-coordinate}
coordinate_interaction_gender_age$
  kable_reg(
    title = "Heterogenous Message Effects on Coordination Process After CT by Gender-Age Group",
    notes = "The robust standard errors are in parentheses. This tabel tests heterogenous message effects by gender and age. We created two age groups (Younger/Older) based on age 40. The unit of treatment effect is a percentage point. Covariates are the number of past coordinations, the number of public holidays in the assigned week and the following week, the number of hospitals per 10 square kilometers, the number of hospitals with PBSC collection per 10 square kilometers and the number of hospitals with BM collection per 10 square kilometers. All covariates were demeaned. We also controlled cross terms of each covariate and gender-age group dummies.",
    hold = TRUE,
    font_size = 8
  )
```

```{r lh-interaction-gender-age-coordinate}
coordinate_interaction_gender_age$
  kable_lh(
    title = "Linear Combination Test: Message Effects on Coordination Process After CT for Specific Gender-Age Group",
    notes = "The robust standard errors are in parentheses. We performed a linear combination test on the coefficients of the linear probability model presented in Table \\\\ref{tab:lm-interaction-gender-age-coordinate}. The null hypothesis for young women is that the treatment dummy is zero. The null hypothesis for the other gender-age groups is that the sum of the treatment dummy and the cross term of the treatment dummy and the gender-age group dummy is zero.",
    hold = TRUE,
    font_size = 8
  )
```

<!---
# Economic Models for Predictions

In this section, we present a simple inter-temporal economic model to make predicitions of message effects. We assume that the matched donor may have the present bias, which is one of the most important insight from behaviorl economics [@Laibson1997; @ODonoghue2001].

\noindent
**Events.** Consider three periods ($t = 1, 2, 3$). At $t=1$, a matched donor receives the compatibility notice, which asks him/her to donate. The matched donor has three options: quick response (responsding at $t=1$); late response (responding at $t=2$); no response. If the matched donor responds, then the donor pays coordination cost $c$ at that time and obtains net-benefit of transplantion at the next period. The net-benefit of transplantion may be time-variant: $b_t$ if the matched donor responds at period $t$. We assume $b_1 \ge b_2$. If the matched donor does not respond, the donor does not pay any cost and receive any net-benefit.

\noindent
**Preference.** According to @Laibson1997, the utility function is $U_t = u_t + \beta \sum_{\tau = t + 1}^{3} \delta^{\tau - t} u_{\tau}$ where $\beta \in (0, 1]$ is the degree of present bias and $\delta \in (0, 1]$ is standard time discount factor. Moreover, at period $t$, the donor expect that s/he makes decisions after $t + 1$ based on $\hat{\beta} \in [\beta, 1]$. If $\beta < \hat{\beta}$, the donor falsely believes that the present bias of their future self is not as strong.

We will solve an interpersonal game [@ODonoghue2001] to obtain optimal response timing. The first result shows that the matched donor thinks that the late response is never optimal regardless of the present bias before receiving the compatibility notice ($t=0$).

\noindent
**Result 1.** For any $\beta$, $\hat{\beta}$ and $b_2$, at $t = 0$, the quick response is optimal if $b_1 \ge c/\delta$; otherwise the no response is optimal.

\noindent
*Proof.* At $t=0$, the utility of the quick response is $\beta(-\delta c + \delta^2 b_1)$, which is positive $b_1 > c / \delta$. The utility of the late response is $\beta(-\delta^2 c + \delta^3 b_2)$. Let $b_2 = b_1 - d$ for $d \ge 0$. Then, the utility of the late response is positive if $b_1 > c/\delta + d$. Note that the utility of the no response is zero. Thus, if $b_1 < c/\delta$, then the no response is optimal because the quick response and the late response produce negative utilities. The quick response is preferred to the late response if
\begin{equation}
  b_1 \ge \frac{c}{\delta} - \frac{\delta}{1-\delta}d. (\#eq:cond-t0)
\end{equation}
Thus, the quick response is optimal if $b_1 \ge c/\delta$ since the Equation (\ref{eq:cond-t0}) holds.

This resuls implies that, before receiving the compatibility notice, the matched donor thinks that the donor quickly respond to the compatibility notice if the transplantion net-benefit is sufficiently large. The next result presents that the donor may delay the response, while receiving the notice, even if the trasplantation value is sufficiently large.

\noindent
**Result 2.** Suppose that $b_1 = b_2$. At $t=1$, the quick response is optimal if $b_1 \ge c \frac{1-\beta\delta}{(1-\delta)\beta\delta}$; the late response is optimal if $c \frac{1-\beta\delta}{(1-\delta)\beta\delta} > b_1 \ge c/\beta\delta$; otherwise the no response is optimal.

\noindent
*Proof.* We employ the backward-induction to solve the interpersonal game. Consider $t=2$. If the matched donor does not choose the quick response, the donor can respond to the notice at that period. Then, the utility of the late response at $t=2$ is $-c + \beta\delta b_2$. Thus, the late response is optimal iff $b_2 \ge c/\beta\delta$. Otherwise, the donor choose the no response. Next, we go back to $t=1$ and analyze how the donor expects behavior at $t=2$. The donor believes that future selve's present bias is $\hat{\beta}$. Thus, at $t = 1$, the donor expect that s/he will respond at $t = 2$ (the late response) if and only if $b_2 \ge c/\hat{\beta}\delta$. Assuming $b_2 = b_1$, we derive the optimal choice at $t=1$ in three cases.

- Consider $b_1 < c/\hat{\beta}\delta$. Then, at $t = 1$, the donor expects to give up responding, and actually does so. Thus, the donor at $t = 1$ responds if and only if $U_1 = -c + \beta\delta b_1 \ge 0$ or $b_1 \ge c/\beta\delta$. Otherwise, the donor gives up responding. Thus, the optimal choice is the no response.
- Consider $c/\hat{\beta}\delta \le b_1 < c/\beta\delta$. Then, at $t=1$, the donor expects to respond at $t = 2$, but will not actually take that action (no response). Due to this false prediction, the donor at $t = 1$ responds if and only if $U_1 \ge \beta(-\delta c + \delta^2 b_1)$ or
\begin{equation}
  c \frac{1 - \beta\delta}{(1-\delta)\beta\delta} \le b_1. (\#eq:cond-t1)
\end{equation}
Otherwise, the donor eventually stops responding. Since $\frac{1}{\beta\delta} < \frac{1 - \beta\delta}{\beta\delta}$, the optimal choice is the no response in this case.
- Consider $c/\beta\delta \le b_1$. Then, at $t = 1$, the donor expects to respond at $t = 2$, and actually does so. Thus, the donor responds at $t = 1$ if and only if equation (\ref{eq:cond-t1}) holds. Otherwise, the donor responds at $t=2$.

This result is motivated us to create the Early Coordination message. If the net benefit of transplantion is time-invariant, then some mathced donors thinks that the quick response is ideal but acutually choose the late response or the no response. Especially, if $c/\delta \le b_1 < c/\beta\delta$, then the matched donor thinks that the quick response but does not actually respond to the compatibility notice. If $c/\beta\delta \le b_1 < c \frac{1 - \beta\delta}{(1-\delta)\beta\delta}$, then the matched donor thinks that the quick response but does delay response to the compatibility notice.

The next result shows that almost matched donor follows ideal behavior (the optimal choice at $t=0$; see Result 1) if there is sufficiently large difference between $b_1$ and $b_2$

\noindent
**Result 3.** Let $b_2 = b_1 - d$. Suppose that $c \left(\frac{1-\beta\delta}{\beta\delta} - \frac{1-\delta}{\hat{\beta}\delta} \right) < d$. Then, the matched donor actually chooses the quick response if $c/\beta\delta \le b_1$; otherwise the matched donor actually chooses the no response.
--->